### 2013-04-01 draft_01/draft.tex
1st upload of evla draft

\documentclass[iop]{emulateapj}
\usepackage{color}
\usepackage{natbib}
\bibliographystyle{apj}

\newcommand{\vdag}{(v)^\dagger}
\newcommand{\myemail}{eogorma@tcd.ie}

\shorttitle{Radio Emission of Dust-free Red Giant Mass Outflows}
\shortauthors{O'Gorman et al.}

\begin{document}

\title{Multi-frequency Radio Continuum Emission of Dust-free Red Giant Mass Outflows}

\author{Eamon O'Gorman\altaffilmark{1}, Graham M. Harper\altaffilmark{1}, Alexander Brown\altaffilmark{2}, Anita M.S. Richards\altaffilmark{3}, and Stephen Drake\altaffilmark{4}}
\altaffiltext{1}{School of Physics, Trinity College Dublin, Dublin 2, Ireland}
\altaffiltext{2}{Center for Astrophysics and Space Astronomy, University of Colorado, 389 UCB, Boulder, CO 80309, USA}
\altaffiltext{3}{Jodrell Bank Centre for Astrophysics, School of Physics and Astronomy, University of Manchester, Manchester M13 9PL, UK}
\altaffiltext{4}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}

%\email{eogorma@tcd.ie}
%\email{graham.harper@tcd.ie}
%\email{alexander.brown@colorado.edu}
%\email{a.m.s.richards@manchester.ac.uk}
%\email{drake@milkyway.gsfc.nasa.gov}

\begin{abstract}

Multi-frequency centimeter radio continumm observations of dust-free red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited. These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements accumulated over many years. Here, we present multi-frequency Karl G. Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus and Aldebaran. Uniquely, these multi-frequency observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored. We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for Arcturus. This is the first time single (non-binary) luminosity class III red giants have been observed at such long wavelengths. These measurements sample the outermost layers where the wind velocity is close to its terminal value and the ionization balance is close to becoming \textit{frozen-in}, and are therefore important empirical inputs for future wind models. We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models. The marked deviations between our data and existing semi-empirical models highlight the need for new atmospheric models to be developed.

\end{abstract}

\keywords{circumstellar matter --- Stars: individual: ($\rm{\alpha}$ Boo, $\rm{\alpha}$ Tau) --- Stars: late-type --- Stars: chromospheres --- Stars: winds, outflows --- Radio continuum: stars}

\section{INTRODUCTION}

Mass loss from late-type evolved stars plays a crucial role in both stellar and galactic evolution and ultimately provides part of of the material required for the next generation of stars and planets. Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery (clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g.
\citealt{2009AIPC.1094..267C}). There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}. Optical and ultraviolet observations reveal an absence of hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.][]{1979ApJ...229L..27L,1981ApJ...250..293A}.

Magnetic fields are most likely involved in the mass loss process, although current magnetic models are also unsuccessful. Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H}) are untenable. These models predict chromospheres as integral parts of turbulently extended and heated wind acceleration zones, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}. One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta. A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not currently in agreement with observations \citep{2009AIPC.1094..267C}. It has also been suggested that the winds may be driven by some form of magnetic pressure acting on highly clumped wind material \citep{2008AJ....136.1964E} but \cite{2010ApJ...720.1767H} does not find support for this hypothesis. Progress in this field continues to be driven by observations that provide new insights into the mass loss problem.

\subsection{Radio Continuum Observations} \label{intro1}

Although studies of wind-scattered UV and optical line profiles have provided clues to the mass-loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained. In the UV, the source function is very sensitive to electron temperature (i.e. $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value. At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e. $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure. It is this value that controls the atomic level populations and ionization that feed into UV spectroscopic analyses. This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.

In the cm-radio regime the radio opacity strongly increases with wavelength (i.e. $ \kappa \propto \lambda ^{2.1}$) so the longer wavelengths sample the extended layers of the stars atmosphere thus essentially providing us with spatial information about the star's mass outflow region. The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes frozen-in at these radii. Furthermore, it is these outer extended regions of the star's atmosphere that contribute to the commonly seen P Cygni line profiles in the UV. In these profiles the line-of-sight absorption caused by the star's wind is superimposed on the blueshifted emission. Thus, centimeter radio continuum observations can provide a test of models based on these UV profiles. In this paper we directly compare our new Karl G. Jansky Very Large Array (VLA) observations with atmospheric models derived from UV analysis.

\subsection{Sample Selection} \label{intro2}

Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the symbiotic and $\zeta$ Aurigae systems (e.g. \citealt{2008ApJ...675..711C};   \citealt{1996ApJ...466..979B}). Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities. For example, the orbital separation is often within the wind acceleration region and one could expect wind accretion and flow perturbations to be present (e.g. \citealt{1981ApJ...248.1043C}). In fact, using the ``old'' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types.

In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III). These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known. These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density. Moreover both stars have existing semi-empirical 1-D chromospheric and wind models which we directly test the validity of in this paper.

\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize}
\tablecaption{Some properties of our red giant sample.}
\tablehead{	\colhead{}		       				& 
			\colhead{$\alpha$ Boo}				&
			\colhead{$\alpha$ Tau}				}
\startdata
Spectral Type 				& K2 III  & K5 III  \\
Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
Wind Temperature (K)		& $\sim 10,000$  & $< 10,000$  \\
Wind Terminal Velocity & $\sim$ 40 km s$^{-1}$ & $\sim$ 30 km s$^{-1}$ \\
Semi-empirical model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
\enddata
\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}.}

\label{tab:tab1}
\end{deluxetable}

\begin{deluxetable*}{ccccccccc}
\tabletypesize{\scriptsize}
%\tablecolumns{6} 
%\tablewidth{0pt} 
\tablecaption{VLA Observations}
\tablehead{\colhead{Star}			            &
\colhead{Date}
				&
          	\colhead{Band}	      				&
          	\colhead{Frequency\tablenotemark{a}}&
	\colhead{Wavelength}			         	&
           	\colhead{Time on Star}              &
           	\colhead{Bandwidth}            		&
           	\colhead{Number of}            		&
	\colhead{Phase}		\\
	\colhead{}									&
    \colhead{}		                			& 
    \colhead{}		                			& 
	\colhead{(GHz)}                        		& 
	\colhead{(cm)}                         		& 
	\colhead{(hr)}                    			&
	\colhead{(GHz)}                        		&
	\colhead{Antennas\tablenotemark{b}}         &
	\colhead{Calibrator}		}
\startdata
$\alpha$ Boo	& 2011 Feb 22 & Q	& 43.3 & 0.7		& 0.3 	&  0.256	&22& J1357+1919  \\
$\alpha$ Boo 	& 2011 Feb 22 & Ka	& 33.6 & 0.9		& 0.2 	&  0.256 	&23&J1357+1919  \\
$\alpha$ Boo 	& 2011 Feb 22 & K	& 22.5 & 1.3		& 0.4	&  0.256 	&24&J1357+1919  \\
$\alpha$ Boo 	& 2011 Feb 11 & X	& 8.5  & 3.5		& 0.3 	&  0.256 	&18&J1415+1320  \\
$\alpha$ Boo	& 2011 Feb 11 & C	& 5.0  & 6.0 		& 0.5	& 0.256 	&21& J1415+1320 \\
$\alpha$ Boo	& 2011 Feb 13 & S	& 3.1  & 9.5 		& 1.8 	& 0.256 	&12& J1415+1320 \\
$\alpha$ Boo 	& 2012 Jul 19 & S	& 3.0  & 10.0 		& 0.7 	& 2.0 		&23& J1415+1320 \\
$\alpha$ Boo	& 2012 Jul 20 & L	& 1.5  & 20.0		& 1.6 	& 1.0 		&23& J1415+1320 \\
$\alpha$ Tau	& 2011 Feb 11 & Q	& 43.3 & 0.7 		& 0.3 	& 0.256 	&22&  J0431+1731\\
$\alpha$ Tau	& 2011 Feb 11 & Ka	& 33.6 & 0.9 		& 0.2 	& 0.256 	&19&  J0449+1121\\
$\alpha$ Tau	& 2011 Feb 11 & K	& 22.5 & 1.3 		& 0.4 	& 0.256 	&21&  J0449+1121\\
$\alpha$ Tau	& 2011 Feb 13 & X	&  8.5 & 3.5 		& 0.5	& 0.256 	&25&  J0449+1121\\
$\alpha$ Tau	& 2011 Feb 13 & C	&  5.0 & 6.0 		& 1.2	& 0.256 	&21&  J0449+1121\\
$\alpha$ Tau	& 2011 Feb 12 & S	&  3.1 & 9.5 		& 1.8 	& 0.256 	&11&  J0431+2037
\enddata
\tablenotetext{a}{Central frequency of used bandpass.}
\tablenotetext{b}{Number of available antennas remaining after flagging.}
\label{tab:tab2}
\end{deluxetable*}

\section{OBSERVATIONS AND DATA REDUCTION}

Observations of $\alpha$ Boo and $\alpha$ Tau were carried out with the VLA during February 2011 at Q, Ka, K, X, C, and S-band in B-configuration (PI: Harper; program 10C-105). $\alpha$ Boo was also observed at S and L-band in July 2012 when the VLA was again in B-configuration (PI: O'Gorman; program 12A-472). Some details of these observations are given in Table \ref{tab:tab2}. For the 2011 observations, the correlator was set up with two 128 MHz sub-bands centered on the frequencies listed in Table \ref{tab:tab2}. Each sub-band had sixty-four channels of width 2 MHz and four polarization products (RR, LL, RL, LR). For the S and L band observations in 2012, the 1-2 GHz and 2-4 GHz frequency ranges were both divided into 16 sub-bands, each with sixty-four channels. The channel width was 2 and 1 MHz for S and L-band, respectively.

Both $\alpha$ Boo and $\alpha$ Tau were slightly offset from the phase-center by $\sim$\,5 synthesized beam widths in order to avoid possible errors at phase-center. All scheduling blocks (SBs) were kept to $\le$\,2.5 hours of duration to improve their likelihood of being scheduled. For the high frequency observations (i.e. Q, Ka, and K-bands) we used the \textit{fast switching} technique which consisted of rapidly alternating observations of the target source and a nearby unresolved phase calibrator. The total cycle times for the Q, Ka, and K-band observations were 160, 230, and 290 s, respectively. For both target sources these high frequency observations were combined into a single 2 hour observing track and commenced with X-band reference pointing with solutions being applied on-line. After X-band pointing the target source was observed at Q-band to insure the best pointing solutions were used. The lower frequencies tracks were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had much longer cycle times. The primary calibration sources 3C286 and 3C138 were observed at the end of all tracks and were used to measure the complex bandpass and set the absolute flux for $\alpha$ Boo and $\alpha$ Tau, respectively.

The data were flagged, calibrated, and imaged within the Common Astronomical Software Application  \cite[CASA;][]{2007ASPC..376..127M} package. Data deemed to be bad by the VLA online system were flagged, as were pure zeros, non-operational antennas antennas, dummy scans at the beginning of each track, and poorly performing antennas. Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged (a process known as \textit{quacking}). For the 2011 low frequency data the two sub-bands were centered at relatively radio frequency interference (RFI) free regions of the bandpass and only a very small amount of RFI had to be flagged.   The 2012 wide-band data was initially Hanning smoothed (combining adjacent frequency channels with weights 0.25, 0.5, and 0.25) to suppress Gibbs ringing. We manually flagged entire sub-bands that were badly contaminated with RFI. The \textit{testautoflag} task was then used to conservatively flag RFI from all sources and any remaining RFI was manually flagged.

In order to calibrate the data, we solved for the complex gains of the calibration sources while applying the bandpass solution, which was derived from the relevant aforementioned flux calibrators.  The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard. At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively. The more frequently observed phase calibrators were then used to calibrate the amplitude and phases of the targets. Atmospheric opacity corrections were also applied to the high frequency data sets using the average of a seasonal model (based on many years of measurements) and information from the weather station obtained during the observations.

The visibilities were then both Fourier transformed and deconvolved using the CASA \textit{clean} task in multi-frequency synthesis imaging mode, which separately grids the the multiple spectral channels onto the \textit{u-v} plane and therefore improves the overall \textit{u-v} coverage. We used natural weighting for maximum sensitivity and the cell size was chosen so that the synthesized beam was about five pixels across. For the high frequencies it was usually sufficient to place just one CLEAN circle around the target source.  For the low frequencies however, the image sizes were usually set to a few times the size of the primary beam so that nearby strong serendipitous sources could be CLEANed thus reducing their sidelobe contamination of the final image. These images were CLEANed interactively, with w-term correction, down to about the $3\sigma$  level with clean boxes placed around sources as they appeared in the residual image. All images were corrected for  primary beam attenuation.

Three different methods were used to calculate the flux density from the unresolved target sources in each image:
\begin{enumerate}
\item by taking the peak pixel value from the source
\item by manually integrating the flux density around the source
\item by fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
\end{enumerate}
Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}. We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies.

\begin{deluxetable*}{Cccccccc}
\tabletypesize{\scriptsize}
%\tablecolumns{6} 
%\tablewidth{0pt} 
\tablecaption{VLA Fluxes of $\alpha$ Boo and $\alpha$ Tau}
\tablehead{\colhead{}		            &
			\colhead{Band}		            &
			\colhead{Frequency\tablenotemark{a}}&
			\colhead{Peak Flux}					&
          	\colhead{Integrated Flux} 			&
          	\colhead{\textit{Imfit} Integrated}	&
			\colhead{Image rms}					&
           	\colhead{\textit{Imfit} Fitting}  	\\
	\colhead{}									&
	\colhead{}									&
	\colhead{(GHz)}								&
    \colhead{(mJy)}		        	& 
    \colhead{(mJy)}		                		& 
	\colhead{Flux (mJy)}                        		& 
	\colhead{(Jy beam^{-1})}         					&
	\colhead{Error (mJy)}		}
\startdata
$\alpha$ Boo (K2 III) &Q  &43.28& 5.941 & 6.093 & 6.420 & 0.301 &  0.261\\
&Ka &33.56& 4.159 & 4.319 & 4.489 & 0.083 & 0.090 \\
&K  &22.46& 1.827 & 1.784 & 1.809 & 0.043 & 0.050 \\
&X  &8.46 & 0.510 & 0.514 & 0.532 & 0.030 & 0.019 \\
&C  &4.90 & 0.214 & 0.144 & 0.159 & 0.035 & 0.009 \\
&S  &3.15 & 0.148 & 0.135 & 0.160 & 0.028 & 0.010\\
&S  &2.87 & 0.127 & 0.118 & 0.116 & 0.012 & 0.016\\
&L  &1.63 & 0.067 & 0.068 & 0.090 & 0.013 & 0.015\\
\hline
\rule{0pt}{3ex}  $\alpha$ Tau (K5 III)&Q  &43.28 & 3.672& 3.734 & 4.082 &  0.259& 0.183	\\
&Ka &33.56 & 2.188& 1.962 & 2.125 &  0.091& 0.070 \\
&K  &22.46 & 1.864& 1.881 & 2.069 &  0.042& 0.083 \\
&X  &8.46  & 0.296& 0.287 & 0.281 &  0.014& 0.015 \\
&C  &4.96  & 0.147& 0.167 & 0.176 &  0.010& 0.010 \\
&S  &3.15  & 0.062& 0.043 & - &  0.017 & -
\enddata
\tablenotetext{a}{Frequency of final image produced using \textit{clean}'s multi-frequency synthesis imaging mode.}
\label{tab:tab3}
\end{deluxetable*}

\section{RESULTS}

Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data. The flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here. Instead we give the values from the radio maps produced by concatenating the two sub-bands. We present in Table \ref{tab:tab3} the target flux densities extracted from these concatenated radio maps. In the following two sections we briefly discuss the properties of these radio maps for both targets.

\subsection{$\alpha$ Boo Radio Maps} \label{results1} 
High S/N detections ($>19\sigma$) of $\alpha$ Boo were made at 22.5, 33.6, and 43.3 GHz. Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations. The lower frequencies maps were contaminated by the emission of a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo. This source was reported by \cite{1986AJ.....91..602D} and their flux of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency. We find the source to have a spectral index of -1.4 and its flux reaches  80.3 mJy at 1.6 GHz. Surprisingly we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only. We obtain good detections ($>5\sigma$) of the star for both epochs at 3 GHz (S-band) and the peak flux densities agree within their uncertainties. We can therefore safely assume that the 1.5 GHz (L-band) flux has not changed significantly over that period either, and so can safely be included in any analysis. The map at L-band was highly contaminated by the emission of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level. There is a slight positional offset of $1\arcsec$ between the position of the peak flux for $\alpha$ Boo at 1.5 and 3.0 GHz for the 2012 data, which were taken within 1 day of each other. However, this is less than a quarter of the 1.5 GHz synthesized beam and considering that the $4\sigma$ contours overlap, we feel that it is highly unlikely that both sources are not $\alpha$ Boo.

\subsection{$\alpha$ Tau Radio Maps} \label{results2}
The final deconvolved radio maps of $\alpha$ Tau were of excellent quality with the rms noise reaching the predicted thermal noise in many cases. The target field at all frequencies was free from strong serendipitous radio sources and thus the final images were free of the sidelobe contamination that were present in the low frequency $\alpha$ Boo images. $\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had a flux of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively. Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz. Due to the limited number of S-band receivers installed at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection. We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density. As this is a weak detection we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may introduce further errors \citep{1999ASPC..180.....T}.

\begin{deluxetable*}{Ccccc}
\tabletypesize{\scriptsize}
%\tablecolumns{6} 
%\tablewidth{0pt} 
\tablecaption{Compilation of Previous $\alpha$ Boo and $\alpha$ Tau Observations ($\le 250$ GHz)}
\tablehead{							            &
    \colhead{Frequency}		       				& 
			\colhead{Date}						&
			\colhead{Flux Density}				&
          	\colhead{Source} 			\\
												&
	\colhead{(GHz)}								&
	\colhead{}									&
    \colhead{(mJy)}		        				& 
    \colhead{}			         				}
\startdata
$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & $0.39 \pm 0.13$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 May 20 & $0.26 \pm 0.08$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 Dec 26 & $\le 0.18(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Mar 17 & $0.24 \pm 0.05$ & \cite{1986AJ.....91..602D} \\
&15 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
&22.5  & 1999 Jan 06  & $ 1.7 \pm 0.2$ & \cite{2011AA...533A.107D} \\
&43.3  & 1999 Jan 06 & $ 3.3 \pm 0.4$ & \cite{2011AA...533A.107D} \\
&43.3  & 2004 Jan 25 & $ 3.34 \pm 0.08$ & \cite{2011AA...533A.107D} \\
&86  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
&108.4  & 1997 Nov - 2000 Jun & $ 20.09 \pm 0.69$ & \cite{2005AJ....129.2836C} \\
&217.8 & 1997 Nov - 2000 Jun  & $ 83.5 \pm 1.71$ & \cite{2005AJ....129.2836C} \\
&250  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
\hline
\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (private communication) \\
&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (private communication) \\
&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (private communication) \\
&15 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
&108.4  & 1997 Nov - 2000 Dec & $ 13.97 \pm 1.46$ & \cite{2005AJ....129.2836C} \\
&217.82 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
&250  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
\enddata
\label{tab:tab4}
\end{deluxetable*}

\section{DISCUSSION}
\subsection{Spectral Energy Distribution of $\alpha$ Boo} \label{disc1}
The first definite detection of a single red giant at centimeter wavelengths was of $\beta$ Gem by \cite{1983ApJ...274L..77D}. Included in this study was a probable $3\sigma$ detection of $\alpha$ Boo and since then there has been only a small number of sporadic centimeter and millimeter observations of the star. In Table \ref{tab:tab3} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}. We also include in this figure the chromosphere and wind models of \cite{1985pssl.proc..351D} which were based on the International Ultraviolet Explorer (IUE) Mg II k emission line and the overlap between the two models are represented by the green shaded area. At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e. $\sim \nu ^{2}$) as a result of the small density scale heights close to the star. At low frequencies however, the models predict the wind to have constant velocity, ionization and temperature and thus the slope  approaches the well known $\sim \nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}. The paucity and, in some cases low S/N, of previous observations make it difficult to discern the validity of this model prior to our multi-frequency study of this star.

The peak flux density values listed in Table \ref{tab:tab3} for $\alpha$ Boo are also included in Figure \ref{fig:fig1} along with their $1\sigma$ rms errors. Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz). At low frequencies this discrepancy may indicate that we are still sampling a region of the wind where it is still accelerating (i.e. it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis. Our highest frequency data points indicate a flux excess which is in agreement with previous higher frequency (i.e. mm-observations) observations. One notable exception to this high frequency flux excess are the two 43 GHz observations of \cite{2011AA...533A.107D} which are lower than our values by over 40\%. Such a level of chromospheric viability seems very high and would be unexpected from such supposedly inactive stars. Another possibility for the difference in values  is that the longer cycle times used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values. Future high frequency observations may clarify this matter.

\subsection{Spectral Energy Distribution of $\alpha$ Tau} \label{disc2}
\\
d
\\
\\
zz
\\
\\
\\
\\
d
\\
\\
zz
\\
\\
\\
\\
d
\\
\\
zz
\\
\\
\\
\subsection{Contribution Functions?} \label{disc3}
\subsection{Mass loss e.g. Drake & Linskey ?} \label{disc4}
\subsection{Future Atmospheric Models e.g. Advection?} \label{disc5}

\begin{figure*}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz. Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circular data points and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D} which are shown in green. The red circular data points are all of the previous observations which were acquired sporadically over the past $\sim 25$ years.}
\label{fig:fig1}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz. All our new $\alpha$ Tau multi-frequency VLA observations (blue circular data points) were acquired in just two days in February 2011. The red circular data points are all of the previous observations which were acquired over many years. The green line is an existing hybrid chromosphere and wind model for the star.}
\label{fig:fig2}
\end{figure*}

\section{CONCLUSIONS}

\acknowledgments
The data presented in this paper were obtained with the Karl G. Jansky Very Large Array (VLA) which is an instrument of the National Radio Astronomy Observatory (NRAO). The NRAO is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc. We wish to thank the NRAO helpdesk for their detailed responses to our CASA related queries.

{\it Facilities:} \facility{VLA}.

\bibliography{references}

\end{document}

### 2013-04-01 draft_02/draft.tex
1st upload of evla draft

--- 2013-04-01 draft_01/draft.tex
@@
 
-Multi-frequency centimeter radio continumm observations of dust-free red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
+Multi-frequency centimeter continuum observations of non-dusty and molecule-free red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
 These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements accumulated over many years.
@@
 We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for Arcturus.
-This is the first time single (non-binary) luminosity class III red giants have been observed at such long wavelengths.
-These measurements sample the outermost layers where the wind velocity is close to its terminal value and the ionization balance is close to becoming \textit{frozen-in}, and are therefore important empirical inputs for future wind models.
+This is the first time single (non-binary) luminosity class III red giants have been observed at such long continuum wavelengths.
+These measurements sample the outermost layers where the wind velocity is approaching its terminal value and the ionization balance is  becoming \textit{frozen-in}, and are therefore important empirical inputs for future wind models.
 We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models.
@@
 One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta.
-A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not currently in agreement with observations \citep{2009AIPC.1094..267C}.
-It has also been suggested that the winds may be driven by some form of magnetic pressure acting on highly clumped wind material \citep{2008AJ....136.1964E} but \cite{2010ApJ...720.1767H} does not find support for this hypothesis.
+A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not yet in agreement with observations \citep{2009AIPC.1094..267C}.
+It has also been suggested that the winds may be driven by some form of magnetic pressure acting on very highly clumped wind material \citep{2008AJ....136.1964E} but \cite{2010ApJ...720.1767H} does not find support for this hypothesis.
 Progress in this field continues to be driven by observations that provide new insights into the mass loss problem.
@@
 Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the symbiotic and $\zeta$ Aurigae systems (e.g.
-\citealt{2008ApJ...675..711C};   \citealt{1996ApJ...466..979B}).
+\citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
 Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
@@
 These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density.
-Moreover both stars have existing semi-empirical 1-D chromospheric and wind models which we directly test the validity of in this paper.
+Moreover both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
 
@@
 	\colhead{(GHz)}                        		&
-	\colhead{Antennas\tablenotemark{b}}         &
+	\colhead{Antennae\tablenotemark{b}}         &
 	\colhead{Calibrator}		}
@@
 \enddata
-\tablenotetext{a}{Central frequency of used bandpass.}
-\tablenotetext{b}{Number of available antennas remaining after flagging.}
+\tablenotetext{a}{Central frequency of selected bandpass.}
+\tablenotetext{b}{Number of available antennae remaining after flagging.}
 \label{tab:tab2}
@@
 &4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (private communication) \\
-&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (private communication) \\
-&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (private communication) \\
+&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (priv. comm.) \\
+&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (priv. comm.) \\
+&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (priv. comm.) \\
 &15 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
@@
 Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circular data points and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D} which are shown in green.
-The red circular data points are all of the previous observations which were acquired sporadically over the past $\sim 25$ years.}
+The red circles are the previous observations which were acquired sporadically over the past $\sim 25$ years.}
 \label{fig:fig1}
@@
 All our new $\alpha$ Tau multi-frequency VLA observations (blue circular data points) were acquired in just two days in February 2011.
-The red circular data points are all of the previous observations which were acquired over many years.
+The red circles are the previous observations which were acquired over many years.
 The green line is an existing hybrid chromosphere and wind model for the star.}

### 2013-04-01 draft_03/draft.tex
1st upload of evla draft

--- 2013-04-01 draft_02/draft.tex
@@
 
-Although studies of wind-scattered UV and optical line profiles have provided clues to the mass-loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
+Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
 In the UV, the source function is very sensitive to electron temperature (i.e.
@@
 Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
+Mass Loss Rate (M$_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
 Wind Temperature (K)		& $\sim 10,000$  & $< 10,000$  \\
@@
 \enddata
-\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}.}
+\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}. Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
 
@@
 &4.9  & 1984 Mar 17 & $0.24 \pm 0.05$ & \cite{1986AJ.....91..602D} \\
-&15 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
+&15.0 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
 &22.5  & 1999 Jan 06  & $ 1.7 \pm 0.2$ & \cite{2011AA...533A.107D} \\
@@
 &43.3  & 2004 Jan 25 & $ 3.34 \pm 0.08$ & \cite{2011AA...533A.107D} \\
-&86  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
+&86.0  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
 &108.4  & 1997 Nov - 2000 Jun & $ 20.09 \pm 0.69$ & \cite{2005AJ....129.2836C} \\
 &217.8 & 1997 Nov - 2000 Jun  & $ 83.5 \pm 1.71$ & \cite{2005AJ....129.2836C} \\
-&250  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
+&250.0  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
 \hline
@@
 &14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (priv. comm.) \\
-&15 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
+&15.0 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
 &108.4  & 1997 Nov - 2000 Dec & $ 13.97 \pm 1.46$ & \cite{2005AJ....129.2836C} \\
-&217.82 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
-&250  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
+&217.8 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
+&250.0  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
 \enddata
@@
 \section{DISCUSSION}
-\subsection{Spectral Energy Distribution of $\alpha$ Boo} \label{disc1}
-The first definite detection of a single red giant at centimeter wavelengths was of $\beta$ Gem by \cite{1983ApJ...274L..77D}.
-Included in this study was a probable $3\sigma$ detection of $\alpha$ Boo and since then there has been only a small number of sporadic centimeter and millimeter observations of the star.
+\subsection{Results Versus Previous Observations} \label{disc1}
+Prior to and during the early operation of the VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g.
+\citealt{1981ApJ...245L..71B}).
+These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were false (e.g.
+\citealt{1992MNRAS.254....1B}).
+The first definitive detection of thermal free-free emission from a single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}.
+Since then there has been a modest number of sporadic centimeter and millimeter observations of this star.
 In Table \ref{tab:tab3} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}.
-We also include in this figure the chromosphere and wind models of \cite{1985pssl.proc..351D} which were based on the International Ultraviolet Explorer (IUE) Mg II k emission line and the overlap between the two models are represented by the green shaded area.
+In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e.
+Q, K, Ku, and C).
+No Ku band receivers were available during the commissioning phase of the VLA in early 2011 so we can compare three of our detections with previous ones.
+
+Previous detections at 6 cm ranged from a 3$\sigma$ upper limit of 0.18 mJy to a 3$\sigma$ detection at 0.39 mJy.
+Our 6 cm value agrees to within $\sim$10$\%$ of the highest S/N (5$\sigma$) value of \cite{1986AJ.....91..602D}.
+There is no significant difference between our 1.3 cm value and that of \cite{2011AA...533A.107D}.
+There is however a notable difference in flux density values at 0.7 cm  where \cite{2011AA...533A.107D} report values that are lower than ours by over 40\%.
+Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars.
+Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values.
+Future high frequency VLA observations of $\alpha$ Boo will clarify this discrepancy at 0.7 cm but past detections at longer wavelengths appear to be in good agreement with our data.
+
+Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e.
+X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind.
+The lack of a Ku measurement means that we can only compare the previous 3 cm detection of Brown $\&$ Harper (1997) to ours.
+We find that there is no significant difference between the two.
+Interestingly however, Brown $\&$ Harper (1997) failed to detect $\alpha$ Tau at 6 cm but placed a 3$\sigma$ upper limit of 0.07 mJy on its emission.
+In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value.
+This hint of variability at long wavelengths can only again be confirmed with future high S/N observations.
+
+\subsection{Existing Atmospheric Models} \label{disc2}
+One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
+Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the the International Ultraviolet Explorer.
+Both of Drake's models predict the wind to reach its terminal velocity of 40 km s${}^{-1}$ at $\sim$ 2 R${}_{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$ 13 R${}_{\star}$ with a cooler region further out.
 At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e.
@@
 At low frequencies however, the models predict the wind to have constant velocity, ionization and temperature and thus the slope approaches the well known $\sim \nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-The paucity and, in some cases low S/N, of previous observations make it difficult to discern the validity of this model prior to our multi-frequency study of this star.
+The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
+Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz).
+At high frequencies our VLA data indicates a flux excess which is in agreement with previous higher frequency (i.e.
+mm-observations) observations.
+The  discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e.
+it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
+We will discuss these possibilities in the following sections.
 
-The peak flux density values listed in Table \ref{tab:tab3} for $\alpha$ Boo are also included in Figure \ref{fig:fig1} along with their $1\sigma$ rms errors.
-Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz).
-At low frequencies this discrepancy may indicate that we are still sampling a region of the wind where it is still accelerating (i.e.
-it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
-Our highest frequency data points indicate a flux excess which is in agreement with previous higher frequency (i.e.
-mm-observations) observations.
-One notable exception to this high frequency flux excess are the two 43 GHz observations of \cite{2011AA...533A.107D} which are lower than our values by over 40\%.
-Such a level of chromospheric viability seems very high and would be unexpected from such supposedly inactive stars.
-Another possibility for the difference in values  is that the longer cycle times used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values.
-Future high frequency observations may clarify this matter.
+In Figure \ref{fig:fig2} we plot the expected thermal radio continuum spectrum produced by the semi-empirical 1-D  chromospheric model of \cite{1999MNRAS.302...37M} embedded in the wind model of \cite{1998ApJ...503..396R}.
+The McMurry model includes a transition region and reaches a maximum temperature of 10$^{5}$ K at 1.2 R$_{\star}$.
+Beyond this we assume an outflow with a constant temperature of 8,000 K reaching a terminal velocity of 30 km s$^{-1}$ at 3 R$_{\star}$.
+The combination of these models predicts an excess of radio emission at high frequencies (i.e.
+$>$ 30 GHz) but does a good job in reproducing the VLA fluxes below 30 GHz.
+The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxes confirm that this model predicts a flux excess at high frequencies.
+One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
+This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors (i.e.
+a thermally bifurcated CO-mosphere).
+For $\alpha$ Boo there is a strong hint that the transition frequency between wind and chromosphere occurs  at about 8.5 GHz but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
+There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.
 
-\subsection{Spectral Energy Distribution of $\alpha$ Tau} \label{disc2}
-\\
-d
-\\
-\\
-zz
-\\
-\\
-\\
-\\
-d
-\\
-\\
-zz
-\\
-\\
-\\
-\\
-d
-\\
-\\
-zz
-\\
-\\
-\\
-\subsection{Contribution Functions?} \label{disc3}
-\subsection{Mass loss e.g. Drake & Linskey ?} \label{disc4}
-\subsection{Future Atmospheric Models e.g. Advection?} \label{disc5}
+We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2}.
+This model is based on a larger than now expected mass-loss rate for the star (i.e 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow.
+As the radio opacity is proportional to n$\rm{_{e}}$n$\rm{_{ion}}$ this model greatly over-predicts the actual radio flux density.
+The same result is to be expected from the Alfv\`{e}n wave model of $\alpha$ Boo \citep{1988AcA....38..107K}.
 
@@
 \caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz.
-Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circular data points and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D} which are shown in green.
-The red circles are the previous observations which were acquired sporadically over the past $\sim 25$ years.}
+Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
+The overlap between the two models are represented by the green shaded area.
+The red circles are previous observations which were acquired sporadically over the past $\sim 25$ years with the ``old" VLA, IRAM and BIMA.}
 \label{fig:fig1}
@@
 \caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz.
-All our new $\alpha$ Tau multi-frequency VLA observations (blue circular data points) were acquired in just two days in February 2011.
+All our new $\alpha$ Tau multi-frequency VLA observations (blue circles) were acquired in just two days in February 2011.
 The red circles are the previous observations which were acquired over many years.
@@
 \end{figure*}
+
+\subsection{Radio Spectral Indices from Mass Outflows} \label{disc3}
+For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($\rm{S}_{\nu} \propto \nu ^{\alpha}$).
+For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e.
+$\alpha = +2$), while for an optically thin homogeneous plasma $\alpha = -0.1$.
+However, the electron density in the mass outflow region of a star is not constant as a function of radius and usually varies by many orders of magnitude.
+It has been shown \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P} that the expected radio spectrum from such a mass outflow region varies as $\nu ^{0.6}$, where a spherically symmetric isothermal mass outflow with a uniform velocity is assumed.
+If we do not make the simplified assumption of an isothermal, constant velocity mass outflow but instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, where $p > 1.5$ then
+
+\begin{figure}
+\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
+\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit straight lines to their long wavelength flux densities and the resulting spectral indices.}
+\label{fig:fig3}
+\end{figure}
+
+\begin{equation}
+\alpha = \frac{4p -6.2 -0.6n}{2p-1-1.35n}.
+\label{eq:eq1}
+\end{equation}
+\citep[e.g.][]{1987ApJ...312..813S}.
+Thus, by assuming either a constant velocity (i.e.
+$p=2$) or an isothermal outflow (i.e.
+$n=0$), we can easily estimate the power-law decay of either the temperature or velocity profile, respectively.
+
+The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
+For $\alpha$ Boo a straight line with $S_{\nu} \propto \nu ^{1.05 \pm x}$ fits the four longest wavelength data points well.
+This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm.
+$\alpha$ Tau was found to have a larger spectral index and a straight line with $S_{\nu} \propto \nu ^{1.58 \pm x}$ best fitted the three longest wavelength data points.
+This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data provided by Brown \& Harper (priv.
+Comm.).
+These new spectral indices were then used in conjunction with Equation \ref{eq:eq1} to obtain the density and temperature coefficients listed in Table \ref{tab:tab5}.
+
+\begin{figure}
+\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig4.ps}
+\caption{Predicted effective radius (dashed lines) as a function of wavelength for $\alpha$ Boo and $\alpha$ Tau.
+Points corresponding to our long wavelength VLA measurements are also shown.
+At the same radio wavelengths the less ionized mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
+\label{fig:fig4}
+\end{figure}
+
+For an isothermal, constant velocity wind, Equation \ref{eq:eq1} implies $\alpha$ = 0.6.
+The fact that our derived values are substantially larger implies at least one of the assumptions regarding the wind's properties are false.
+A common explanation in the literature for spectral indices larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from.
+If this is also the case here, then the density obeys a power-law falloff with coefficients listed in column 3 of Table \ref{tab:tab5}.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at  long VLA wavelengths (i.e.
+between 6 and 20 cm) this assumption might be false and we may indeed be sampling the wind very close to its terminal velocity.
+
+\begin{deluxetable}{cccc}
+\tabletypesize{\scriptsize}
+\tablecaption{Radio Spectral Indices for $\alpha$ Boo and $\alpha$ Tau along with their density and temperature coefficients.}
+\tablehead{	\colhead{}		       				& 
+			\colhead{Spectral}				&
+			\colhead{Density}				&
+			\colhead{Temperature}				\\
+			\colhead{Star}		       				& 
+			\colhead{index $\alpha$ }				&
+			\colhead{coefficient $p$ }				&
+			\colhead{coefficient $n$ }				}
+
+\startdata
+$\alpha$ Boo				& 1.05  & 2.71 & 1.65\\
+$\alpha$ Tau			& 1.58 & 5.50 & 1.92
+\enddata
+\label{tab:tab5}
+\end{deluxetable}
+
+To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength using the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
+We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at any wavelength emanates from a surface at effective optical depth $\tau _{\rm{eff}}=$1/3.
+Since the radio free-free opacity increases at longer wavelengths (i.e.
+$\kappa \propto \lambda ^{2.1}$) the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
+This implies that the effective radius (i.e.
+the radius where $\tau = \tau _{\rm{eff}}$) will increase with longer wavelengths and will be greater for outflows with higher ionization densities as $\tau \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
+
+The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig4}.
+At 6, 13, and 20 cm the effective radius of $\alpha$ Boo is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ while is only $\sim 1.1 R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
+\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind does not reach its terminal velocity until 3 $R_{\star}?$ while the transition region in the model of \cite{1999MNRAS.302...37M} begins at 1.2 $R_{\star}$, so it appears highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
+For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$ 2 $R_{\star}$ so based on this model, our longest VLA measurements probable sample its wind at (or very close to) its terminal velocity.
+Our spectral index would then indicate that the wind is cooling as it expands with a constant velocity and has a temperature coefficient of 1.65.
+
+\subsection{Analytical Advection Model for $\alpha$ Boo's Wind} \label{disc4}
+A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths as clearly shown in Figure \ref{fig:fig1}.
+If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the model.
+The main mechanism for this cooling would be wind expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
+To investigate this possibility further we adjusted the existing model to include a temperature power-law falloff of the form
+\begin{equation}
+T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{1.65},
+\label{eq:eq2}
+\end{equation}
+where $r_{1}$ is just an arbitrary distance from the star and the temperature coefficient is that obtained from our new VLA data (see Table \ref{tab:tab5}).
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_H$.
+In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
+\begin{itemize}
+\item We assume a conserved mass outflow i.e.
+$n_{H}(r)=C/r^2$ where $n_{H}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
+\item We assume that all ionization processes cease.
+\item We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha ^{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
+\item We assume a constant heavy ion fraction, $x_{hi}=10^{-4}$.
+\end{itemize}
+Using these assumptions it can be shown that 
+\begin{equation}
+x_H(r)= \frac{x_{H}(r_1)x_{hi}e^{-I}}{x_{hi}+x_{H}(r_1)(1 - e^{-I})}
+\label{eq:eq3}
+\end{equation}
+where
+\begin{equation}
+I = 2.38 \times 10^{-3} \left[\left( \frac{r_{1}}{r}\right)^{-0.19} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
+\label{eq:eq4}
+\end{equation}
+If we alter the existing Drake model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile given by Equation \ref{eq:eq2} and a density profile governed by Equation \ref{eq:eq3} beyond 2.3 $R_{\star}$, then we get a  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+
+Encouraging as it is that such a simple analytical model can reproduce values close to the observed radio fluxes at long wavelengths, it must be stressed that this \textit{hybrid} model is just a first order approximation.
+It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$ 3 cm and therefore a new atmospheric model is still required that can reproduce all the observed fluxes.
+To do so, the non-trivial task of simultaneously solving the non-local radiative transfer equation and atomic rate equations which include advection will be required.
+
+\subsection{Ionized Mass Loss Rates} \label{disc5}
 

### 2013-04-01 draft_04/draft.tex
1st upload of evla draft

--- 2013-04-01 draft_03/draft.tex
@@
 \usepackage{natbib}
+\usepackage{amsmath}
 \bibliographystyle{apj}
@@
 
-\shorttitle{Radio Emission of Dust-free Red Giant Mass Outflows}
+\shorttitle{Radio Emission Studies of Dust-free Red Giants}
 \shortauthors{O'Gorman et al.}
@@
 
-\title{Multi-frequency Radio Continuum Emission of Dust-free Red Giant Mass Outflows}
+\title{Multi-wavelength Radio Continuum Emission Studies of Dust-free Red Giants}
 
-\author{Eamon O'Gorman\altaffilmark{1}, Graham M. Harper\altaffilmark{1}, Alexander Brown\altaffilmark{2}, Anita M.S. Richards\altaffilmark{3}, and Stephen Drake\altaffilmark{4}}
+\author{Eamon O'Gorman\altaffilmark{1}, Graham M. Harper\altaffilmark{1}, Alexander Brown\altaffilmark{2}, Stephen Drake\altaffilmark{3}, and Anita M.S. Richards\altaffilmark{4}}
 \altaffiltext{1}{School of Physics, Trinity College Dublin, Dublin 2, Ireland}
 \altaffiltext{2}{Center for Astrophysics and Space Astronomy, University of Colorado, 389 UCB, Boulder, CO 80309, USA}
-\altaffiltext{3}{Jodrell Bank Centre for Astrophysics, School of Physics and Astronomy, University of Manchester, Manchester M13 9PL, UK}
-\altaffiltext{4}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
+\altaffiltext{3}{NASA Goddard Space Flight Center, Greenbelt, MD 20771, USA}
+\altaffiltext{4}{Jodrell Bank Centre for Astrophysics, School of Physics and Astronomy, University of Manchester, Manchester M13 9PL, UK}
 
@@
 
-Multi-frequency centimeter continuum observations of non-dusty and molecule-free red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
+Multi-wavelength centimeter continuum observations of non-dusty red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
 These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements accumulated over many years.
-Here, we present multi-frequency Karl G.
-Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus and Aldebaran.
-Uniquely, these multi-frequency observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
-We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for Arcturus.
+Here, we present multi-wavelength Karl G.
+Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
+Uniquely, these multi-wavelength observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
+We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
 This is the first time single (non-binary) luminosity class III red giants have been observed at such long continuum wavelengths.
-These measurements sample the outermost layers where the wind velocity is approaching its terminal value and the ionization balance is  becoming \textit{frozen-in}, and are therefore important empirical inputs for future wind models.
+These long wavelength flux density measurements sample the outer layers of the stars atmosphere where the wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
+As a result, they are important empirical inputs for future atmospheric models.
 We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models.
 The marked deviations between our data and existing semi-empirical models highlight the need for new atmospheric models to be developed.
+The derived spectral indices are discussed in relation to the possible properties of the stellar atmospheres and a simple analytical atmospheric model is developed for $\alpha$ Boo which is in close agreement to the observed flux densities at long wavelengths.
 
@@
 $ \kappa \propto \lambda ^{2.1}$) so the longer wavelengths sample the extended layers of the stars atmosphere thus essentially providing us with spatial information about the star's mass outflow region.
-The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes frozen-in at these radii.
+The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at these radii due to advection.
 Furthermore, it is these outer extended regions of the star's atmosphere that contribute to the commonly seen P Cygni line profiles in the UV.
@@
 \citealt{1981ApJ...248.1043C}).
-In fact, using the ``old'' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types.
+In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types.
 
@@
 These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
-These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density.
+These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
 Moreover both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
@@
 Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
+Distance (pc)	& 20.43  & 11.26 \\
 Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
@@
 \enddata
-\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}. Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
+\tablecomments{Effective temperatures and photospheric diameters are from \cite{1993AA...270..315D}.
+Distances are from \cite{2007A&A...474..653V}.
+Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
 
@@
 Each sub-band had sixty-four channels of width 2 MHz and four polarization products (RR, LL, RL, LR).
-For the S and L band observations in 2012, the 1-2 GHz and 2-4 GHz frequency ranges were both divided into 16 sub-bands, each with sixty-four channels.
+For the S and L-band observations in 2012, the 1-2 GHz and 2-4 GHz frequency ranges were both divided into 16 sub-bands, each with sixty-four channels.
 The channel width was 2 and 1 MHz for S and L-band, respectively.
@@
 The data were flagged, calibrated, and imaged within the Common Astronomical Software Application  \cite[CASA;][]{2007ASPC..376..127M} package.
-Data deemed to be bad by the VLA online system were flagged, as were pure zeros, non-operational antennas antennas, dummy scans at the beginning of each track, and poorly performing antennas.
+Data deemed to be bad by the VLA online system were flagged, as were pure zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
 Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged (a process known as \textit{quacking}).
@@
 %\tablewidth{0pt} 
-\tablecaption{VLA Fluxes of $\alpha$ Boo and $\alpha$ Tau}
+\tablecaption{VLA Fluxe Densities of $\alpha$ Boo and $\alpha$ Tau}
 \tablehead{\colhead{}		            &
@@
 			\colhead{Frequency\tablenotemark{a}}&
-			\colhead{Peak Flux}					&
-          	\colhead{Integrated Flux} 			&
+			\colhead{Peak $F_{\nu}$}					&
+          	\colhead{Integrated $F_{\nu}$} 			&
           	\colhead{\textit{Imfit} Integrated}	&
@@
     \colhead{(mJy)}		                		& 
-	\colhead{Flux (mJy)}                        		& 
+	\colhead{$F_{\nu}$ (\rm{mJy})}                        		& 
 	\colhead{(Jy beam^{-1})}         					&
@@
 Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data.
-The flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here.
+The flux densities of the targets in each sub-bands were found to be the same within their uncertainties so we do not present these values here.
 Instead we give the values from the radio maps produced by concatenating the two sub-bands.
@@
 Surprisingly we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
-We obtain good detections ($>5\sigma$) of the star for both epochs at 3 GHz (S-band) and the peak flux densities agree within their uncertainties.
+We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
 We can therefore safely assume that the 1.5 GHz (L-band) flux has not changed significantly over that period either, and so can safely be included in any analysis.
 The map at L-band was highly contaminated by the emission of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level.
-There is a slight positional offset of $1\arcsec$ between the position of the peak flux for $\alpha$ Boo at 1.5 and 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
+There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
 However, this is less than a quarter of the 1.5 GHz synthesized beam and considering that the $4\sigma$ contours overlap, we feel that it is highly unlikely that both sources are not $\alpha$ Boo.
@@
 The target field at all frequencies was free from strong serendipitous radio sources and thus the final images were free of the sidelobe contamination that were present in the low frequency $\alpha$ Boo images.
-$\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had a flux of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively.
+$\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had flux densities of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively.
 Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
@@
 %\tablewidth{0pt} 
-\tablecaption{Compilation of Previous $\alpha$ Boo and $\alpha$ Tau Observations ($\le 250$ GHz)}
+\tablecaption{Compilation of Previous Radio Observations of $\alpha$ Boo and $\alpha$ Tau ($\nu \le 250$ GHz)}
 \tablehead{							            &
@@
 \subsection{Results Versus Previous Observations} \label{disc1}
-Prior to and during the early operation of the VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g.
+Prior to and during the early operation of the `old' VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g.
 \citealt{1981ApJ...245L..71B}).
@@
 Since then there has been a modest number of sporadic centimeter and millimeter observations of this star.
-In Table \ref{tab:tab3} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}.
+In Table \ref{tab:tab4} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}.
 In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e.
@@
 Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the the International Ultraviolet Explorer.
-Both of Drake's models predict the wind to reach its terminal velocity of 40 km s${}^{-1}$ at $\sim$ 2 R${}_{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$ 13 R${}_{\star}$ with a cooler region further out.
+Both of Drake's models predict the wind to reach a terminal velocity of 40 km s${}^{-1}$ at $\sim$ 2 R${}_{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$ 13 R${}_{\star}$ with a cooler region further out.
 At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e.
@@
 Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz).
-At high frequencies our VLA data indicates a flux excess which is in agreement with previous higher frequency (i.e.
-mm-observations) observations.
+At high frequencies our VLA data indicates a flux excess which is in agreement with previous mm-observations.
 The  discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e.
@@
 Beyond this we assume an outflow with a constant temperature of 8,000 K reaching a terminal velocity of 30 km s$^{-1}$ at 3 R$_{\star}$.
-The combination of these models predicts an excess of radio emission at high frequencies (i.e.
+The combination of these atmospheric models result in a predicted excess of radio emission at high frequencies (i.e.
 $>$ 30 GHz) but does a good job in reproducing the VLA fluxes below 30 GHz.
-The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxes confirm that this model predicts a flux excess at high frequencies.
+The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxes confirm that this model predicts a flux excess at even higher frequencies.
 One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
@@
 a thermally bifurcated CO-mosphere).
-For $\alpha$ Boo there is a strong hint that the transition frequency between wind and chromosphere occurs  at about 8.5 GHz but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
+For $\alpha$ Boo there is a hint that the transition frequency between wind and chromosphere occurs  at about 8.5 GHz due to the change of slope but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
 There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.
 
-We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2}.
-This model is based on a larger than now expected mass-loss rate for the star (i.e 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow.
-As the radio opacity is proportional to n$\rm{_{e}}$n$\rm{_{ion}}$ this model greatly over-predicts the actual radio flux density.
+We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
+This model is based on a larger than now expected mass loss rate for the star (i.e 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow.
+As the radio opacity is proportional to n$\rm{_{e}}$n$\rm{_{ion}}$ this model greatly over estimates the actual radio flux density at all VLA wavelengths.
 The same result is to be expected from the Alfv\`{e}n wave model of $\alpha$ Boo \citep{1988AcA....38..107K}.
@@
 \caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz.
-Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
+Our new multi-wavelength VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and are in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
 The overlap between the two models are represented by the green shaded area.
-The red circles are previous observations which were acquired sporadically over the past $\sim 25$ years with the ``old" VLA, IRAM and BIMA.}
+The red circles are previous observations which were acquired sporadically over the past $\sim 25$ years with the `old' VLA, IRAM and BIMA.
+The black line is the expected radio emission from the Drake model which undergoes rapid wind cooling at $\sim$ 2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
 \label{fig:fig1}
@@
 \caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz.
-All our new $\alpha$ Tau multi-frequency VLA observations (blue circles) were acquired in just two days in February 2011.
+All our new $\alpha$ Tau multi-wavelength VLA observations (blue circles) were acquired in just two days in February 2011.
 The red circles are the previous observations which were acquired over many years.
@@
 
-\subsection{Radio Spectral Indices from Mass Outflows} \label{disc3}
-For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($\rm{S}_{\nu} \propto \nu ^{\alpha}$).
+\subsection{Radio Spectral Indices} \label{disc:disc3}
+For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$).
 For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e.
@@
 It has been shown \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P} that the expected radio spectrum from such a mass outflow region varies as $\nu ^{0.6}$, where a spherically symmetric isothermal mass outflow with a uniform velocity is assumed.
-If we do not make the simplified assumption of an isothermal, constant velocity mass outflow but instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, where $p > 1.5$ then
+If we relax these assumptions and instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, where $p > 1.5$ then
 
@@
 \begin{equation}
-\alpha = \frac{4p -6.2 -0.6n}{2p-1-1.35n}.
+\alpha = \frac{4p -6.2 -0.6n}{2p-1-1.35n}
 \label{eq:eq1}
@@
 \citep[e.g.][]{1987ApJ...312..813S}.
+In doing this, we are assuming that the ionization fraction is constant throughout the outflow.
 Thus, by assuming either a constant velocity (i.e.
@@
 The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
-For $\alpha$ Boo a straight line with $S_{\nu} \propto \nu ^{1.05 \pm x}$ fits the four longest wavelength data points well.
+For $\alpha$ Boo a straight line with $F_{\nu} \propto \nu ^{1.05 \pm x}$ fits the four longest wavelength data points well.
 This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm.
@@
 The fact that our derived values are substantially larger implies at least one of the assumptions regarding the wind's properties are false.
-A common explanation in the literature for spectral indices larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from.
+A common explanation in the literature for spectral indices larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are ignored.
 If this is also the case here, then the density obeys a power-law falloff with coefficients listed in column 3 of Table \ref{tab:tab5}.
 This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at  long VLA wavelengths (i.e.
-between 6 and 20 cm) this assumption might be false and we may indeed be sampling the wind very close to its terminal velocity.
+between 6 and 20 cm) this assumption might be false and we may indeed be sampling the wind very close to or at its terminal velocity.
 
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Radio Spectral Indices for $\alpha$ Boo and $\alpha$ Tau along with their density and temperature coefficients.}
+\tablecaption{Radio Spectral Indices and Resulting Density and Temperature Coefficients.}
 \tablehead{	\colhead{}		       				& 
@@
 
-To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength using the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
+To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
 We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at any wavelength emanates from a surface at effective optical depth $\tau _{\rm{eff}}=$1/3.
@@
 The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig4}.
-At 6, 13, and 20 cm the effective radius of $\alpha$ Boo is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ while is only $\sim 1.1 R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
-\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind does not reach its terminal velocity until 3 $R_{\star}?$ while the transition region in the model of \cite{1999MNRAS.302...37M} begins at 1.2 $R_{\star}$, so it appears highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
+At 6, 13, and 20 cm the effective radius of $\alpha$ Boo is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ while is only $\sim$ 1.1 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
+\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind does not reach its terminal velocity until 3 $R_{\star}?$ while the transition region in the model of \cite{1999MNRAS.302...37M} begins at 1.2 $R_{\star}$, so it appears unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
 For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$ 2 $R_{\star}$ so based on this model, our longest VLA measurements probable sample its wind at (or very close to) its terminal velocity.
@@
 
-\subsection{Analytical Advection Model for $\alpha$ Boo's Wind} \label{disc4}
+\subsection{Analytical Advection Model for $\alpha$ Boo's Wind} \label{disc:disc4}
 A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths as clearly shown in Figure \ref{fig:fig1}.
@@
 where $r_{1}$ is just an arbitrary distance from the star and the temperature coefficient is that obtained from our new VLA data (see Table \ref{tab:tab5}).
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_H$.
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_\rm{H}$.
 In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
@@
 \item We assume a conserved mass outflow i.e.
-$n_{H}(r)=C/r^2$ where $n_{H}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+$n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
@@
 \item We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha ^{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
-\item We assume a constant heavy ion fraction, $x_{hi}=10^{-4}$.
+\item We assume a constant heavy ion fraction, $x_{\rm{hi}}=10^{-4}$.
 \end{itemize}
@@
 \begin{equation}
-x_H(r)= \frac{x_{H}(r_1)x_{hi}e^{-I}}{x_{hi}+x_{H}(r_1)(1 - e^{-I})}
+x_{\rm{H}}(r)= \frac{x_{\rm{H}}(r_1)x_{\rm{hi}}e^{-I}}{x_{\rm{hi}}+x_{\rm{H}}(r_1)(1 - e^{-I})}
 \label{eq:eq3}
@@
 \end{equation}
+\\
 If we alter the existing Drake model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile given by Equation \ref{eq:eq2} and a density profile governed by Equation \ref{eq:eq3} beyond 2.3 $R_{\star}$, then we get a  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
@@
 \subsection{Ionized Mass Loss Rates} \label{disc5}
+For a partially ionized outflow, such as that expected from $\alpha$ Boo and $\alpha$ Tau, the ionized mass loss rate can be estimated from the radio emission assuming a constant velocity, constant temperature, and constant ionization fraction and can be written as
+\begin{align}
+\dot{M}_{\rm{ion}} & \simeq 5.58 \times 10^{-14} \left(\frac{v_{\infty}}{\rm{km \  s^{-1}}}\right) \left(\frac{D}{\rm{pc}}\right)\left( \frac{F_{\nu}}{\rm{mJy}} \right)^{0.75} \nonumber \\
+ & \qquad \times \left( \frac{\lambda}{\rm{cm}} \right)^{0.45} \left( \frac{T_{\rm{e}}}{10^4 \rm{K}} \right)^{0.1} \ \dot{M}_{\odot} \ \rm{yr}^{-1} 
+\label{eq:5}
+\end{align}
+where $D$ is the distance and $v_{\infty}$ is the wind terminal velocity defined earlier in Table \ref{tab:tab1}.
+Using this expression, the ionized mass loss rates were derived for each of the long wavelength measurements for both stars and are listed in Table \ref{tab:tab5}.
+These values are based on the assumption of a $T_{\rm{e}} = 10^4 \ \rm{K}$  wind for both stars.
+
+\begin{deluxetable}{ccc}
+
+\tablecaption{Ionized mass loss rates for $\alpha$ Boo and $\alpha$ Tau.}
+\tablehead{	\colhead{Star}		       				& 
+			\colhead{Wavelength (cm)}				&
+			\colhead{$\rm{\dot{M}_{ion}}$ (M$_{\odot}$ yr$^{-1}$)}}
+
+\startdata
+$\alpha$ Boo				& 6.0  & 5.9 \times 10^{-11} \\
+							& 9.5  & 5.5 \times 10^{-11} \\
+							& 10.0  & 5.1 \times 10^{-11} \\
+							& 20.0  & 4.3 \times 10^{-11} \\
+$\alpha$ Tau				& 6.0  & \leq 8.2 \times 10^{-11} \\
+							& 9.5 & \leq 5.3 \times 10^{-11} 
+\enddata
+\label{tab:tab6}
+\end{deluxetable}
+
+We have have discussed in the previous sections that for $\alpha$ Boo, these long wavelengths sample the outer atmosphere of the star where the wind  is close to or has reached its terminal velocity and is beginning to cool due to gas expansion.
+In this case, these $\dot{M}_{\rm{ion}}$ values would be lower than those given in \ref{tab:tab6}.
+However, as $\dot{M}_{\rm{ion}}$  is only weakly dependent on $T_{\rm{e}}$ this makes only a small difference and amounts to about a 7\% increase in the ionized mass loss if the temperature is actually lower by 50\%.
+If the ionization balance is frozen-in in the regions of the outflow where these long wavelengths sample then the derived $\dot{M}_{\rm{ion}}$ should be the same  for these wavelengths.
+The decrease in $\dot{M}_{\rm{ion}}$ with longer wavelengths as seen in Table \ref{tab:tab6} is probably therefore due to a combination of lower temperatures and lower ionization fractions further out in the atmosphere.
+The ionized mass loss rates for $\alpha$ Tau given in Table \ref{tab:tab6} are derived assuming the radio emission emanates from the outer atmosphere where the wind has reached its terminal velocity.
+As discussed in Section \ref{disc:disc3} the longest wavelengths are still sampling the acceleration zone and thus these ionized mass loss rates are just upper limits.
 

### 2013-04-01 draft_06/draft.tex
added draft_06

--- 2013-04-01 draft_04/draft.tex
@@
 Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Uniquely, these multi-wavelength observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
+Uniquely, our observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
 We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
@@
 As a result, they are important empirical inputs for future atmospheric models.
-We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models.
+We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models based on ultraviolet data.
 The marked deviations between our data and existing semi-empirical models highlight the need for new atmospheric models to be developed.
-The derived spectral indices are discussed in relation to the possible properties of the stellar atmospheres and a simple analytical atmospheric model is developed for $\alpha$ Boo which is in close agreement to the observed flux densities at long wavelengths.
+The derived spectral indices are discussed in relation to the possible properties of the stellar atmospheres and a simple analytical atmospheric model is developed for $\alpha$ Boo's outer atmosphere which is in good agreement with our new long wavelength flux densities.
 
@@
 Mass loss from late-type evolved stars plays a crucial role in both stellar and galactic evolution and ultimately provides part of of the material required for the next generation of stars and planets.
-Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery (clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g.
-\citealt{2009AIPC.1094..267C}).
+Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g.,
+\citealt{2009AIPC.1094..267C}].
 There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
-Optical and ultraviolet observations reveal an absence of hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.][]{1979ApJ...229L..27L,1981ApJ...250..293A}.
+Optical and ultraviolet observations reveal an absence of hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.,][]{1979ApJ...229L..27L,1981ApJ...250..293A}.
 
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function is very sensitive to electron temperature (i.e.
-$S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value.
-At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e.
-$S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure.
+In the UV, the source function is very sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value.
+At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure.
 It is this value that controls the atomic level populations and ionization that feed into UV spectroscopic analyses.
@@
 
-In the cm-radio regime the radio opacity strongly increases with wavelength (i.e.
-$ \kappa \propto \lambda ^{2.1}$) so the longer wavelengths sample the extended layers of the stars atmosphere thus essentially providing us with spatial information about the star's mass outflow region.
+In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of the stars atmosphere, thus essentially providing us with spatial information about the star's mass outflow region.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at these radii due to advection.
@@
 Thus, centimeter radio continuum observations can provide a test of models based on these UV profiles.
-In this paper we directly compare our new Karl G.
+In this paper we directly compare our new NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
 Jansky Very Large Array (VLA) observations with atmospheric models derived from UV analysis.
@@
 
-Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the symbiotic and $\zeta$ Aurigae systems (e.g.
-\citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
+Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the symbiotic and $\zeta$ Aurigae systems (e.g., \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
 Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
-For example, the orbital separation is often within the wind acceleration region and one could expect wind accretion and flow perturbations to be present (e.g.
-\citealt{1981ApJ...248.1043C}).
-In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types.
+For example, the orbital separation is often within the wind acceleration region and one could expect flow perturbations to be present (e.g., \citealt{1981ApJ...248.1043C}).
+In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
 
@@
 These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
-Moreover both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
+Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
 
@@
 Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
-Distance (pc)	& 20.43  & 11.26 \\
 Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
-Mass Loss Rate (M$_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
-Wind Temperature (K)		& $\sim 10,000$  & $< 10,000$  \\
-Wind Terminal Velocity & $\sim$ 40 km s$^{-1}$ & $\sim$ 30 km s$^{-1}$ \\
+Distance (pc)	& $11.3 \pm 0.1$ & $20.4 \pm 0.3$\\
+Radius ($R_{\odot}$)	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
+Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
+Wind Temperature (K)		& $\sim10,000$  & $< 10,000$  \\
+Wind Terminal Velocity & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
 Semi-empirical model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
 \enddata
-\tablecomments{Effective temperatures and photospheric diameters are from \cite{1993AA...270..315D}.
+\tablecomments{Effective temperatures and photospheric angular diameters are from \cite{1993AA...270..315D}.
 Distances are from \cite{2007A&A...474..653V}.
@@
 All scheduling blocks (SBs) were kept to $\le$\,2.5 hours of duration to improve their likelihood of being scheduled.
-For the high frequency observations (i.e.
-Q, Ka, and K-bands) we used the \textit{fast switching} technique which consisted of rapidly alternating observations of the target source and a nearby unresolved phase calibrator.
+For the high frequency observations (i.e., Q, Ka, and K-bands) we used the \textit{fast switching} technique which consisted of rapidly alternating observations of the target source and a nearby unresolved phase calibrator.
 The total cycle times for the Q, Ka, and K-band observations were 160, 230, and 290 s, respectively.
@@
 Data deemed to be bad by the VLA online system were flagged, as were pure zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
-Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged (a process known as \textit{quacking}).
+Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged.
 For the 2011 low frequency data the two sub-bands were centered at relatively radio frequency interference (RFI) free regions of the bandpass and only a very small amount of RFI had to be flagged.
-The 2012 wide-band data was initially Hanning smoothed (combining adjacent frequency channels with weights 0.25, 0.5, and 0.25) to suppress Gibbs ringing.
+The 2012 wide-band data were initially Hanning smoothed (combining adjacent frequency channels with weights 0.25, 0.5, and 0.25) to suppress Gibbs ringing.
 We manually flagged entire sub-bands that were badly contaminated with RFI.
@@
 
-Three different methods were used to calculate the flux density from the unresolved target sources in each image:
-\begin{enumerate}
-\item by taking the peak pixel value from the source
-\item by manually integrating the flux density around the source
-\item by fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
-\end{enumerate}
+In each image the flux density from the unresolved target source was calculated by, 1) taking the peak pixel value from the source, 2) manually integrating the flux density around the source, and 3) fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
 Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}.
-We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies.
+We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies \citep{2013ApJS..204...19P}.
 
@@
 \enddata
-\tablenotetext{a}{Frequency of final image produced using \textit{clean}'s multi-frequency synthesis imaging mode.}
+\tablenotetext{a}{Frequency of the final image produced using the multi-frequency synthesis imaging mode within CASA's \textit{clean} task.}
 \label{tab:tab3}
@@
 Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data.
-The flux densities of the targets in each sub-bands were found to be the same within their uncertainties so we do not present these values here.
+At each other frequency, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here.
 Instead we give the values from the radio maps produced by concatenating the two sub-bands.
@@
 The lower frequencies maps were contaminated by the emission of a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
-This source was reported by \cite{1986AJ.....91..602D} and their flux of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index of -1.4 and its flux reaches  80.3 mJy at 1.6 GHz.
+This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
+We find the source to have a spectral index of -1.4 and reaches 80.3 mJy at 1.6 GHz.
 Surprisingly we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
 We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
-We can therefore safely assume that the 1.5 GHz (L-band) flux has not changed significantly over that period either, and so can safely be included in any analysis.
-The map at L-band was highly contaminated by the emission of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level.
+We can therefore safely assume that the 1.5 GHz (L-band) flux density has not changed significantly over that period either, and so can safely be included in any analysis.
+The map at L-band was highly contaminated by the sidelobes of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level.
 There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
@@
 We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density.
-As this is a weak detection we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may introduce further errors \citep{1999ASPC..180.....T}.
+As this is a weak detection we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may introduce additional errors \citep{1999ASPC..180.....T}.
 
@@
 &4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (priv. comm.) \\
-&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (priv. comm.) \\
-&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (priv. comm.) \\
+&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& \cite{2007ApJ...655..946W} \\
+&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& \cite{2007ApJ...655..946W} \\
+&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& \cite{2007ApJ...655..946W} \\
 &15.0 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
@@
 \subsection{Results Versus Previous Observations} \label{disc1}
-Prior to and during the early operation of the `old' VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g.
-\citealt{1981ApJ...245L..71B}).
-These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were false (e.g.
-\citealt{1992MNRAS.254....1B}).
-The first definitive detection of thermal free-free emission from a single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}.
+Prior to and during the early operation of the `old' VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g., \citealt{1981ApJ...245L..71B}).
+These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were false (e.g., \citealt{1992MNRAS.254....1B}).
+The first definitive detection of thermal free-free emission from a luminosity class III single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}.
 Since then there has been a modest number of sporadic centimeter and millimeter observations of this star.
 In Table \ref{tab:tab4} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}.
-In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e.
-Q, K, Ku, and C).
+In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e., Q, K, Ku, and C).
 No Ku band receivers were available during the commissioning phase of the VLA in early 2011 so we can compare three of our detections with previous ones.
 
-Previous detections at 6 cm ranged from a 3$\sigma$ upper limit of 0.18 mJy to a 3$\sigma$ detection at 0.39 mJy.
+Previous detections of $\alpha$ Boo at 6 cm ranged from a 3$\sigma$ upper limit of 0.18 mJy to a 3$\sigma$ detection at 0.39 mJy.
 Our 6 cm value agrees to within $\sim$10$\%$ of the highest S/N (5$\sigma$) value of \cite{1986AJ.....91..602D}.
@@
 
-Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e.
-X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind.
+Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind.
 The lack of a Ku measurement means that we can only compare the previous 3 cm detection of Brown $\&$ Harper (1997) to ours.
 We find that there is no significant difference between the two.
-Interestingly however, Brown $\&$ Harper (1997) failed to detect $\alpha$ Tau at 6 cm but placed a 3$\sigma$ upper limit of 0.07 mJy on its emission.
+Interestingly however, Brown $\&$ Harper (1997; priv.
+comm.) failed to detect $\alpha$ Tau at 6 cm but placed a 3$\sigma$ upper limit of 0.07 mJy on its emission.
 In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value.
@@
 \subsection{Existing Atmospheric Models} \label{disc2}
+\textbf{GMH: A few words on Radspec code.}
+
 One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
 Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the the International Ultraviolet Explorer.
-Both of Drake's models predict the wind to reach a terminal velocity of 40 km s${}^{-1}$ at $\sim$ 2 R${}_{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$ 13 R${}_{\star}$ with a cooler region further out.
-At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e.
-$\sim \nu ^{2}$) as a result of the small density scale heights close to the star.
-At low frequencies however, the models predict the wind to have constant velocity, ionization and temperature and thus the slope approaches the well known $\sim \nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of 40 km s${}^{-1}$ at $\sim$2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$13 $R _{\star}$ with a cooler region further out.
+At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small density scale heights close to the star.
+At low frequencies however, where the models predict the wind to have constant velocity, ionization and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
 The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
-Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz).
+Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$8 GHz and above $\sim$25 GHz).
 At high frequencies our VLA data indicates a flux excess which is in agreement with previous mm-observations.
-The  discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e.
-it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
+The  discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e., it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
 We will discuss these possibilities in the following sections.
-
-In Figure \ref{fig:fig2} we plot the expected thermal radio continuum spectrum produced by the semi-empirical 1-D  chromospheric model of \cite{1999MNRAS.302...37M} embedded in the wind model of \cite{1998ApJ...503..396R}.
-The McMurry model includes a transition region and reaches a maximum temperature of 10$^{5}$ K at 1.2 R$_{\star}$.
-Beyond this we assume an outflow with a constant temperature of 8,000 K reaching a terminal velocity of 30 km s$^{-1}$ at 3 R$_{\star}$.
-The combination of these atmospheric models result in a predicted excess of radio emission at high frequencies (i.e.
-$>$ 30 GHz) but does a good job in reproducing the VLA fluxes below 30 GHz.
-The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxes confirm that this model predicts a flux excess at even higher frequencies.
-One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
-This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors (i.e.
-a thermally bifurcated CO-mosphere).
-For $\alpha$ Boo there is a hint that the transition frequency between wind and chromosphere occurs  at about 8.5 GHz due to the change of slope but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
-There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.
-
-We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
-This model is based on a larger than now expected mass loss rate for the star (i.e 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow.
-As the radio opacity is proportional to n$\rm{_{e}}$n$\rm{_{ion}}$ this model greatly over estimates the actual radio flux density at all VLA wavelengths.
-The same result is to be expected from the Alfv\`{e}n wave model of $\alpha$ Boo \citep{1988AcA....38..107K}.
 
@@
 \\
-\caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz.
-Our new multi-wavelength VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and are in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
+\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz.
+Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and are in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
 The overlap between the two models are represented by the green shaded area.
-The red circles are previous observations which were acquired sporadically over the past $\sim 25$ years with the `old' VLA, IRAM and BIMA.
-The black line is the expected radio emission from the Drake model which undergoes rapid wind cooling at $\sim$ 2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
+The red triangles are previous observations which were acquired sporadically over the past $\sim25$ years with the `old' VLA, IRAM and BIMA.
+The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
 \label{fig:fig1}
@@
 \\
-\caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz.
-All our new $\alpha$ Tau multi-wavelength VLA observations (blue circles) were acquired in just two days in February 2011.
-The red circles are the previous observations which were acquired over many years.
-The green line is an existing hybrid chromosphere and wind model for the star.}
+\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
+All our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
+The red triangles are the previous radio observations of the star which were acquired over many years.The green line is the expected radio emission from the current hybrid chromosphere and wind model while the dashed  green line is the expected radio emission from a theoretical Alfv\`en wave driven model atmosphere.}
 \label{fig:fig2}
@@
 
+In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromospheric model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
+The McMurry model includes a transition region and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
+Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value by 3 $R_{\star}$.
+We assume the wind to have a constant temperature of 8,000 K and have a constant ionization fraction, $x_{e}$, of 0.01 throughout.
+The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $>$ 30 GHz) but does a good job in reproducing the VLA flux densities below 30 GHz.
+The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxe densities confirm that this model predicts a flux excess at even higher frequencies.
+One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
+This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere.
+For $\alpha$ Boo there is a hint that the transition frequency between wind and chromosphere occurs at about 8.5 GHz due to the change of slope but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
+There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.
+
+We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
+This model is based on a larger than now expected mass loss rate for the star (i.e., 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow with $v_{\infty} \approx 115$ km s$^{-1}$.
+As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$ this model greatly overestimates the actual radio flux density at all VLA wavelengths.
+The same result is to be expected from the Alfv\`{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger than now expected mass loss rates and outflow velocities.
+
 \subsection{Radio Spectral Indices} \label{disc:disc3}
 For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$).
-For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e.
-$\alpha = +2$), while for an optically thin homogeneous plasma $\alpha = -0.1$.
-However, the electron density in the mass outflow region of a star is not constant as a function of radius and usually varies by many orders of magnitude.
-It has been shown \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P} that the expected radio spectrum from such a mass outflow region varies as $\nu ^{0.6}$, where a spherically symmetric isothermal mass outflow with a uniform velocity is assumed.
-If we relax these assumptions and instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, where $p > 1.5$ then
+For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), while for an optically thin plasma $\alpha = -0.1$.
+However, the electron density in the mass outflow region of a star is not constant as a function of radius and varies by many orders of magnitude.
+It can be shown that the expected radio spectrum from an isothermal spherically symmetric steady flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
 
@@
 \end{equation}
-\citep[e.g.][]{1987ApJ...312..813S}.
-In doing this, we are assuming that the ionization fraction is constant throughout the outflow.
-Thus, by assuming either a constant velocity (i.e.
-$p=2$) or an isothermal outflow (i.e.
-$n=0$), we can easily estimate the power-law decay of either the temperature or velocity profile, respectively.
+\citep[e.g.,][]{1987ApJ...312..813S}.
+Here $p > 1.5$, otherwise we are in the optically thin regime.
+Equation \ref{eq:eq1} is also only valid if the ionization fraction is constant throughout the outflow.
+By making these assumptions and assuming either a constant velocity (i.e., $p=2$) or an isothermal outflow (i.e., $n=0$), we can easily estimate the power-law decay of either the temperature or velocity profile, respectively.
 
 The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
-For $\alpha$ Boo a straight line with $F_{\nu} \propto \nu ^{1.05 \pm x}$ fits the four longest wavelength data points well.
+For $\alpha$ Boo a straight line with $F_{\nu} \propto \nu ^{1.05 \pm 0.05}$ fits the four longest wavelength data points well.
 This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm.
-$\alpha$ Tau was found to have a larger spectral index and a straight line with $S_{\nu} \propto \nu ^{1.58 \pm x}$ best fitted the three longest wavelength data points.
-This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data provided by Brown \& Harper (priv.
-Comm.).
-These new spectral indices were then used in conjunction with Equation \ref{eq:eq1} to obtain the density and temperature coefficients listed in Table \ref{tab:tab5}.
+$\alpha$ Tau was found to have a larger spectral index and a straight line with $S_{\nu} \propto \nu ^{1.58 \pm 0.25}$ best fitted the three longest wavelength data points.
+This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data given in \cite{2007ApJ...655..946W}.
+It should be emphasized that the spectral index for both stars is steeper than that expected for an isothermal spherically symmetric steady flow.
 
 \begin{figure}
-\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig4.ps}
+\includegraphics[trim = 0mm 10mm 0mm 20mm, clip,scale=0.385,angle=90]{fig4.ps}
+\caption{The variation of density and temperature coefficients for the empirically derived spectral indices.
+The density coefficients for an isothermal flow along with the temperature coefficients for a constant outflow velocity are also shown for both stars.}
+\label{fig:fig4}
+\end{figure}
+
+Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that describe their outflow.
+The degree of variation of these coefficients with respect to one another is shown in Figure \ref{fig:fig4}.
+A common explanation in the literature for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are usually ignored.
+If we too make this assumption then the density coefficients are 2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) this assumption may be false and we may indeed be sampling the wind very close to or at its terminal velocity.
+
+\begin{figure}
+\includegraphics[trim = 5mm 0mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
 \caption{Predicted effective radius (dashed lines) as a function of wavelength for $\alpha$ Boo and $\alpha$ Tau.
@@
 At the same radio wavelengths the less ionized mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
-\label{fig:fig4}
+\label{fig:fig5}
 \end{figure}
 
-For an isothermal, constant velocity wind, Equation \ref{eq:eq1} implies $\alpha$ = 0.6.
-The fact that our derived values are substantially larger implies at least one of the assumptions regarding the wind's properties are false.
-A common explanation in the literature for spectral indices larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are ignored.
-If this is also the case here, then the density obeys a power-law falloff with coefficients listed in column 3 of Table \ref{tab:tab5}.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at  long VLA wavelengths (i.e.
-between 6 and 20 cm) this assumption might be false and we may indeed be sampling the wind very close to or at its terminal velocity.
-
-\begin{deluxetable}{cccc}
-\tabletypesize{\scriptsize}
-\tablecaption{Radio Spectral Indices and Resulting Density and Temperature Coefficients.}
-\tablehead{	\colhead{}		       				& 
-			\colhead{Spectral}				&
-			\colhead{Density}				&
-			\colhead{Temperature}				\\
-			\colhead{Star}		       				& 
-			\colhead{index $\alpha$ }				&
-			\colhead{coefficient $p$ }				&
-			\colhead{coefficient $n$ }				}
-
-\startdata
-$\alpha$ Boo				& 1.05  & 2.71 & 1.65\\
-$\alpha$ Tau			& 1.58 & 5.50 & 1.92
-\enddata
-\label{tab:tab5}
-\end{deluxetable}
-
 To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
-We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at any wavelength emanates from a surface at effective optical depth $\tau _{\rm{eff}}=$1/3.
-Since the radio free-free opacity increases at longer wavelengths (i.e.
-$\kappa \propto \lambda ^{2.1}$) the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
-This implies that the effective radius (i.e.
-the radius where $\tau = \tau _{\rm{eff}}$) will increase with longer wavelengths and will be greater for outflows with higher ionization densities as $\tau \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
+We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at each wavelength emanates from a surface at radial optical depth $\tau _{\rm{rad}}=$1/3.
+This is just the Eddington-Barbier relation for an extended atmosphere where emission from smaller optical depths gets added weight.
+Since the radio free-free opacity increases at longer wavelengths (i.e., $\kappa _{\lambda} \propto \lambda ^{2.1}$) the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
+This implies that the effective radius (i.e., the radius where $\tau _{\lambda} = \tau _{\rm{rad}}$) will increase with longer wavelengths and will be greater for outflows with higher ionization densities as $\tau _{\lambda} \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
 
 The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig4}.
-At 6, 13, and 20 cm the effective radius of $\alpha$ Boo is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ while is only $\sim$ 1.1 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
-\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind does not reach its terminal velocity until 3 $R_{\star}?$ while the transition region in the model of \cite{1999MNRAS.302...37M} begins at 1.2 $R_{\star}$, so it appears unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
-For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$ 2 $R_{\star}$ so based on this model, our longest VLA measurements probable sample its wind at (or very close to) its terminal velocity.
-Our spectral index would then indicate that the wind is cooling as it expands with a constant velocity and has a temperature coefficient of 1.65.
+At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.1 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
+\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$ so it is highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
+For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest VLA measurements probable sample the wind at, or very close to, its terminal velocity.
+Assuming this to be the case, Equation \ref{eq:eq1} then indicates that $\alpha$ Boo's steady outflow undergoes rapid cooling at a few stellar radii.
+The derived temperature coefficient of 1.65 points to a temperature power-law falloff exceeding that from a wind adiabatically cooling with no heat source (i.e.
+n=4/3 in this case) with the excess cooling being possible due to recombination of H$^{+}$ or heavier ions.
+Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpah$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization balance.
+In this scenario the temperature coefficient may be smaller then our derived value here.
 
 \subsection{Analytical Advection Model for $\alpha$ Boo's Wind} \label{disc:disc4}
-A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths as clearly shown in Figure \ref{fig:fig1}.
-If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the model.
-The main mechanism for this cooling would be wind expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
+
+A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
+If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$10 $R_{\star}$.
+The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
 To investigate this possibility further we adjusted the existing model to include a temperature power-law falloff of the form
@@
 \end{equation}
-where $r_{1}$ is just an arbitrary distance from the star and the temperature coefficient is that obtained from our new VLA data (see Table \ref{tab:tab5}).
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_\rm{H}$.
+at some distance $r_{1}$, from the star.The temperature coefficient is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H}}=n_{\rm{HII}}/n_{\rm{H}}$.
 In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
-\begin{itemize}
-\item We assume a conserved mass outflow i.e.
-$n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+\item 1.
+We assume a conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
-\item We assume that all ionization processes cease.
-\item We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha ^{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
-\item We assume a constant heavy ion fraction, $x_{\rm{hi}}=10^{-4}$.
-\end{itemize}
-Using these assumptions it can be shown that 
+\item 2. We assume that all ionization processes cease (\textbf{GMH}).
+\item 3.
+We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
+The recombination coefficient varies with temperature according the the relationship
 \begin{equation}
-x_{\rm{H}}(r)= \frac{x_{\rm{H}}(r_1)x_{\rm{hi}}e^{-I}}{x_{\rm{hi}}+x_{\rm{H}}(r_1)(1 - e^{-I})}
+\alpha _{b} = \alpha _{b}(r_{1})\left[\frac{T(r_1)}{T(r)}\right]^{0.77},
 \label{eq:eq3}
+\end{equation}
+where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
+\item 4. We assume a constant heavy ion fraction, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$.
+\item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by
+\begin{equation}
+x_{\rm{H}}(r)= \frac{x_{\rm{H}}(r_1)x_{\rm{ion}}e^{-I(r)}}{x_{\rm{ion}}+x_{\rm{H}}(r_1)[1 - e^{-I(r)}]}
+\label{eq:eq4}
 \end{equation}
@@
 \begin{equation}
-I = 2.38 \times 10^{-3} \left[\left( \frac{r_{1}}{r}\right)^{-0.19} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
-\label{eq:eq4}
+I(r) = 2.38 \times 10^{-3} \left[\left( \frac{r_{1}}{r}\right)^{-0.19} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
+\label{eq:eq5}
 \end{equation}
 \\
-If we alter the existing Drake model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile given by Equation \ref{eq:eq2} and a density profile governed by Equation \ref{eq:eq3} beyond 2.3 $R_{\star}$, then we get a  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by given by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then tails off to a constant value of $\sim$0.04 beyond $\sim$10$R_{\star}$.
 
 Encouraging as it is that such a simple analytical model can reproduce values close to the observed radio fluxes at long wavelengths, it must be stressed that this \textit{hybrid} model is just a first order approximation.
-It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$ 3 cm and therefore a new atmospheric model is still required that can reproduce all the observed fluxes.
+It assumes that the excess slope from the radio spectrum is a result of rapid cooling alone.
+It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$3 cm and therefore a new atmospheric model is still required that can reproduce all of the observed fluxe densities.
 To do so, the non-trivial task of simultaneously solving the non-local radiative transfer equation and atomic rate equations which include advection will be required.
 
-\subsection{Ionized Mass Loss Rates} \label{disc5}
-For a partially ionized outflow, such as that expected from $\alpha$ Boo and $\alpha$ Tau, the ionized mass loss rate can be estimated from the radio emission assuming a constant velocity, constant temperature, and constant ionization fraction and can be written as
-\begin{align}
-\dot{M}_{\rm{ion}} & \simeq 5.58 \times 10^{-14} \left(\frac{v_{\infty}}{\rm{km \  s^{-1}}}\right) \left(\frac{D}{\rm{pc}}\right)\left( \frac{F_{\nu}}{\rm{mJy}} \right)^{0.75} \nonumber \\
- & \qquad \times \left( \frac{\lambda}{\rm{cm}} \right)^{0.45} \left( \frac{T_{\rm{e}}}{10^4 \rm{K}} \right)^{0.1} \ \dot{M}_{\odot} \ \rm{yr}^{-1} 
-\label{eq:5}
-\end{align}
-where $D$ is the distance and $v_{\infty}$ is the wind terminal velocity defined earlier in Table \ref{tab:tab1}.
-Using this expression, the ionized mass loss rates were derived for each of the long wavelength measurements for both stars and are listed in Table \ref{tab:tab5}.
-These values are based on the assumption of a $T_{\rm{e}} = 10^4 \ \rm{K}$  wind for both stars.
+\section{CONCLUSIONS}
+We have presented the most comprehensive set of multi-wavelength radio continuum observations of two standard luminosity class III red giants to date.
+This is the first time such classes of stars have been detected longword of 6 cm.
+Such long wavelength detections are crucial if one wants to study the outer environments of these partially ionized stellar outflows.
+Our observations were carried out with the VLA during its commissioning phase when only a fraction of the now available bandwidth was at our disposal.
+The continuous bandwidth coverage between 1 and 50 GHz of the new VLA will allow fast detections of historically weak or undetectable radio continuum luminosity class III red giants at both long and short wavelengths.
+Previous upper limits will be replaced by firm detections allowing a greater understanding of their atmospheric properties.
 
-\begin{deluxetable}{ccc}
-
-\tablecaption{Ionized mass loss rates for $\alpha$ Boo and $\alpha$ Tau.}
-\tablehead{	\colhead{Star}		       				& 
-			\colhead{Wavelength (cm)}				&
-			\colhead{$\rm{\dot{M}_{ion}}$ (M$_{\odot}$ yr$^{-1}$)}}
-
-\startdata
-$\alpha$ Boo				& 6.0  & 5.9 \times 10^{-11} \\
-							& 9.5  & 5.5 \times 10^{-11} \\
-							& 10.0  & 5.1 \times 10^{-11} \\
-							& 20.0  & 4.3 \times 10^{-11} \\
-$\alpha$ Tau				& 6.0  & \leq 8.2 \times 10^{-11} \\
-							& 9.5 & \leq 5.3 \times 10^{-11} 
-\enddata
-\label{tab:tab6}
-\end{deluxetable}
-
-We have have discussed in the previous sections that for $\alpha$ Boo, these long wavelengths sample the outer atmosphere of the star where the wind  is close to or has reached its terminal velocity and is beginning to cool due to gas expansion.
-In this case, these $\dot{M}_{\rm{ion}}$ values would be lower than those given in \ref{tab:tab6}.
-However, as $\dot{M}_{\rm{ion}}$  is only weakly dependent on $T_{\rm{e}}$ this makes only a small difference and amounts to about a 7\% increase in the ionized mass loss if the temperature is actually lower by 50\%.
-If the ionization balance is frozen-in in the regions of the outflow where these long wavelengths sample then the derived $\dot{M}_{\rm{ion}}$ should be the same  for these wavelengths.
-The decrease in $\dot{M}_{\rm{ion}}$ with longer wavelengths as seen in Table \ref{tab:tab6} is probably therefore due to a combination of lower temperatures and lower ionization fractions further out in the atmosphere.
-The ionized mass loss rates for $\alpha$ Tau given in Table \ref{tab:tab6} are derived assuming the radio emission emanates from the outer atmosphere where the wind has reached its terminal velocity.
-As discussed in Section \ref{disc:disc3} the longest wavelengths are still sampling the acceleration zone and thus these ionized mass loss rates are just upper limits.
-
-\section{CONCLUSIONS}
+The spectral index of both $\alpha$ Tau and $\alpha$ Boo at long wavelengths is found to be greater than the predicted value for an isothermal steady spherically symmetric flow.
+For $\alpha$ Tau our longest wavelength detections are still sampling emission from an accelerating region within the outflow while for $\alpha$ Boo the emission probably emanates from a region where the flow is close to, or indeed have reached its terminal velocity.
+We have developed a simple analytical model for the outer atmosphere of $\alpha$ Boo based on these measurements which contains a rapid wind cooling profile.
+Future detailed non-LTE radiative transfer models which include advection are required to match all radio flux densities at all wavelengths.
 
@@
 We wish to thank the NRAO helpdesk for their detailed responses to our CASA related queries.
+This publication has emanated from research conducted with the financial support of Science Foundation Ireland under Grant Number SFI11/RFP.1/AST/3064, and a grant from Trinity College Dublin.
 

### 2013-04-01 draft_06/draft.tex
a small few edits from rathmines

@@
 
-\author{Eamon O'Gorman\altaffilmark{1}, Graham M. Harper\altaffilmark{1}, Alexander Brown\altaffilmark{2}, Stephen Drake\altaffilmark{3}, and Anita M.S. Richards\altaffilmark{4}}
+\author{Eamon O'Gorman\altaffilmark{1}, Graham M. Harper\altaffilmark{1}, Alexander Brown\altaffilmark{2}, Stephen Drake\altaffilmark{3}, and Anita M. S. Richards\altaffilmark{4}}
 \altaffiltext{1}{School of Physics, Trinity College Dublin, Dublin 2, Ireland}
@@
 
-Multi-wavelength centimeter continuum observations of non-dusty red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
-These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements accumulated over many years.
+Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
+These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over many years.
 Here, we present multi-wavelength Karl G.
 Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Uniquely, our observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
-We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
-This is the first time single (non-binary) luminosity class III red giants have been observed at such long continuum wavelengths.
+Importantly, our observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
+We report the first detections \textbf{at many wavelengths} for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
+This is the first time single (non-binary) luminosity class III red giants have been detected at these wavelengths.
 These long wavelength flux density measurements sample the outer layers of the stars atmosphere where the wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
-As a result, they are important empirical inputs for future atmospheric models.
+As a result, they are important empirical constraints for atmospheric models.
 We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models based on ultraviolet data.
@@
 Mass loss from late-type evolved stars plays a crucial role in both stellar and galactic evolution and ultimately provides part of of the material required for the next generation of stars and planets.
-Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g.,
-\citealt{2009AIPC.1094..267C}].
+Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g., \citealt{2009AIPC.1094..267C}].
 There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
@@
 
-Magnetic fields are most likely involved in the mass loss process, although current magnetic models are also unsuccessful.
-Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H}) are untenable.
-These models predict chromospheres as integral parts of turbulently extended and heated wind acceleration zones, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}.
-One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta.
+Magnetic fields are most likely involved in the mass loss process, although current magnetic models are also unable to explain spectral diagnostics.
+Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
+These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zones, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}.
+One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta as shown by the increase of wind scattering absorption with optical depth in Fe II lines \citep{1999ApJ...521..382C}.
 A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not yet in agreement with observations \citep{2009AIPC.1094..267C}.
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function is very sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value.
-At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure.
-It is this value that controls the atomic level populations and ionization that feed into UV spectroscopic analyses.
+In the UV, the source function of electron collisionally excited emission lines is sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value.
+At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal wind structure.
+It is this value that controls the atomic level populations and ionization of the plasma that feed into UV spectroscopic analyses.
 This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.
 
-In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of the stars atmosphere, thus essentially providing us with spatial information about the star's mass outflow region.
+In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of the stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at these radii due to advection.
 Furthermore, it is these outer extended regions of the star's atmosphere that contribute to the commonly seen P Cygni line profiles in the UV.
-In these profiles the line-of-sight absorption caused by the star's wind is superimposed on the blueshifted emission.
+In these profiles the line-of-sight absorption caused by the star's wind is superimposed on the blueshifted scattered emission.
 Thus, centimeter radio continuum observations can provide a test of models based on these UV profiles.

### 2013-04-02 draft_06/draft.tex
Trinity: Made GMHs edits on April 2nd

@@
 Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
-These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over many years.
+These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over three decades.
 Here, we present multi-wavelength Karl G.
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function of electron collisionally excited emission lines is sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value.
-At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal wind structure.
-It is this value that controls the atomic level populations and ionization of the plasma that feed into UV spectroscopic analyses.
+In the UV, the source function of electron collisionally excited emission lines is sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not hence reflect the global mean value.
+At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the mean thermal wind structure.
+It is this value that controls the atomic level populations and ionization of the mean plasma that feed into UV spectroscopic analyses.
 This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.
@@
 In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of the stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
+The VLA offers over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zones of evolved late type stars.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at these radii due to advection.
@@
 
-Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the symbiotic and $\zeta$ Aurigae systems (e.g., \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
+Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the $\zeta$ Aurigae and symbiotic systems (e.g., \citealt{1970VA.....12..147W}; \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
 Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
@@
 Spectral Type 				& K2 III  & K5 III  \\
+Mass (M_{\odot})	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
 Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
@@
 \enddata
-\tablecomments{Effective temperatures and photospheric angular diameters are from \cite{1993AA...270..315D}.
+\tablecomments{Masses are from \cite{2010A&A...509A..77K} and \cite{2012A&A...547A.108L}.
+Effective temperatures and photospheric angular diameters are from \cite{1993AA...270..315D}.
 Distances are from \cite{2007A&A...474..653V}.
@@
 
-Observations of $\alpha$ Boo and $\alpha$ Tau were carried out with the VLA during February 2011 at Q, Ka, K, X, C, and S-band in B-configuration (PI: Harper; program 10C-105).
+Observations of $\alpha$ Boo and $\alpha$ Tau were carried out with the VLA during Open Shared Risk Observing (OSRO) in February 2011 at Q, Ka, K, X, C, and S-band in B-configuration (PI: Harper; program 10C-105).
 $\alpha$ Boo was also observed at S and L-band in July 2012 when the VLA was again in B-configuration (PI: O'Gorman; program 12A-472).
@@
 Both $\alpha$ Boo and $\alpha$ Tau were slightly offset from the phase-center by $\sim$\,5 synthesized beam widths in order to avoid possible errors at phase-center.
-All scheduling blocks (SBs) were kept to $\le$\,2.5 hours of duration to improve their likelihood of being scheduled.
-For the high frequency observations (i.e., Q, Ka, and K-bands) we used the \textit{fast switching} technique which consisted of rapidly alternating observations of the target source and a nearby unresolved phase calibrator.
+All scheduling blocks (SBs) were kept to $\le$\,2.5 hours of duration.
+For the high frequency observations (i.e., Q, Ka, and K-bands) we used the \textit{fast switching} technique which consists of rapidly alternating observations of the target source and a nearby unresolved phase calibrator.
 The total cycle times for the Q, Ka, and K-band observations were 160, 230, and 290 s, respectively.
@@
 After X-band pointing the target source was observed at Q-band to insure the best pointing solutions were used.
-The lower frequencies tracks were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had much longer cycle times.
+The lower frequencies tracks were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had longer cycle times.
 The primary calibration sources 3C286 and 3C138 were observed at the end of all tracks and were used to measure the complex bandpass and set the absolute flux for $\alpha$ Boo and $\alpha$ Tau, respectively.
@@
 The data were flagged, calibrated, and imaged within the Common Astronomical Software Application  \cite[CASA;][]{2007ASPC..376..127M} package.
-Data deemed to be bad by the VLA online system were flagged, as were pure zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
+Data deemed to be bad by the VLA online system were flagged, as were zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
 Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged.
@@
 
-In order to calibrate the data, we solved for the complex gains of the calibration sources while applying the bandpass solution, which was derived from the relevant aforementioned flux calibrators.
-The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard.
+In order to calibrate the data, we solved for the complex gains of the calibration sources while applying the bandpass solution, which was derived from the relevant flux calibrator.
+The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard \citep{2013ApJS..204...19P}.
 At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively.
@@
 
-The visibilities were then both Fourier transformed and deconvolved using the CASA \textit{clean} task in multi-frequency synthesis imaging mode, which separately grids the the multiple spectral channels onto the \textit{u-v} plane and therefore improves the overall \textit{u-v} coverage.
+The visibilities were then both Fourier transformed and deconvolved using the CASA \textit{clean} task in multi-frequency synthesis imaging mode, which separately grids the multiple spectral channels onto the \textit{u-v} plane and therefore improves the overall \textit{u-v} coverage.
 We used natural weighting for maximum sensitivity and the cell size was chosen so that the synthesized beam was about five pixels across.
@@
 This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index of -1.4 and reaches 80.3 mJy at 1.6 GHz.
-Surprisingly we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
+We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.
+For unknown reasons we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
 We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
@@
 \subsection{$\alpha$ Tau Radio Maps} \label{results2}
-The final deconvolved radio maps of $\alpha$ Tau were of excellent quality with the rms noise reaching the predicted thermal noise in many cases.
+The final deconvolved radio maps of $\alpha$ Tau were of excellent quality with the rms noise reaching the predicted noise levels in many cases.
 The target field at all frequencies was free from strong serendipitous radio sources and thus the final images were free of the sidelobe contamination that were present in the low frequency $\alpha$ Boo images.
@@
 Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
-Due to the limited number of S-band receivers installed at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection.
+Due to the limited number of S-band receivers available at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection.
 We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density.
@@
 
-\begin{deluxetable*}{Ccccc}
+\begin{deluxetable*}{cccccc}
 \tabletypesize{\scriptsize}
@@
 \tablehead{							            &
-    \colhead{Frequency}		       				& 
+    \colhead{$\nu$ (GHz)}		       				& 
 			\colhead{Date}						&
-			\colhead{Flux Density}				&
-          	\colhead{Source} 			\\
-												&
-	\colhead{(GHz)}								&
-	\colhead{}									&
-    \colhead{(mJy)}		        				& 
-    \colhead{}			         				}
+			\colhead{$F_{\nu}$ (mJy)}				&
+			\colhead{$F_{\nu}/\sigma$}				&
+          	\colhead{Source} 					}
 \startdata
-$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & $0.39 \pm 0.13$ & \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 May 20 & $0.26 \pm 0.08$ & \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 Dec 26 & $\le 0.18(3\sigma)$ & \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Mar 17 & $0.24 \pm 0.05$ & \cite{1986AJ.....91..602D} \\
-&15.0 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
-&22.5  & 1999 Jan 06  & $ 1.7 \pm 0.2$ & \cite{2011AA...533A.107D} \\
-&43.3  & 1999 Jan 06 & $ 3.3 \pm 0.4$ & \cite{2011AA...533A.107D} \\
-&43.3  & 2004 Jan 25 & $ 3.34 \pm 0.08$ & \cite{2011AA...533A.107D} \\
-&86.0  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
-&108.4  & 1997 Nov - 2000 Jun & $ 20.09 \pm 0.69$ & \cite{2005AJ....129.2836C} \\
-&217.8 & 1997 Nov - 2000 Jun  & $ 83.5 \pm 1.71$ & \cite{2005AJ....129.2836C} \\
-&250.0  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
+$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & 0.39 & 3.0 & \cite{1986AJ.....91..602D} \\
+&4.9  & 1983 May 20 & 0.26 & 3.3& \cite{1986AJ.....91..602D} \\
+&4.9  & 1983 Dec 26 & $\le 0.18 \ (3\sigma)$&- & \cite{1986AJ.....91..602D} \\
+&4.9  & 1984 Mar 17 & 0.24  & 4.8& \cite{1986AJ.....91..602D} \\
+&15.0 & 1984 Nov 6 & 0.68 & 7.6& \cite{1986AJ.....91..602D} \\
+&22.5  & 1999 Jan 06  &1.7& 8.5& \cite{2011AA...533A.107D} \\
+&43.3  & 1999 Jan 06 & 3.3& 8.3& \cite{2011AA...533A.107D} \\
+&43.3  & 2004 Jan 25 & 3.34& 41.8& \cite{2011AA...533A.107D} \\
+&86.0  & 1985 Nov  & 21.4& 3.0& \cite{1986AA...164..227A} \\
+&108.4  & 1997 Nov - 2000 Jun & 20.1 &29.1 & \cite{2005AJ....129.2836C} \\
+&217.8 & 1997 Nov - 2000 Jun  & 83.5 &48.8 & \cite{2005AJ....129.2836C} \\
+&250.0  & 1986 Dec - 1989 Mar  & 78.0 & 9.8& \cite{1994AA...281..161A} \\
 \hline
-\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27(3\sigma)$ & \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& \cite{2007ApJ...655..946W} \\
-&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& \cite{2007ApJ...655..946W} \\
-&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& \cite{2007ApJ...655..946W} \\
-&15.0 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
-&108.4  & 1997 Nov - 2000 Dec & $ 13.97 \pm 1.46$ & \cite{2005AJ....129.2836C} \\
-&217.8 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
-&250.0  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
+\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27 \ (3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&4.9  & 1984 Nov 6 & $\le 0.22 \ (3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&5.0  & 1997 Sep 27 & $\le 0.07 \ (3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
+&8.5  & 1997 Sep 27 & 0.28 	&9.3	& \cite{2007ApJ...655..946W} \\
+&14.9 & 1997 Sep 27 & 0.95 	&11.9	& \cite{2007ApJ...655..946W} \\
+&15.0 & 1984 Nov 6 & 0.60 	&6.0	& \cite{1986AJ.....91..602D} \\
+&108.4  & 1997 Nov - 2000 Dec &  14.0  & 9.6& \cite{2005AJ....129.2836C} \\
+&217.8 & 1999 Sep - 2000 Dec  & 25.8 & 4.6& \cite{2005AJ....129.2836C} \\
+&250.0  & 1986 Dec - 1987 Jan & 51.0 & 8.5& \cite{1994AA...281..161A} 
 \enddata
@@
 The first definitive detection of thermal free-free emission from a luminosity class III single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}.
-Since then there has been a modest number of sporadic centimeter and millimeter observations of this star.
+Since then there has been a modest number of centimeter and millimeter observations of this star.
 In Table \ref{tab:tab4} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}.
-In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e., Q, K, Ku, and C).
+In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio continuum wavelengths before this study, including detections in four VLA bands (i.e., Q, K, Ku, and C).
 No Ku band receivers were available during the commissioning phase of the VLA in early 2011 so we can compare three of our detections with previous ones.
@@
 There is however a notable difference in flux density values at 0.7 cm  where \cite{2011AA...533A.107D} report values that are lower than ours by over 40\%.
-Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars.
+Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
 Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values.
@@
 
-Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind.
+Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate.
 The lack of a Ku measurement means that we can only compare the previous 3 cm detection of Brown $\&$ Harper (1997) to ours.
@@
 \subsection{Existing Atmospheric Models} \label{disc2}
-\textbf{GMH: A few words on Radspec code.}
+One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
+Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
+We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities included.
+The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
 
-One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
-Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the the International Ultraviolet Explorer.
 Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of 40 km s${}^{-1}$ at $\sim$2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$13 $R _{\star}$ with a cooler region further out.
-At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small density scale heights close to the star.
+At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small density scale heights close to the star where the temperature is changing slowly.
 At low frequencies however, where the models predict the wind to have constant velocity, ionization and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
 The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
-Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$8 GHz and above $\sim$25 GHz).
+Our new data reveal significant deviations from the semi-empirical model at both low and high frequencies (in this case below $\sim$8 GHz and above $\sim$25 GHz).
 At high frequencies our VLA data indicates a flux excess which is in agreement with previous mm-observations.
@@
 In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromospheric model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
-The McMurry model includes a transition region and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
+The McMurry model is based on high S/N Hubble UV spectra and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
 Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value by 3 $R_{\star}$.
 We assume the wind to have a constant temperature of 8,000 K and have a constant ionization fraction, $x_{e}$, of 0.01 throughout.
-The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $>$ 30 GHz) but does a good job in reproducing the VLA flux densities below 30 GHz.
+The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $\nu >$ 30 GHz) but does well in reproducing the VLA flux densities below 30 GHz.
 The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxe densities confirm that this model predicts a flux excess at even higher frequencies.
@@
 
-We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
+We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
 This model is based on a larger than now expected mass loss rate for the star (i.e., 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow with $v_{\infty} \approx 115$ km s$^{-1}$.
@@
 \subsection{Radio Spectral Indices} \label{disc:disc3}
-For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$).
-For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), while for an optically thin plasma $\alpha = -0.1$.
-However, the electron density in the mass outflow region of a star is not constant as a function of radius and varies by many orders of magnitude.
+The radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows.
+The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from an optically thick homogeneous plasma ($\alpha$ follows the Rayleigh-Jeans tail of the Planck function i.e., $\alpha = +2$) and that from an optically thin plasma ($\alpha = -0.1$).
 It can be shown that the expected radio spectrum from an isothermal spherically symmetric steady flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
@@
 \citep[e.g.,][]{1987ApJ...312..813S}.
-Here $p > 1.5$, otherwise we are in the optically thin regime.
+For an isothermal flow $p > 1.5$, otherwise we are in the optically thin regime.
 Equation \ref{eq:eq1} is also only valid if the ionization fraction is constant throughout the outflow.
@@
 The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
-For $\alpha$ Boo a straight line with $F_{\nu} \propto \nu ^{1.05 \pm 0.05}$ fits the four longest wavelength data points well.
+For $\alpha$ Boo a power law with $F_{\nu} \propto \nu ^{1.05 \pm 0.05}$ fits the four longest wavelength data points well.
 This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm.
-$\alpha$ Tau was found to have a larger spectral index and a straight line with $S_{\nu} \propto \nu ^{1.58 \pm 0.25}$ best fitted the three longest wavelength data points.
+$\alpha$ Tau was found to have a larger spectral index and a power law with $S_{\nu} \propto \nu ^{1.58 \pm 0.25}$ best fitted the three longest wavelength data points.
 This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data given in \cite{2007ApJ...655..946W}.
@@
 The degree of variation of these coefficients with respect to one another is shown in Figure \ref{fig:fig4}.
-A common explanation in the literature for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are usually ignored.
-If we too make this assumption then the density coefficients are 2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
+An explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from if thermal gradients are ignored.
+If we too make this assumption then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
 This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) this assumption may be false and we may indeed be sampling the wind very close to or at its terminal velocity.
@@
 Points corresponding to our long wavelength VLA measurements are also shown.
-At the same radio wavelengths the less ionized mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
+At the same radio wavelengths the less ionized and less opaque mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
 \label{fig:fig5}
@@
 \end{equation}
-at some distance $r_{1}$, from the star.The temperature coefficient is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H}}=n_{\rm{HII}}/n_{\rm{H}}$.
+at some distance $r_{1}$, from the star.
+The temperature coefficient is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$.
 In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
 \item 1.
-We assume a conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+Assume a conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
-\item 2. We assume that all ionization processes cease (\textbf{GMH}).
+\item 2. All ionization processes cease beyond $r_{1}$(\textbf{GMH}).
 \item 3.
-We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
-The recombination coefficient varies with temperature according the the relationship
+Consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
+The recombination coefficient varies with temperature according the relationship
 \begin{equation}
@@
 where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
-\item 4. We assume a constant heavy ion fraction, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$.
-\item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by
+\item 4. The heavy ion fraction is constant, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$.
+\item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
 \begin{equation}
-x_{\rm{H}}(r)= \frac{x_{\rm{H}}(r_1)x_{\rm{ion}}e^{-I(r)}}{x_{\rm{ion}}+x_{\rm{H}}(r_1)[1 - e^{-I(r)}]}
+x_{\rm{HII}}(r)= \frac{x_{\rm{HII}}(r_1)x_{\rm{ion}}e^{-I(r)}}{x_{\rm{ion}}+x_{\rm{HII}}(r_1)[1 - e^{-I(r)}]}
 \label{eq:eq4}
@@
 \\
-By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by given by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by given by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
 This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then tails off to a constant value of $\sim$0.04 beyond $\sim$10$R_{\star}$.

### 2013-04-03 draft_06/draft.tex
April GMH 3rd edits

@@
 
-Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of 40 km s${}^{-1}$ at $\sim$2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$13 $R _{\star}$ with a cooler region further out.
+Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out.
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small density scale heights close to the star where the temperature is changing slowly.
@@
 
+ALMA, Ohnaka etc....
+
 \acknowledgments

### 2013-04-03 draft_06/draft.tex
A few edits from Rathmines

@@
 \includegraphics[trim = 5mm 0mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
-\caption{Predicted effective radius (dashed lines) as a function of wavelength for $\alpha$ Boo and $\alpha$ Tau.
+\caption{Predicted effective radius (dashed lines) as a function of wavelength derived from the existing atmospheric models of $\alpha$ Boo and $\alpha$ Tau.
+Also plotted is the predicted effective radius derived from our analytical advection model discussed in \ref{disc:disc4}.
 Points corresponding to our long wavelength VLA measurements are also shown.
-At the same radio wavelengths the less ionized and less opaque mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
+At the same radio wavelengths the less ionized and less opaque mass outflow of  Tau results in a smaller effective radius than $\alpha$ Boo.}
 \label{fig:fig5}

### 2013-04-04 draft_06/draft.tex
Edits on April 4th

@@
 Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Importantly, our observations were mostly carried out within a few days of each other so any long term variability that may exist can be ignored.
-We report the first detections \textbf{at many wavelengths} for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
+Importantly, most of our observations were carried out within a few days of each other so any long term variability that may exist will not affect our interpretation of the data.
+We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
 This is the first time single (non-binary) luminosity class III red giants have been detected at these wavelengths.
@@
 
-\keywords{circumstellar matter --- Stars: individual: ($\rm{\alpha}$ Boo, $\rm{\alpha}$ Tau) --- Stars: late-type --- Stars: chromospheres --- Stars: winds, outflows --- Radio continuum: stars}
+\keywords{Radio continuum: stars --- Stars: chromospheres --- Stars: individual ($\rm{\alpha}$ Boo, $\rm{\alpha}$ Tau) --- Stars: late-type --- Stars: winds, outflows}
 
@@
 Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
-These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zones, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}.
+These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zone, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}.
 One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta as shown by the increase of wind scattering absorption with optical depth in Fe II lines \citep{1999ApJ...521..382C}.
@@
 
-In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of the stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
-The VLA offers over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zones of evolved late type stars.
-The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at these radii due to advection.
+In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of a stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
+The NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
+Jansky Very Large Array (VLA) offers over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zones of evolved late type stars.
+The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at large radii due to advection.
 Furthermore, it is these outer extended regions of the star's atmosphere that contribute to the commonly seen P Cygni line profiles in the UV.
@@
 Thus, centimeter radio continuum observations can provide a test of models based on these UV profiles.
-In this paper we directly compare our new NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
-Jansky Very Large Array (VLA) observations with atmospheric models derived from UV analysis.
+In this paper we directly compare our new VLA observations with atmospheric models derived from UV analysis.
 
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Some properties of our red giant sample.}
+\tablecaption{Properties of red giant sample.}
 \tablehead{	\colhead{}		       				& 
@@
 Radius ($R_{\odot}$)	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
+Photospheric Escape Velocity & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
+Wind Terminal Velocity & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
-Wind Temperature (K)		& $\sim10,000$  & $< 10,000$  \\
-Wind Terminal Velocity & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
-Semi-empirical model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
+Wind Temperature (K)		& $\sim$10,000  & $< 10,000$  \\
+Semi-empirical Model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
 \enddata
@@
 
-Both $\alpha$ Boo and $\alpha$ Tau were slightly offset from the phase-center by $\sim$\,5 synthesized beam widths in order to avoid possible errors at phase-center.
+Both $\alpha$ Boo and $\alpha$ Tau were slightly offset from the phase-center by $\sim$5 synthesized beam widths in order to avoid possible errors at phase-center.
 All scheduling blocks (SBs) were kept to $\le$\,2.5 hours of duration.
@@
 Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}.
+For weak detections (i.e., $F_{\nu} \lesssim 5\sigma$) we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may produce biased parameter estimates \citep{1999ASPC..180.....T}.
+The flux density values used in Section \ref{disc:disc0} are the peak values listed in Table \ref{tab:tab3}.
 We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies \citep{2013ApJS..204...19P}.
@@
 &C  &4.90 & 0.214 & 0.144 & 0.159 & 0.035 & 0.009 \\
-&S  &3.15 & 0.148 & 0.135 & 0.160 & 0.028 & 0.010\\
+&S  &3.15 & 0.148 & 0.135 & -     & 0.028 & -     \\
 &S  &2.87 & 0.127 & 0.118 & 0.116 & 0.012 & 0.016\\
-&L  &1.63 & 0.067 & 0.068 & 0.090 & 0.013 & 0.015\\
+&L  &1.63 & 0.067 & 0.068 & -     & 0.013 & -    \\
 \hline
@@
 Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data.
-At each other frequency, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here.
+For all other bands, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here.
 Instead we give the values from the radio maps produced by concatenating the two sub-bands.
@@
 We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density.
-As this is a weak detection we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may introduce additional errors \citep{1999ASPC..180.....T}.
 
@@
 
-\section{DISCUSSION}
+\section{DISCUSSION} \label{disc:disc0}
 \subsection{Results Versus Previous Observations} \label{disc1}
@@
 Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate.
-The lack of a Ku measurement means that we can only compare the previous 3 cm detection of Brown $\&$ Harper (1997) to ours.
+Our lack of a Ku measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours.
 We find that there is no significant difference between the two.
-Interestingly however, Brown $\&$ Harper (1997; priv.
-comm.) failed to detect $\alpha$ Tau at 6 cm but placed a 3$\sigma$ upper limit of 0.07 mJy on its emission.
+Interestingly, \cite{2007ApJ...655..946W} report a non-detection of $\alpha$ Tau at 6 cm and placed a 3$\sigma$ upper limit of 0.07 mJy on its emission.
 In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value.
@@
 Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out.
-At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small density scale heights close to the star where the temperature is changing slowly.
-At low frequencies however, where the models predict the wind to have constant velocity, ionization and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
+At low frequencies however, where the models predict the wind to have constant velocity, ionization fraction and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
 The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
@@
 The overlap between the two models are represented by the green shaded area.
-The red triangles are previous observations which were acquired sporadically over the past $\sim25$ years with the `old' VLA, IRAM and BIMA.
+The red triangles are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
 The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
@@
 \caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
-All our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
-The red triangles are the previous radio observations of the star which were acquired over many years.The green line is the expected radio emission from the current hybrid chromosphere and wind model while the dashed  green line is the expected radio emission from a theoretical Alfv\`en wave driven model atmosphere.}
+Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
+The red triangles are the previous radio observations of the star which were acquired over many years.
+The green line is the expected radio emission from the existing hybrid chromosphere and wind model while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
 \label{fig:fig2}
@@
 The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $\nu >$ 30 GHz) but does well in reproducing the VLA flux densities below 30 GHz.
-The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxe densities confirm that this model predicts a flux excess at even higher frequencies.
+The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum flux densities confirm that this model predicts a flux excess at even higher frequencies.
 One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
 This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere.
-For $\alpha$ Boo there is a hint that the transition frequency between wind and chromosphere occurs at about 8.5 GHz due to the change of slope but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish.
-There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.
 
-We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
+We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
 This model is based on a larger than now expected mass loss rate for the star (i.e., 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow with $v_{\infty} \approx 115$ km s$^{-1}$.
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$ this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The same result is to be expected from the Alfv\`{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger than now expected mass loss rates and outflow velocities.
+The same result is to be expected from the Alfv\'{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger than now expected mass loss rates and outflow velocities.
 
@@
 It can be shown that the expected radio spectrum from an isothermal spherically symmetric steady flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
+If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
 

### 2013-04-05 draft_06/draft.tex
Edits on April 5th

@@
 The radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows.
-The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from an optically thick homogeneous plasma ($\alpha$ follows the Rayleigh-Jeans tail of the Planck function i.e., $\alpha = +2$) and that from an optically thin plasma ($\alpha = -0.1$).
-It can be shown that the expected radio spectrum from an isothermal spherically symmetric steady flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
+The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the stellar disk emission where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$) and that from an optically thin plasma ($\alpha = -0.1$).
+It can be shown that the expected radio spectrum from a spherically symmetric, steady isothermal constant velocity and ionization fraction flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
 
@@
 \end{equation}
-\citep[e.g.,][]{1987ApJ...312..813S}.
-For an isothermal flow $p > 1.5$, otherwise we are in the optically thin regime.
-Equation \ref{eq:eq1} is also only valid if the ionization fraction is constant throughout the outflow.
-By making these assumptions and assuming either a constant velocity (i.e., $p=2$) or an isothermal outflow (i.e., $n=0$), we can easily estimate the power-law decay of either the temperature or velocity profile, respectively.
+\citep[e.g.,][]{1987ApJ...312..813S}. (always spherical,steady but not ..)
 
@@
 The derived temperature coefficient of 1.65 points to a temperature power-law falloff exceeding that from a wind adiabatically cooling with no heat source (i.e.
-n=4/3 in this case) with the excess cooling being possible due to recombination of H$^{+}$ or heavier ions.
-Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpah$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization balance.
+n=1.33 in this case) with the excess cooling being possible due to recombination of H$^{+}$ or heavier ions.
+Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization balance.
 In this scenario the temperature coefficient may be smaller then our derived value here.
@@
 To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$.
-In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
+In doing so we need to make a number of assumptions about the wind properties from a distnace $r_{1}$ from the star onwards, namely:
 \item 1.
-Assume a conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+A conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
-\item 2. All ionization processes cease beyond $r_{1}$(\textbf{GMH}).
+\item 2.
+All ionization processes cease beyond $r_{1}$.
+The ionization of hydrogen in the chromosphere and wind is a two stage process: the $n = 2$ level is excited by electron collisions and Lyman-alpha scattering, followed by photoionization by the optically thin Balmer continuum.
+When the temperatures begins to decrease in the wind the collisional excitation rate and thus ionization rate decrease rapidly.
 \item 3.
 Consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
-The recombination coefficient varies with temperature according the relationship
+The recombination coefficient varies with temperature as
 \begin{equation}
@@
 where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
-\item 4. The heavy ion fraction is constant, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$.
+\item 4. A fixed ion contribution from from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
 \item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
@@
 By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by given by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then tails off to a constant value of $\sim$0.04 beyond $\sim$10$R_{\star}$.
+This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then tails off to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 
@@
 It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$3 cm and therefore a new atmospheric model is still required that can reproduce all of the observed fluxe densities.
-To do so, the non-trivial task of simultaneously solving the non-local radiative transfer equation and atomic rate equations which include advection will be required.
+To do so, the non-trivial task of simultaneously solving the radiative transfer equation and non-LTE atomic level populations which include advection will be required.
 
@@
 We have presented the most comprehensive set of multi-wavelength radio continuum observations of two standard luminosity class III red giants to date.
-This is the first time such classes of stars have been detected longword of 6 cm.
+This is the first time such class of stars have been detected longword of 6 cm.
 Such long wavelength detections are crucial if one wants to study the outer environments of these partially ionized stellar outflows.

### 2013-04-07 draft_06/draft.tex
Last edits before sending out to authors

@@
 
-Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is being deposited.
-These stars are feeble thermal emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over three decades.
-Here, we present multi-wavelength Karl G.
-Jansky Very Large Array (VLA) thermal continuum observations of the acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Importantly, most of our observations were carried out within a few days of each other so any long term variability that may exist will not affect our interpretation of the data.
-We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz; S-band) for both stars and a 20 cm (1.5 GHz; L-band) detection for $\alpha$ Boo.
+Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is deposited.
+Such stars are feeble emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over three decades.
+We present multi-wavelength Karl G.
+Jansky Very Large Array (VLA) thermal continuum observations of the wind acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
+Importantly, most of our observations were carried out within a few days of each other so any long term variability that may exist does not affect our analysis.
+We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz: S-band) for both stars and a 20 cm (1.5 GHz: L-band) detection for $\alpha$ Boo.
 This is the first time single (non-binary) luminosity class III red giants have been detected at these wavelengths.
@@
 The marked deviations between our data and existing semi-empirical models highlight the need for new atmospheric models to be developed.
-The derived spectral indices are discussed in relation to the possible properties of the stellar atmospheres and a simple analytical atmospheric model is developed for $\alpha$ Boo's outer atmosphere which is in good agreement with our new long wavelength flux densities.
+Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
+We develop a simple analytical atmospheric model for $\alpha$ Boo which includes a rapidly cooling constant velocity wind and is found to be in good agreement with our new long wavelength flux density values.
 
@@
 Mass loss from late-type evolved stars plays a crucial role in both stellar and galactic evolution and ultimately provides part of of the material required for the next generation of stars and planets.
-Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g., \citealt{2009AIPC.1094..267C}].
+Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g., \cite{2009AIPC.1094..267C}].
 There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
@@
 Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
-These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zone, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, e.g., \cite{1998ApJ...494..828J}.
+These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zone, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, \cite[e.g.,][]{1998ApJ...494..828J}.
 One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta as shown by the increase of wind scattering absorption with optical depth in Fe II lines \citep{1999ApJ...521..382C}.
@@
 It is this value that controls the atomic level populations and ionization of the mean plasma that feed into UV spectroscopic analyses.
-This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.
+This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, allowing constraints on potential mass loss mechanisms to be derived.
 
@@
 Spectral Type 				& K2 III  & K5 III  \\
+HD Number 				& 124897  & 29139  \\
 Mass (M_{\odot})	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
@@
 Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate.
-Our lack of a Ku measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours.
+Our lack of a Ku-band measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours.
 We find that there is no significant difference between the two.
@@
 Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
-We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities included.
+We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free capacities included.
 The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
+Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm and this is a good check on the robustness of our method of producing radio spectra from these model atmospheres.
 
-Both of Drake's models predict the wind to reach a terminal velocity, $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out.
+Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$.
+They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out.
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
@@
 In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromospheric model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
-The McMurry model is based on high S/N Hubble UV spectra and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
+The McMurry model, which contains  the photospheric model of \cite{1973ApJ...180...81J}, is based on high S/N Hubble UV spectra and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
 Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value by 3 $R_{\star}$.
@@
 
-We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
+We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
 This model is based on a larger than now expected mass loss rate for the star (i.e., 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow with $v_{\infty} \approx 115$ km s$^{-1}$.
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$ this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The same result is to be expected from the Alfv\'{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger than now expected mass loss rates and outflow velocities.
+The same result is to be expected from the Alfv\'{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger mass loss rates and outflow velocities than the established values given in Table \ref{tab:tab1}.
 
@@
 The radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows.
-The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the stellar disk emission where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$) and that from an optically thin plasma ($\alpha = -0.1$).
-It can be shown that the expected radio spectrum from a spherically symmetric, steady isothermal constant velocity and ionization fraction flow varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-If we relax some of these assumptions about the outflow and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
+The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
+It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
 
@@
 \end{equation}
-\citep[e.g.,][]{1987ApJ...312..813S}. (always spherical,steady but not ..)
+\citep[e.g.,][]{1987ApJ...312..813S}.
 
@@
 This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data given in \cite{2007ApJ...655..946W}.
-It should be emphasized that the spectral index for both stars is steeper than that expected for an isothermal spherically symmetric steady flow.
+It should be emphasized that the spectral index for both stars is steeper than that expected from the constant property wind model.
 
 \begin{figure}
-\includegraphics[trim = 0mm 10mm 0mm 20mm, clip,scale=0.385,angle=90]{fig4.ps}
+\includegraphics[trim = 0mm 11mm 0mm 21mm, clip,scale=0.4,angle=90]{fig4.ps}
 \caption{The variation of density and temperature coefficients for the empirically derived spectral indices.
@@
 Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that describe their outflow.
-The degree of variation of these coefficients with respect to one another is shown in Figure \ref{fig:fig4}.
-An explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from if thermal gradients are ignored.
+The degree of variation of these coefficients with respect to one another are shown in Figure \ref{fig:fig4}.
+One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are assumed to be small.
+Ignoring thermal gradients may be reasonable over the small distances in which the red giants outflow undergoes rapid acceleration.
 If we too make this assumption then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) this assumption may be false and we may indeed be sampling the wind very close to or at its terminal velocity.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may be have substantial thermal gradients.
 
@@
 
-The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig4}.
-At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.1 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
+The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig5}.
+At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.2 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
 \cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$ so it is highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
@@
 A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
-If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$10 $R_{\star}$.
+If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the existing models, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
 The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
-To investigate this possibility further we adjusted the existing model to include a temperature power-law falloff of the form
+To investigate this possibility further we adjusted one of the existing models [referred to `Model B' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
 \begin{equation}
@@
 at some distance $r_{1}$, from the star.
-The temperature coefficient is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
+The temperature coefficient used here is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
 To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$.
-In doing so we need to make a number of assumptions about the wind properties from a distnace $r_{1}$ from the star onwards, namely:
+In doing so we need to make a number of assumptions about the wind properties from a distance $r_{1}$ from the star onward, namely:
 \item 1.
@@
 \\
-By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by given by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then tails off to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
+By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 
 Encouraging as it is that such a simple analytical model can reproduce values close to the observed radio fluxes at long wavelengths, it must be stressed that this \textit{hybrid} model is just a first order approximation.
-It assumes that the excess slope from the radio spectrum is a result of rapid cooling alone.
+It assumes that the excess slope from the radio spectrum is a result of rapid cooling only.
 It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$3 cm and therefore a new atmospheric model is still required that can reproduce all of the observed fluxe densities.
@@
 We have presented the most comprehensive set of multi-wavelength radio continuum observations of two standard luminosity class III red giants to date.
-This is the first time such class of stars have been detected longword of 6 cm.
+This is the first time such class of stars have been detected at wavelengths longer than 6 cm.
 Such long wavelength detections are crucial if one wants to study the outer environments of these partially ionized stellar outflows.
@@
 The continuous bandwidth coverage between 1 and 50 GHz of the new VLA will allow fast detections of historically weak or undetectable radio continuum luminosity class III red giants at both long and short wavelengths.
-Previous upper limits will be replaced by firm detections allowing a greater understanding of their atmospheric properties.
+Previous upper limits will be replaced by firm detections allowing a greater understanding of their outer atmospheric properties.
 
-The spectral index of both $\alpha$ Tau and $\alpha$ Boo at long wavelengths is found to be greater than the predicted value for an isothermal steady spherically symmetric flow.
+The spectral index of both $\alpha$ Tau and $\alpha$ Boo at long wavelengths is found to be greater than that expected from a constant property wind.
 For $\alpha$ Tau our longest wavelength detections are still sampling emission from an accelerating region within the outflow while for $\alpha$ Boo the emission probably emanates from a region where the flow is close to, or indeed have reached its terminal velocity.
-We have developed a simple analytical model for the outer atmosphere of $\alpha$ Boo based on these measurements which contains a rapid wind cooling profile.
+Using our new VLA data we have developed a simple analytical model for the outer atmosphere of $\alpha$ Boo which contains a rapid wind cooling profile.
 Future detailed non-LTE radiative transfer models which include advection are required to match all radio flux densities at all wavelengths.
-
-ALMA, Ohnaka etc....
 

### 2013-04-22 draft_07/draft.tex
1st round of edits from co-I's

--- 2013-04-07 draft_06/draft.tex
@@
 %\email{alexander.brown@colorado.edu}
+%\email{drake@milkyway.gsfc.nasa.gov}
 %\email{a.m.s.richards@manchester.ac.uk}
-%\email{drake@milkyway.gsfc.nasa.gov}
 
@@
 
-Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their wind acceleration zones where most of the energy that drives their mass loss is deposited.
+Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their chromospheres and wind acceleration zones where most of the energy that drives their mass loss is deposited.
 Such stars are feeble emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over three decades.
@@
 Jansky Very Large Array (VLA) thermal continuum observations of the wind acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Importantly, most of our observations were carried out within a few days of each other so any long term variability that may exist does not affect our analysis.
-We report the first detections at many wavelengths for each star including a detection at 10 cm (3.0 GHz: S-band) for both stars and a 20 cm (1.5 GHz: L-band) detection for $\alpha$ Boo.
-This is the first time single (non-binary) luminosity class III red giants have been detected at these wavelengths.
-These long wavelength flux density measurements sample the outer layers of the stars atmosphere where the wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
-As a result, they are important empirical constraints for atmospheric models.
+Importantly, most of our observations of each star were carried out over just a few days, so that we obtained an essentially consistent snapshot of the different stellar layers sampled at different wavelengths, independent of any long-term variability.
+We report the first detections at several wavelengths for each star including a detection at 10 cm (3.0 GHz: S-band) for both stars and a 20 cm (1.5 GHz: L-band) detection for $\alpha$ Boo.
+This is the first time single (non-binary) luminosity class III red giants have been detected at these continuum wavelengths.
+We find that these flux density measurements sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
 We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models based on ultraviolet data.
@@
 Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
-We develop a simple analytical atmospheric model for $\alpha$ Boo which includes a rapidly cooling constant velocity wind and is found to be in good agreement with our new long wavelength flux density values.
+We develop a simple analytical atmospheric model for $\alpha$ Boo which includes a rapidly cooling constant velocity wind, and the model is found to be in good agreement with our new long wavelength flux density values.
 
@@
 The NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
-Jansky Very Large Array (VLA) offers over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zones of evolved late type stars.
+Jansky Very Large Array (VLA) is sensitive to over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zone of evolved late type stars.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at large radii due to advection.
@@
 These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
-These stars are predicted to be point sources at all frequencies in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
+These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
 Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
@@
 After X-band pointing the target source was observed at Q-band to insure the best pointing solutions were used.
-The lower frequencies tracks were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had longer cycle times.
+The tracks at lower frequencies were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had longer cycle times.
 The primary calibration sources 3C286 and 3C138 were observed at the end of all tracks and were used to measure the complex bandpass and set the absolute flux for $\alpha$ Boo and $\alpha$ Tau, respectively.
@@
 The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard \citep{2013ApJS..204...19P}.
-At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively.
+At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively, which were scaled according to their spectral indices.
 The more frequently observed phase calibrators were then used to calibrate the amplitude and phases of the targets.
@@
 For the low frequencies however, the image sizes were usually set to a few times the size of the primary beam so that nearby strong serendipitous sources could be CLEANed thus reducing their sidelobe contamination of the final image.
-These images were CLEANed interactively, with w-term correction, down to about the $3\sigma$  level with clean boxes placed around sources as they appeared in the residual image.
+These images were CLEANed interactively, taking sky curvature into account, down to about the $3\sigma$  level with clean boxes placed around sources as they appeared in the residual image.
 All images were corrected for  primary beam attenuation.
@@
 %\tablewidth{0pt} 
-\tablecaption{VLA Fluxe Densities of $\alpha$ Boo and $\alpha$ Tau}
+\tablecaption{VLA Flux Densities of $\alpha$ Boo and $\alpha$ Tau}
 \tablehead{\colhead{}		            &
@@
 Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data.
-For all other bands, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present these values here.
+For all other bands, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present separate values here.
 Instead we give the values from the radio maps produced by concatenating the two sub-bands.
@@
 Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations.
-The lower frequencies maps were contaminated by the emission of a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
-This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
+The lower-frequency maps were contaminated by the emission of a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
+This source was found to have a flux density of 25 mJy at 4.9 GHz by \cite{1986AJ.....91..602D}, in close agreement with our measurement of 23.2 mJy at the same frequency.
 We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.
@@
 There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
-However, this is less than a quarter of the 1.5 GHz synthesized beam and considering that the $4\sigma$ contours overlap, we feel that it is highly unlikely that both sources are not $\alpha$ Boo.
+However, the position uncertainties, due to noise and to the atmospheric differences between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
 
@@
 One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
-Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
+Figure \ref{fig:fig1} shows the predicted radio spectrum for $\alpha$ Boo from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
 We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free capacities included.
@@
 One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
-This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere.
+This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
 
 We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
-This model is based on a larger than now expected mass loss rate for the star (i.e., 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow with $v_{\infty} \approx 115$ km s$^{-1}$.
-As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$ this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The same result is to be expected from the Alfv\'{e}n wave models of $\alpha$ Boo \citep{1988AcA....38..107K} which are also fully ionized and have larger mass loss rates and outflow velocities than the established values given in Table \ref{tab:tab1}.
+This model is based on a fully-ionized outflow at a mass loss rate of  6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
+As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
+The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization, and have higher mass loss rates and outflow velocities than the established values given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
 
 \subsection{Radio Spectral Indices} \label{disc:disc3}
-The radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows.
-The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
+Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers.
+The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
 It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
@@
 \includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
-\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit straight lines to their long wavelength flux densities and the resulting spectral indices.}
+\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices.}
 \label{fig:fig3}
@@
 \caption{The variation of density and temperature coefficients for the empirically derived spectral indices.
-The density coefficients for an isothermal flow along with the temperature coefficients for a constant outflow velocity are also shown for both stars.}
+The density coefficients for an isothermal flow ($n$=0) along with the temperature coefficients for a constant outflow velocity ($p$=2) are also shown for both stars.}
 \label{fig:fig4}
@@
 Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that describe their outflow.
-The degree of variation of these coefficients with respect to one another are shown in Figure \ref{fig:fig4}.
-One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from and thermal gradients are assumed to be small.
-Ignoring thermal gradients may be reasonable over the small distances in which the red giants outflow undergoes rapid acceleration.
+The combinations of the electron temperature and density coefficients are shown for each star in Figure \ref{fig:fig4} along with the coefficients obtained by assuming either an isothermal flow or a constant velocity flow.
+One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from if the thermal gradients are assumed to be small.
+Ignoring thermal gradients may be reasonable over the wind acceleration region since it is probable that some sort of Alfv\'en waves are required to lift the material out of the gravitational potential and large damping lengths would be needed to do so.
+These large damping lengths could result in low thermal gradients close in.
 If we too make this assumption then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may be have substantial thermal gradients.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may be have substantial thermal gradients.
 
@@
 We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at each wavelength emanates from a surface at radial optical depth $\tau _{\rm{rad}}=$1/3.
-This is just the Eddington-Barbier relation for an extended atmosphere where emission from smaller optical depths gets added weight.
-Since the radio free-free opacity increases at longer wavelengths (i.e., $\kappa _{\lambda} \propto \lambda ^{2.1}$) the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
-This implies that the effective radius (i.e., the radius where $\tau _{\lambda} = \tau _{\rm{rad}}$) will increase with longer wavelengths and will be greater for outflows with higher ionization densities as $\tau _{\lambda} \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
+This is a modification of the Eddington-Barbier relation for an extended atmosphere where emission from smaller optical depths has added weight.
+Since the radio free-free opacity increases at longer wavelengths the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
+This implies that the effective radius (i.e., the radius where $\tau _{\lambda} = \tau _{\rm{rad}}$) will increase with longer wavelengths and will be greater for outflows with higher densities of ionized material as $\tau _{\lambda} \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
 
-The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig5}.
+The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau means that the latter has a substantially smaller effective radius at longer wavelengths, as seen in Figure \ref{fig:fig5}.
 At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.2 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
-\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$ so it is highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind.
-For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest VLA measurements probable sample the wind at, or very close to, its terminal velocity.
-Assuming this to be the case, Equation \ref{eq:eq1} then indicates that $\alpha$ Boo's steady outflow undergoes rapid cooling at a few stellar radii.
-The derived temperature coefficient of 1.65 points to a temperature power-law falloff exceeding that from a wind adiabatically cooling with no heat source (i.e.
-n=1.33 in this case) with the excess cooling being possible due to recombination of H$^{+}$ or heavier ions.
+\cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$, but even our longest-wavelength observations are highly unlikely to sample the wind outside the lower velocity layers closer to the star.
+For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest-wavelength measurements are of the region where the wind has reached a steady terminal velocity.
+From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$.
+Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
 Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization balance.
-In this scenario the temperature coefficient may be smaller then our derived value here.
+In this scenario the temperature coefficient may be smaller than our derived value here.
 
@@
 
-A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
-If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the existing models, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
+A failure of the Drake model for $\alpha$ Boo is that it overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
+If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than predicted by the existing models, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
 The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
@@
 To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$.
-In doing so we need to make a number of assumptions about the wind properties from a distance $r_{1}$ from the star onward, namely:
+In doing so we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
 \item 1.
-A conserved mass outflow i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+A constant velocity mass outflow, i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
@@
 \item 3.
-Consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
+Only radiative recombination of H is considered and the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S} is included.
 The recombination coefficient varies with temperature as
 \begin{equation}
-\alpha _{b} = \alpha _{b}(r_{1})\left[\frac{T(r_1)}{T(r)}\right]^{0.77},
+\alpha _{B} = \alpha _{B}(r_{1})\left[\frac{T(r_1)}{T(r)}\right]^{0.77},
 \label{eq:eq3}
@@
 where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
-\item 4. A fixed ion contribution from from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
+\item 4. A fixed ion contribution from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
 \item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
@@
 \\
-By altering the existing atmospheric model so that it now has a narrow temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+By altering the existing atmospheric model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
 This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
@@
 It assumes that the excess slope from the radio spectrum is a result of rapid cooling only.
-It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$3 cm and therefore a new atmospheric model is still required that can reproduce all of the observed fluxe densities.
+It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$3 cm and therefore a new atmospheric model is still required that can reproduce all of the observed flux densities.
 To do so, the non-trivial task of simultaneously solving the radiative transfer equation and non-LTE atomic level populations which include advection will be required.

### 2013-04-22 draft_07/draft.tex
Small few changes to draft 07 from Rathmines

@@
 A failure of the Drake model for $\alpha$ Boo is that it overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
-If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than predicted by the existing models, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
-The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
+If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
+The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O}, which would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
 To investigate this possibility further we adjusted one of the existing models [referred to `Model B' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
 \begin{equation}
-T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{1.65},
+T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{p},
 \label{eq:eq2}
@@
 The spectral index of both $\alpha$ Tau and $\alpha$ Boo at long wavelengths is found to be greater than that expected from a constant property wind.
-For $\alpha$ Tau our longest wavelength detections are still sampling emission from an accelerating region within the outflow while for $\alpha$ Boo the emission probably emanates from a region where the flow is close to, or indeed have reached its terminal velocity.
+For $\alpha$ Tau our longest wavelength detections are still sampling emission from an accelerating region within the outflow while for $\alpha$ Boo the emission probably emanates from a region where the flow is close to, or indeed has reached its terminal velocity.
 Using our new VLA data we have developed a simple analytical model for the outer atmosphere of $\alpha$ Boo which contains a rapid wind cooling profile.

### 2013-04-27 draft_07/draft.tex
27/04 More co-I edits

@@
 This is the first time single (non-binary) luminosity class III red giants have been detected at these continuum wavelengths.
-We find that these flux density measurements sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
+We sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
+For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating.
 We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models based on ultraviolet data.
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function of electron collisionally excited emission lines is sensitive to electron temperature (i.e., $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not hence reflect the global mean value.
-At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the mean thermal wind structure.
+In the UV, the source function, $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature, $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}$).
+Therefore, a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and hence not reflect the global mean radial electron temperature value.
+At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT_{\rm{e}}\nu ^2 /c^2}$).
+This should give a more appropriate estimate of the mean radial electron temperature.
 It is this value that controls the atomic level populations and ionization of the mean plasma that feed into UV spectroscopic analyses.
@@
 
-In the cm-radio regime the radio opacity strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of a stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
+In the cm-radio regime the radio opacity, $ \kappa _{\lambda}$, strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of a stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
 The NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
-Jansky Very Large Array (VLA) is sensitive to over three orders of magnitude in continuum optical depth ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zone of evolved late type stars.
+Jansky Very Large Array (VLA) is sensitive to over three orders of magnitude in continuum optical depth, $\tau _{\lambda}$, ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zone of evolved late type stars.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at large radii due to advection.
@@
 
-\begin{deluxetable}{ccc}
+\begin{deluxetable}{lcc}
 \tabletypesize{\scriptsize}
@@
 \startdata
-Spectral Type 				& K2 III  & K5 III  \\
-HD Number 				& 124897  & 29139  \\
-Mass (M_{\odot})	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
-Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
-Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
-Distance (pc)	& $11.3 \pm 0.1$ & $20.4 \pm 0.3$\\
-Radius ($R_{\odot}$)	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
-Photospheric Escape Velocity & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
-Wind Terminal Velocity & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
-Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
-Wind Temperature (K)		& $\sim$10,000  & $< 10,000$  \\
-Semi-empirical Model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
+Spectral Type$\dotfill$	& K2 III  & K5 III  \\
+HD Number$\dotfill$				& 124897  & 29139  \\
+Mass ($M_{\odot}$)$\dotfill$	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
+Effective Temperature (K)$\dotfill$	& $4294 \pm 30$  & $3970 \pm 49$ \\
+Angular Diameter (mas)$\dotfill$		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
+Distance (pc)$\dotfill$	& $11.3 \pm 0.1$ & $20.4 \pm 0.3$\\
+Radius ($R_{\odot}$)$\dotfill$	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
+Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
+Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
+Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $< 10,000$  \\
+Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
 \enddata
@@
 
-\begin{deluxetable*}{ccccccccc}
+\begin{deluxetable*}{lccccccccc}
 \tabletypesize{\scriptsize}
@@
            	\colhead{Time on Star}            &
+           	\colhead{Restoring Beam}              &
            	\colhead{Bandwidth}            		&
@@
 	\colhead{(hr)}                    			&
+	\colhead{($\arcsec \times \arcsec$ )}                    			&
 	\colhead{(GHz)}                        		&
@@
 \startdata
-$\alpha$ Boo	& 2011 Feb 22 & Q	& 43.3 & 0.7		& 0.3 	&  0.256	&22& J1357+1919  \\
-$\alpha$ Boo 	& 2011 Feb 22 & Ka	& 33.6 & 0.9		& 0.2 	&  0.256 	&23&J1357+1919  \\
-$\alpha$ Boo 	& 2011 Feb 22 & K	& 22.5 & 1.3		& 0.4	&  0.256 	&24&J1357+1919  \\
-$\alpha$ Boo 	& 2011 Feb 11 & X	& 8.5  & 3.5		& 0.3 	&  0.256 	&18&J1415+1320  \\
-$\alpha$ Boo	& 2011 Feb 11 & C	& 5.0  & 6.0 		& 0.5	& 0.256 	&21& J1415+1320 \\
-$\alpha$ Boo	& 2011 Feb 13 & S	& 3.1  & 9.5 		& 1.8 	& 0.256 	&12& J1415+1320 \\
-$\alpha$ Boo 	& 2012 Jul 19 & S	& 3.0  & 10.0 		& 0.7 	& 2.0 		&23& J1415+1320 \\
-$\alpha$ Boo	& 2012 Jul 20 & L	& 1.5  & 20.0		& 1.6 	& 1.0 		&23& J1415+1320 \\
-$\alpha$ Tau	& 2011 Feb 11 & Q	& 43.3 & 0.7 		& 0.3 	& 0.256 	&22&  J0431+1731\\
-$\alpha$ Tau	& 2011 Feb 11 & Ka	& 33.6 & 0.9 		& 0.2 	& 0.256 	&19&  J0449+1121\\
-$\alpha$ Tau	& 2011 Feb 11 & K	& 22.5 & 1.3 		& 0.4 	& 0.256 	&21&  J0449+1121\\
-$\alpha$ Tau	& 2011 Feb 13 & X	&  8.5 & 3.5 		& 0.5	& 0.256 	&25&  J0449+1121\\
-$\alpha$ Tau	& 2011 Feb 13 & C	&  5.0 & 6.0 		& 1.2	& 0.256 	&21&  J0449+1121\\
-$\alpha$ Tau	& 2011 Feb 12 & S	&  3.1 & 9.5 		& 1.8 	& 0.256 	&11&  J0431+2037
+$\alpha$ Boo 	& 2011 Feb 22 & Q	& 43.3 & 0.7		& 0.3 	&0.19 $\times$ 0.15& 0.256	&22& J1357+1919  \\
+				& 2011 Feb 22 & Ka	& 33.6 & 0.9		& 0.2 	&0.25 $\times$ 0.20& 0.256 	&23&J1357+1919  \\
+				& 2011 Feb 22 & K	& 22.5 & 1.3		& 0.4	&0.35 $\times$ 0.28& 0.256 	&24&J1357+1919  \\
+				& 2011 Feb 11 & X	& 8.5  & 3.5		& 0.3 	&1.14 $\times$ 0.70& 0.256 	&18&J1415+1320  \\
+				& 2011 Feb 11 & C	& 5.0  & 6.0 		& 0.5	&2.02 $\times$ 1.30& 0.256 	&21& J1415+1320 \\
+				& 2011 Feb 13 & S	& 3.1  & 9.5 		& 1.8 	&2.57 $\times$ 2.08& 0.256 	&12& J1415+1320 \\
+				& 2012 Jul 19 & S	& 3.0  & 10.0 		& 0.7 	&2.82 $\times$ 2.30& 2.0		&23& J1415+1320 \\
+				& 2012 Jul 20 & L	& 1.5  & 20.0		& 1.6 	&4.46 $\times$ 3.94& 1.0		&23& J1415+1320 \\
+\hline
+\rule{0pt}{3ex}  $\alpha$ Tau	& 2011 Feb 11 & Q	& 43.3 & 0.7 		& 0.3 	&0.18 $\times$0.16& 0.256 	&22&  J0431+1731\\
+				& 2011 Feb 11 & Ka	& 33.6 & 0.9 		& 0.2 	&0.22 $\times$ 0.20& 0.256 	&19&  J0449+1121\\
+				& 2011 Feb 11 & K	& 22.5 & 1.3 		& 0.4 	&0.35 $\times$ 0.31& 0.256 	&21&  J0449+1121\\
+				& 2011 Feb 13 & X	&  8.5 & 3.5 		& 0.5	&0.85 $\times$ 0.78& 0.256 	&25&  J0449+1121\\
+				& 2011 Feb 13 & C	&  5.0 & 6.0 		& 1.2	&1.48 $\times$ 1.32& 0.256 	&21&  J0449+1121\\
+				& 2011 Feb 12 & S	&  3.1 & 9.5 		& 1.8 	&2.74 $\times$ 2.02& 0.256 	&11&  J0431+2037
 \enddata
@@
 For both target sources these high frequency observations were combined into a single 2 hour observing track and commenced with X-band reference pointing with solutions being applied on-line.
-After X-band pointing the target source was observed at Q-band to insure the best pointing solutions were used.
-The tracks at lower frequencies were composed of repeatedly interleaving observations of the target source and a nearby phase calibrator but had longer cycle times.
+After X-band pointing the target source was observed at Q-band to ensure the best pointing solutions were used.
+The tracks at lower frequencies were composed of repeatedly interleaved observations of the target source and a nearby phase calibrator but had longer cycle times.
 The primary calibration sources 3C286 and 3C138 were observed at the end of all tracks and were used to measure the complex bandpass and set the absolute flux for $\alpha$ Boo and $\alpha$ Tau, respectively.
@@
 
-\begin{deluxetable*}{Cccccccc}
+\begin{deluxetable*}{cccccccc}
 \tabletypesize{\scriptsize}
@@
 \tablecaption{VLA Flux Densities of $\alpha$ Boo and $\alpha$ Tau}
-\tablehead{\colhead{}		            &
+\tablehead{\colhead{Star}		            &
 			\colhead{Band}		            &
@@
 			\colhead{Image rms}					&
-           	\colhead{\textit{Imfit} Fitting}  	\\
+           	\colhead{\textit{Imfit} Fitting Error}  	\\
 	\colhead{}									&
@@
 	\colhead{(GHz)}								&
-    \colhead{(mJy)}		        	& 
-    \colhead{(mJy)}		                		& 
-	\colhead{$F_{\nu}$ (\rm{mJy})}                        		& 
-	\colhead{(Jy beam^{-1})}         					&
-	\colhead{Error (mJy)}		}
+    \colhead{(mJy beam$^{-1}$)}		        	& 
+    \colhead{(mJy beam$^{-1}$)}		                		& 
+	\colhead{$F_{\nu}$ (\rm{mJy beam$^{-1}$})}                        		& 
+	\colhead{(mJy beam$^{-1}$)}         					&
+	\colhead{(mJy beam$^{-1}$)}		}
 \startdata
-$\alpha$ Boo (K2 III) &Q  &43.28& 5.941 & 6.093 & 6.420 & 0.301 &  0.261\\
-&Ka &33.56& 4.159 & 4.319 & 4.489 & 0.083 & 0.090 \\
-&K  &22.46& 1.827 & 1.784 & 1.809 & 0.043 & 0.050 \\
-&X  &8.46 & 0.510 & 0.514 & 0.532 & 0.030 & 0.019 \\
-&C  &4.90 & 0.214 & 0.144 & 0.159 & 0.035 & 0.009 \\
-&S  &3.15 & 0.148 & 0.135 & -     & 0.028 & -     \\
-&S  &2.87 & 0.127 & 0.118 & 0.116 & 0.012 & 0.016\\
-&L  &1.63 & 0.067 & 0.068 & -     & 0.013 & -    \\
+$\alpha$ Boo  &Q  &43.28& 5.94 & 6.09 & 6.42 & 0.30 &  0.26\\
+&Ka &33.56& 4.16 & 4.32 & 4.49 & 0.08 & 0.09 \\
+&K  &22.46& 1.83 & 1.78 & 1.81 & 0.04 & 0.05 \\
+&X  &8.46 & 0.51 & 0.51 & 0.53 & 0.03 & 0.02 \\
+&C  &4.90 & 0.21 & 0.14 & 0.16 & 0.04 & 0.01 \\
+&S  &3.15 & 0.15 & 0.14 & -     & 0.03 & -     \\
+&S  &2.87 & 0.13 & 0.12 & 0.12 & 0.01 & 0.02\\
+&L  &1.63 & 0.07 & 0.07 & -     & 0.01 & -    \\
 \hline
-\rule{0pt}{3ex}  $\alpha$ Tau (K5 III)&Q  &43.28 & 3.672& 3.734 & 4.082 &  0.259& 0.183	\\
-&Ka &33.56 & 2.188& 1.962 & 2.125 &  0.091& 0.070 \\
-&K  &22.46 & 1.864& 1.881 & 2.069 &  0.042& 0.083 \\
-&X  &8.46  & 0.296& 0.287 & 0.281 &  0.014& 0.015 \\
-&C  &4.96  & 0.147& 0.167 & 0.176 &  0.010& 0.010 \\
-&S  &3.15  & 0.062& 0.043 & - &  0.017 & -
+\rule{0pt}{3ex}  $\alpha$ Tau &Q  &43.28 & 3.67& 3.73 & 4.08 &  0.26& 0.18	\\
+&Ka &33.56 & 2.19& 1.96 & 2.13 &  0.09& 0.07 \\
+&K  &22.46 & 1.86& 1.88 & 2.07 &  0.04& 0.08 \\
+&X  &8.46  & 0.30& 0.29 & 0.28 &  0.01& 0.02 \\
+&C  &4.96  & 0.15& 0.17 & 0.18 &  0.01& 0.01 \\
+&S  &3.15  & 0.06& 0.04 & - &  0.02 & -
 \enddata
@@
 Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations.
-The lower-frequency maps were contaminated by the emission of a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
-This source was found to have a flux density of 25 mJy at 4.9 GHz by \cite{1986AJ.....91..602D}, in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.
-For unknown reasons we do not detect $\alpha$ Boo in the higher frequency sub-band at 5.0 GHz (C-band) so the values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
+At the lower frequencies, it was necessary to image confusing sources, notably a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
+This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
+We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4; it reaches 80.3 mJy at 1.6 GHz.
+
+We detected $\alpha$ Boo at 6$\sigma$ in the lower frequency sub-band of C-band, at 4.9 GHz.
+The noise was slightly higher and the images were poorer quality in the C-band higher frequency sub-band, with artifacts exceeding $\pm$200 $\mu$Jy, and we cannot report a detection in this sub-band, so values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
 We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
@@
 			\colhead{$F_{\nu}$ (mJy)}				&
-			\colhead{$F_{\nu}/\sigma$}				&
+			\colhead{S/N}				&
           	\colhead{Source} 					}
@@
 
+\begin{figure}
+\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.36,angle=90]{fig0.ps}
+\caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}).
+}
+\label{fig:fig0}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
+\\
+\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz.
+Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and disagree with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
+The overlap between the two models is represented by the green shaded area.
+The red triangles are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
+The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
+\label{fig:fig1}
+\centering
+\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
+\\
+\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
+Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
+The red triangles are the previous radio observations of the star which were acquired over many years.
+The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
+\label{fig:fig2}
+\end{figure*}
+
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$.
@@
 
-\begin{figure*}
-\centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
-\\
-\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz.
-Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and are in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
-The overlap between the two models are represented by the green shaded area.
-The red triangles are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
-The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
-\label{fig:fig1}
-\centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
-\\
-\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
-Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
-The red triangles are the previous radio observations of the star which were acquired over many years.
-The green line is the expected radio emission from the existing hybrid chromosphere and wind model while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
-\label{fig:fig2}
-\end{figure*}
-
 In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromospheric model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
@@
 The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum flux densities confirm that this model predicts a flux excess at even higher frequencies.
-One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
+One possible explanation for this is that the inner atmosphere contains extensive amounts of cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
 This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
@@
 We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
-This model is based on a fully-ionized outflow at a mass loss rate of  6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
+This model is based on a fully-ionized outflow at a mass loss rate of  6.3$\times$10$^{-9}$ $M_{\odot}$ yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
@@
 Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers.
-The radio flux density-frequency relationship for these type of stars is always found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
+The radio flux density-frequency relationship for this type of stars is always found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
 It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
@@
 \begin{figure}
-\includegraphics[trim = 0mm 11mm 0mm 21mm, clip,scale=0.4,angle=90]{fig4.ps}
+\includegraphics[trim = 0mm 11mm 10mm 21mm, clip,scale=0.4,angle=90]{fig4.ps}
 \caption{The variation of density and temperature coefficients for the empirically derived spectral indices.
@@
 \begin{figure}
-\includegraphics[trim = 5mm 0mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
+\includegraphics[trim = 5mm 10mm 10mm 20mm, clip,scale=0.4,angle=90]{fig5.ps}
 \caption{Predicted effective radius (dashed lines) as a function of wavelength derived from the existing atmospheric models of $\alpha$ Boo and $\alpha$ Tau.
-Also plotted is the predicted effective radius derived from our analytical advection model discussed in \ref{disc:disc4}.
+Also plotted is the predicted effective radius derived from our analytical advection model for $\alpha$ Boo (discussed in \ref{disc:disc4}).
 Points corresponding to our long wavelength VLA measurements are also shown.
-At the same radio wavelengths the less ionized and less opaque mass outflow of  Tau results in a smaller effective radius than $\alpha$ Boo.}
+At the same radio wavelengths the less ionized and less opaque mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
 \label{fig:fig5}
@@
 Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
-Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization balance.
-In this scenario the temperature coefficient may be smaller than our derived value here.
+Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction.
+In this scenario the temperature coefficient may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.
 
@@
 
-A failure of the Drake model for $\alpha$ Boo is that it overestimates the radio fluxes at long VLA wavelengths which sample its outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
+A failure of the Drake model for $\alpha$ Boo is that it overestimates the radio fluxes at long VLA wavelengths which sample the outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
 If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
-The main mechanism for this cooling would be adiabatic expansion \citep{2011ASPC..448..691O}, which would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
-To investigate this possibility further we adjusted one of the existing models [referred to `Model B' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
+The main mechanism for such cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
+
+To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [referred to `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
 \begin{equation}
@@
 \end{equation}
-at some distance $r_{1}$, from the star.
-The temperature coefficient used here is that obtained from our new VLA data assuming a steady flow (see Figure \ref{fig:fig4}).
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$.
+at some distance $r_{1}$ from the star, and used the temperature coefficient $p=1.65$ obtained from our new VLA data assuming a constant velocity flow (see Figure \ref{fig:fig4}).
+We introduce the distance $r_{1}$ as the outer limit to ionization processes; at $r > r_{1}$, the ionization fraction is only determined by recombination.
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
 In doing so we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
-\item 1.
+
+1.
 A constant velocity mass outflow, i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
-\item 2.
+
+2.
 All ionization processes cease beyond $r_{1}$.
@@
 When the temperatures begins to decrease in the wind the collisional excitation rate and thus ionization rate decrease rapidly.
-\item 3.
+
+3.
 Only radiative recombination of H is considered and the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S} is included.
@@
 where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
-\item 4. A fixed ion contribution from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
-\item Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
+
+4. A fixed ion contribution from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
+
+Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
 \begin{equation}
@@
 By altering the existing atmospheric model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{H}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{H}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
+This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 
@@
 We have presented the most comprehensive set of multi-wavelength radio continuum observations of two standard luminosity class III red giants to date.
-This is the first time such class of stars have been detected at wavelengths longer than 6 cm.
+This is the first time such stars have been detected at wavelengths longer than 6 cm.
 Such long wavelength detections are crucial if one wants to study the outer environments of these partially ionized stellar outflows.

### 2013-04-30 draft_07/draft.tex
30/4 Work done while invigilating

@@
 This is the first time single (non-binary) luminosity class III red giants have been detected at these continuum wavelengths.
-We sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
+Our long-wavelength data sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
 For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating.
@@
 Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
-We develop a simple analytical atmospheric model for $\alpha$ Boo which includes a rapidly cooling constant velocity wind, and the model is found to be in good agreement with our new long wavelength flux density values.
+We develop a simple analytical wind model for $\alpha$ Boo based on our new long wavelength flux density values.
 
@@
 
+In order to understand the unknown mechanisms which drive the large mass loss rates from evolved spectral-type K through mid-M stars, an understanding of the dynamics and thermodynamics of their atmospheres is essential.
+An important discovery in late-type evolved stellar atmospheres resulted from the first ultraviolet survey of such stars using the International Ultraviolet Explorer (IUE).
+The survey revealed a `transition region dividing line' in the giant branch near spectral type K1 III which separates these stars based on the properties of their atmospheres \citep{1979ApJ...229L..27L}.
+Stars blueward of the dividing line were found to possess chromospheres and transition regions like the Sun, while stars on the red side were found to possess chromospheres and cool winds.
+X-ray observations showed that this dividing line extended to coronal emission \citep{1981ApJ...250..293A}.
+Around the same time, another class of late-type evolved star emerged which showed signs of possessing both a transition region and a cool wind \citep[e.g.,][]{1982A&A...107..292R}.
+Nowadays, many of these so called `hybrid atmosphere' stars show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
+Understanding the exact nature of the atmospheric properties of late-type evolved stars will lead to a broader understanding of the mass-loss process.
+
 Mass loss from late-type evolved stars plays a crucial role in both stellar and galactic evolution and ultimately provides part of of the material required for the next generation of stars and planets.
@@
 There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
-Optical and ultraviolet observations reveal an absence of hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.,][]{1979ApJ...229L..27L,1981ApJ...250..293A}.
+Ultraviolet (UV) and optical observations reveal an absence of significant hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.,][]{1979ApJ...229L..27L,1981ApJ...250..293A}.
 
 Magnetic fields are most likely involved in the mass loss process, although current magnetic models are also unable to explain spectral diagnostics.
-Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} ultraviolet (UV) spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
+Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} UV spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
 These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zone, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, \cite[e.g.,][]{1998ApJ...494..828J}.
@@
 The NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
-Jansky Very Large Array (VLA) is sensitive to over three orders of magnitude in continuum optical depth, $\tau _{\lambda}$, ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zone of evolved late type stars.
+Jansky Very Large Array (VLA) is sensitive to over three orders of magnitude in continuum optical depth, $\tau _{\lambda}$, ($\tau _{20 \ \rm{cm}}/\tau _{0.7 \ \rm{cm}} \approx 10^3$) and provides an area-averaged sweep through the wind acceleration zone of evolved late-type stars.
 The thermodynamic properties in this spatial region control the ionization in the far wind because the ionization balance, which also controls the cooling rates, becomes \textit{frozen-in} at large radii due to advection.
@@
 Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
+%$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
+Rotational Period (days)$\dotfill$ & 233 & 643 \\
 Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
-Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $< 10,000$  \\
+Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<10,000$  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Distances are from \cite{2007A&A...474..653V}.
+Rotaional periods are from \cite{1993ApJ...413..339H}.
 Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
@@
 \subsection{Existing Atmospheric Models} \label{disc2}
-One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
-Figure \ref{fig:fig1} shows the predicted radio spectrum for $\alpha$ Boo from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
-We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free capacities included.
+One of the most important diagnostic features indicating mass outflows in late-type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
+Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \citep{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
+Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity, $v_{\infty}$, of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
+They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are $\sim$50\% ionized.
+We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
 The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
 Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm and this is a good check on the robustness of our method of producing radio spectra from these model atmospheres.
+In reality, substantial departures from spherical symmetry are to be expected in most stellar atmospheres.
+For example, a global magnetic dipole would cause density variations between the equator and the polar regions.
+Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.
 
@@
 The overlap between the two models is represented by the green shaded area.
-The red triangles are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
+The red diamonds are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
 The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
@@
 Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
-The red triangles are the previous radio observations of the star which were acquired over many years.
+The red diamonds are the previous radio observations of the star which were acquired over many years.
 The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
@@
 
-Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity $v_{\infty}$, of $\sim$40 km s${}^{-1}$ by 2 $R _{\star}$.
-They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out.
+Figure \ref{fig:fig1} shows the resulting predicted radio spectrum between 1 GHz and 1 THz for $\alpha$ Boo from these chromosphere and wind models.
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
@@
 We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
-This model is based on a fully-ionized outflow at a mass loss rate of  6.3$\times$10$^{-9}$ $M_{\odot}$ yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
+This model is based on a fully-ionized outflow at a mass loss rate of  6.3 $\times$ 10$^{-9}$ $M_{\odot}$ yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
@@
 To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
-In doing so we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
+To do so, we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
 
@@
 
-4. A fixed ion contribution from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.
-
+4. A fixed ion contribution from metals with a low first ionization potential, $x_{\rm{ion}}=n_{\rm{ion}}/n_{\rm{H}}=10^{-4}$, as these are easily ionized in the outflow.\\
 Using these assumptions it can be shown that the ionization fraction beyond $r_{1}$ is given by \citep{1986ApJ...306..605G}
@@
 \\
-By altering the existing atmospheric model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile and a density profile governed by Equation \ref{eq:eq2}  and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$ respectively, then we get  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model, which still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$, now contains an  initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
+
+We adjusted the value of $r_{1}$ to obtain the best fit to our long wavelength observations and found this happened when $r_{1}$ = 2.3 $R_{\star}$.
+To get this best fit, the existing atmospheric model (i.e.
+the Drake Model) needed to be adjusted so that it now has a narrower temperature plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, and a temperature profile and a density profile governed by Equation \ref{eq:eq2} and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$, respectively.
+This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
+This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 

### 2013-05-01 draft_07/draft.tex
30/4 Small few things

@@
 Nowadays, many of these so called `hybrid atmosphere' stars show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
-Understanding the exact nature of the atmospheric properties of late-type evolved stars will lead to a broader understanding of the mass-loss process.
+Understanding the exact nature of the atmospheric properties of late-type evolved stars will ultimately lead to a broader understanding of the mass-loss process.
 
@@
 Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
-%$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
-Rotational Period (days)$\dotfill$ & 233 & 643 \\
+$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
+$\textit{i}$ (degrees) $\dotfill$ & $58 \pm 25$  & x \\
+Rotation Period (years)$\dotfill$ & $2.0 \pm 0.2$ & 643 \\
 Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
@@
 \hline
-\rule{0pt}{3ex}  $\alpha$ Tau	& 2011 Feb 11 & Q	& 43.3 & 0.7 		& 0.3 	&0.18 $\times$0.16& 0.256 	&22&  J0431+1731\\
+\rule{0pt}{3ex}  $\alpha$ Tau	& 2011 Feb 11 & Q	& 43.3 & 0.7 		& 0.3 	&0.18 $\times$ 0.16& 0.256 	&22&  J0431+1731\\
 				& 2011 Feb 11 & Ka	& 33.6 & 0.9 		& 0.2 	&0.22 $\times$ 0.20& 0.256 	&19&  J0449+1121\\

### 2013-05-01 draft_07/draft.tex
1/5 Morning Invigilation

@@
 Our long-wavelength data sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
-For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating.
-We present spectral energy distributions for both stars and compare these with previous measurements and published semi-empirical models based on ultraviolet data.
-The marked deviations between our data and existing semi-empirical models highlight the need for new atmospheric models to be developed.
+For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating, probably due to its lower mass loss rate and lower level of ionization in its outflow.
+We compare our data with previous measurements and published semi-empirical models based on ultraviolet data and the marked deviations highlight the need for new atmospheric models to be developed.
 Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
-We develop a simple analytical wind model for $\alpha$ Boo based on our new long wavelength flux density values.
+Finally, we develop a simple analytical wind model for $\alpha$ Boo based on our new long wavelength flux density values.
 
@@
 These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
+Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
+Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
 These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.

### 2013-05-01 draft_07/draft.tex
nothing

@@
 
-Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the $\zeta$ Aurigae and symbiotic systems (e.g., \citealt{1970VA.....12..147W}; \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
-Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
-For example, the orbital separation is often within the wind acceleration region and one could expect flow perturbations to be present (e.g., \citealt{1981ApJ...248.1043C}).
-In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
-
-In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III).
-These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
-Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
-These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
-Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
-
 \begin{deluxetable}{lcc}
@@
 \end{deluxetable}
+
+Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the $\zeta$ Aurigae and symbiotic systems (e.g., \citealt{1970VA.....12..147W}; \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
+Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
+For example, the orbital separation is often within the wind acceleration region and one could expect flow perturbations to be present (e.g., \citealt{1981ApJ...248.1043C}).
+In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
+
+In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III).
+These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
+Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
+Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
+These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
+Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
 
@@
 
-Observations of $\alpha$ Boo and $\alpha$ Tau were carried out with the VLA during Open Shared Risk Observing (OSRO) in February 2011 at Q, Ka, K, X, C, and S-band in B-configuration (PI: Harper; program 10C-105).
-$\alpha$ Boo was also observed at S and L-band in July 2012 when the VLA was again in B-configuration (PI: O'Gorman; program 12A-472).
+Observations of $\alpha$ Boo and $\alpha$ Tau were carried out with the VLA during Open Shared Risk Observing (OSRO) in February 2011 at Q, Ka, K, X, C, and S-band in B-configuration (PI: G.
+M.
+Harper, Program ID: 10C-105).
+$\alpha$ Boo was also observed at S and L-band in July 2012 when the VLA was again in B-configuration (PI: E.
+O'Gorman, Program ID: 12A-472).
 Some details of these observations are given in Table \ref{tab:tab2}.

### 2013-05-04 draft_07/draft.tex
4 May: Added Ohnaka discussion

@@
 Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
-$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
-$\textit{i}$ (degrees) $\dotfill$ & $58 \pm 25$  & x \\
-Rotation Period (years)$\dotfill$ & $2.0 \pm 0.2$ & 643 \\
+%$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
+%$\textit{i}$ (degrees) $\dotfill$ & $58 \pm 25$  & x \\
+Rotation Period (yr)$\dotfill$ & $2.0 \pm 0.2$ & 1.8 \\
 Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
@@
 Distances are from \cite{2007A&A...474..653V}.
-Rotaional periods are from \cite{1993ApJ...413..339H}.
+Rotaion periods are from \cite{2006PASP..118.1112G} and \cite{1993ApJ...413..339H}.
 Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
+Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq 14$ yr \citep{2008ApJ...679.1531B}, and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
 These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
@@
 
-The data were flagged, calibrated, and imaged within the Common Astronomical Software Application  \cite[CASA;][]{2007ASPC..376..127M} package.
-Data deemed to be bad by the VLA online system were flagged, as were zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
-Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged.
-For the 2011 low frequency data the two sub-bands were centered at relatively radio frequency interference (RFI) free regions of the bandpass and only a very small amount of RFI had to be flagged.
-The 2012 wide-band data were initially Hanning smoothed (combining adjacent frequency channels with weights 0.25, 0.5, and 0.25) to suppress Gibbs ringing.
-We manually flagged entire sub-bands that were badly contaminated with RFI.
-The \textit{testautoflag} task was then used to conservatively flag RFI from all sources and any remaining RFI was manually flagged.
-
-In order to calibrate the data, we solved for the complex gains of the calibration sources while applying the bandpass solution, which was derived from the relevant flux calibrator.
-The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard \citep{2013ApJS..204...19P}.
-At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively, which were scaled according to their spectral indices.
-The more frequently observed phase calibrators were then used to calibrate the amplitude and phases of the targets.
-Atmospheric opacity corrections were also applied to the high frequency data sets using the average of a seasonal model (based on many years of measurements) and information from the weather station obtained during the observations.
-
-The visibilities were then both Fourier transformed and deconvolved using the CASA \textit{clean} task in multi-frequency synthesis imaging mode, which separately grids the multiple spectral channels onto the \textit{u-v} plane and therefore improves the overall \textit{u-v} coverage.
-We used natural weighting for maximum sensitivity and the cell size was chosen so that the synthesized beam was about five pixels across.
-For the high frequencies it was usually sufficient to place just one CLEAN circle around the target source.
-For the low frequencies however, the image sizes were usually set to a few times the size of the primary beam so that nearby strong serendipitous sources could be CLEANed thus reducing their sidelobe contamination of the final image.
-These images were CLEANed interactively, taking sky curvature into account, down to about the $3\sigma$  level with clean boxes placed around sources as they appeared in the residual image.
-All images were corrected for  primary beam attenuation.
-
-In each image the flux density from the unresolved target source was calculated by, 1) taking the peak pixel value from the source, 2) manually integrating the flux density around the source, and 3) fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
-Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}.
-For weak detections (i.e., $F_{\nu} \lesssim 5\sigma$) we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may produce biased parameter estimates \citep{1999ASPC..180.....T}.
-The flux density values used in Section \ref{disc:disc0} are the peak values listed in Table \ref{tab:tab3}.
-We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies \citep{2013ApJS..204...19P}.
-
 \begin{deluxetable*}{cccccccc}
@@
 
+The data were flagged, calibrated, and imaged within the Common Astronomical Software Application  \cite[CASA;][]{2007ASPC..376..127M} package.
+Data deemed to be bad by the VLA online system were flagged, as were zeros, non-operational antennae, dummy scans at the beginning of each track, and poorly performing antennae.
+Visual inspection of each scan was carried out to determine if data at the beginning or end of these scans needed to be flagged.
+For the 2011 low frequency data the two sub-bands were centered at relatively radio frequency interference (RFI) free regions of the bandpass and only a very small amount of RFI had to be flagged.
+The 2012 wide-band data were initially Hanning smoothed (combining adjacent frequency channels with weights 0.25, 0.5, and 0.25) to suppress Gibbs ringing.
+We manually flagged entire sub-bands that were badly contaminated with RFI.
+The \textit{testautoflag} task was then used to conservatively flag RFI from all sources and any remaining RFI was manually flagged.
+
+In order to calibrate the data, we solved for the complex gains of the calibration sources while applying the bandpass solution, which was derived from the relevant flux calibrator.
+The amplitude gains of the phase calibrators were scaled according to values derived from the flux calibrators using the ``Perley-Butler 2010" flux density standard \citep{2013ApJS..204...19P}.
+At the time, no Ka or S-band flux density standard models were available so instead for these we used the K and L-band models, respectively, which were scaled according to their spectral indices.
+The more frequently observed phase calibrators were then used to calibrate the amplitude and phases of the targets.
+Atmospheric opacity corrections were also applied to the high frequency data sets using the average of a seasonal model (based on many years of measurements) and information from the weather station obtained during the observations.
+
+The visibilities were then both Fourier transformed and deconvolved using the CASA \textit{clean} task in multi-frequency synthesis imaging mode, which separately grids the multiple spectral channels onto the \textit{u-v} plane and therefore improves the overall \textit{u-v} coverage.
+We used natural weighting for maximum sensitivity and the cell size was chosen so that the synthesized beam was about five pixels across.
+For the high frequencies it was usually sufficient to place just one CLEAN circle around the target source.
+For the low frequencies however, the image sizes were usually set to a few times the size of the primary beam so that nearby strong serendipitous sources could be CLEANed thus reducing their sidelobe contamination of the final image.
+These images were CLEANed interactively, taking sky curvature into account, down to about the $3\sigma$  level with clean boxes placed around sources as they appeared in the residual image.
+All images were corrected for  primary beam attenuation.
+
+In each image the flux density from the unresolved target source was calculated by, 1) taking the peak pixel value from the source, 2) manually integrating the flux density around the source, and 3) fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
+Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}.
+For weak detections (i.e., $F_{\nu} \lesssim 5\sigma$) we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may produce biased parameter estimates \citep{1999ASPC..180.....T}.
+The flux density values used in Section \ref{disc:disc0} are the peak values listed in Table \ref{tab:tab3}.
+We assume absolute flux density scale systematic uncertainties of  3\% at all frequencies \citep{2013ApJS..204...19P}.
+
 \section{RESULTS}
@@
 We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4; it reaches 80.3 mJy at 1.6 GHz.
-
-We detected $\alpha$ Boo at 6$\sigma$ in the lower frequency sub-band of C-band, at 4.9 GHz.
-The noise was slightly higher and the images were poorer quality in the C-band higher frequency sub-band, with artifacts exceeding $\pm$200 $\mu$Jy, and we cannot report a detection in this sub-band, so values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
-We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
-We can therefore safely assume that the 1.5 GHz (L-band) flux density has not changed significantly over that period either, and so can safely be included in any analysis.
-The map at L-band was highly contaminated by the sidelobes of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level.
-There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
-However, the position uncertainties, due to noise and to the atmospheric differences between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
-
-\subsection{$\alpha$ Tau Radio Maps} \label{results2}
-The final deconvolved radio maps of $\alpha$ Tau were of excellent quality with the rms noise reaching the predicted noise levels in many cases.
-The target field at all frequencies was free from strong serendipitous radio sources and thus the final images were free of the sidelobe contamination that were present in the low frequency $\alpha$ Boo images.
-$\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had flux densities of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively.
-Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
-Due to the limited number of S-band receivers available at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection.
-We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density.
 
@@
 \end{deluxetable*}
+
+We detected $\alpha$ Boo at 6$\sigma$ in the lower frequency sub-band of C-band, at 4.9 GHz.
+The noise was slightly higher and the images were poorer quality in the C-band higher frequency sub-band, with artifacts exceeding $\pm$200 $\mu$Jy, and we cannot report a detection in this sub-band, so values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
+We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
+We can therefore safely assume that the 1.5 GHz (L-band) flux density has not changed significantly over that period either, and so can safely be included in any analysis.
+The map at L-band was highly contaminated by the sidelobes of the strong source north-west of $\alpha$ Boo but the star is still detected at the $5\sigma$ level.
+There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
+However, the position uncertainties, due to noise and to the atmospheric differences between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
+
+\subsection{$\alpha$ Tau Radio Maps} \label{results2}
+The final deconvolved radio maps of $\alpha$ Tau were of excellent quality with the rms noise reaching the predicted noise levels in many cases.
+The target field at all frequencies was free from strong serendipitous radio sources and thus the final images were free of the sidelobe contamination that were present in the low frequency $\alpha$ Boo images.
+$\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had flux densities of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively.
+Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
+Due to the limited number of S-band receivers available at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection.
+We report a tentative $3\sigma$ detection of $\alpha$ Tau at 3.1 GHz when we take its peak pixel value as its total flux density.
 
@@
 The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization, and have higher mass loss rates and outflow velocities than the established values given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
+
+Recently, \cite{2013A&A...553A...3O} has suggested that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e.
+a so-called MOLsphere) which extends out to $2.5  \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$ and a geometrical extent of 0.1 $R_{\star}$.
+It can be shown that a MOLsphere with these properties would be optically thick between 3 and 10 cm (i.e.
+X, C and S-band) if we assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim 1 \times 10^{-5}\ n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
+Using the assumption then of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe.
+In the next section we argue that the radio emission from $\alpha$ Tau at these long VLA wavelengths comes from a region much closer in to the star suggesting that the MOLsphere has either a lower column depth or has a much larger geometrical width in order to make it optically thin at these wavelengths.
 

### 2013-05-06 draft_07/draft.tex
6th May: Edits from Rathmines

@@
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<10,000$  \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<$10,000  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq 14$ yr \citep{2008ApJ...679.1531B}, and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
+Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
 These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
@@
 This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4; it reaches 80.3 mJy at 1.6 GHz.
+We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.
 
@@
 
+\begin{figure*}
+\centering
+\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig0.ps}
+\\
+\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz.
+Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and disagree with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
+The overlap between the two models is represented by the green shaded area.
+The red diamonds are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
+The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
+\label{fig:fig1}
+\centering
+\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
+\\
+\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
+Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
+The red diamonds are the previous radio observations of the star which were acquired over many years.
+The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
+\label{fig:fig2}
+\end{figure*}
+
 Previous detections of $\alpha$ Boo at 6 cm ranged from a 3$\sigma$ upper limit of 0.18 mJy to a 3$\sigma$ detection at 0.39 mJy.
@@
 \subsection{Existing Atmospheric Models} \label{disc2}
-One of the most important diagnostic features indicating mass outflows in late-type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
+One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
 Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \citep{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
-Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity, $v_{\infty}$, of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
-They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are $\sim$50\% ionized.
-We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
+Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
+They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are 50\% ionized.
+We compute the expected radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
 The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
@@
 \begin{figure}
-\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.36,angle=90]{fig0.ps}
+\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.36,angle=90]{fig2.ps}
 \caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}).
-}
+The original Drake Model has a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$ 20 $R_{\star}$ (solid black line), reaches a terminal velocity of 35-40 km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and has a wind which is 50\% ionized (dashed and dotted black lines).}
 \label{fig:fig0}
 \end{figure}
-
-\begin{figure*}
-\centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
-\\
-\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz.
-Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and disagree with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}.
-The overlap between the two models is represented by the green shaded area.
-The red diamonds are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA.
-The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
-\label{fig:fig1}
-\centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
-\\
-\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz.
-Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
-The red diamonds are the previous radio observations of the star which were acquired over many years.
-The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
-\label{fig:fig2}
-\end{figure*}
 
@@
 
-Recently, \cite{2013A&A...553A...3O} has suggested that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e.
+Recently, \cite{2013A&A...553A...3O} has found that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e.
 a so-called MOLsphere) which extends out to $2.5  \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$ and a geometrical extent of 0.1 $R_{\star}$.
 It can be shown that a MOLsphere with these properties would be optically thick between 3 and 10 cm (i.e.
-X, C and S-band) if we assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim 1 \times 10^{-5}\ n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
+X, C and S-band) if we conservatively assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
 Using the assumption then of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe.
@@
 Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers.
-The radio flux density-frequency relationship for this type of stars is always found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
+The radio flux density-frequency relationship for these stars is usually found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
 It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
@@
 \includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
-\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices.}
+\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices.
+The spectral index for $\alpha$ Boo and $\alpha$ Tau are found to be 1.05 and 1.58, respectively, which are both larger than the 0.6 value expected for a constant property wind model.}
 \label{fig:fig3}
@@
 Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction.
-In this scenario the temperature coefficient may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.
+In this scenario the temperature coefficient $n$, may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.
 
@@
 We adjusted the value of $r_{1}$ to obtain the best fit to our long wavelength observations and found this happened when $r_{1}$ = 2.3 $R_{\star}$.
-To get this best fit, the existing atmospheric model (i.e.
-the Drake Model) needed to be adjusted so that it now has a narrower temperature plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, and a temperature profile and a density profile governed by Equation \ref{eq:eq2} and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$, respectively.
+To get this best fit, the existing atmospheric model (plotted in Figure \ref{fig:fig0}) needed to be adjusted so that it now has a narrower and slightly larger temperature plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, and a temperature profile and a density profile governed by Equation \ref{eq:eq2} and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$, respectively.
 This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.

### 2013-05-07 draft_07/draft.tex
7th May: Mag Field stuff in sec 3.3

@@
 For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating, probably due to its lower mass loss rate and lower level of ionization in its outflow.
-We compare our data with previous measurements and published semi-empirical models based on ultraviolet data and the marked deviations highlight the need for new atmospheric models to be developed.
+We compare our data with published semi-empirical models based on ultraviolet data and the marked deviations highlight the need for new atmospheric models to be developed.
 Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
@@
 \subsection{$\alpha$ Boo Radio Maps} \label{results1} 
-High S/N detections ($>19\sigma$) of $\alpha$ Boo were made at 22.5, 33.6, and 43.3 GHz.
+High S/N detections ($>$19$\sigma$) of $\alpha$ Boo were made at 22.5, 33.6, and 43.3 GHz.
 Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations.
@@
 &4.9  & 1983 May 20 & 0.26 & 3.3& \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 Dec 26 & $\le 0.18 \ (3\sigma)$&- & \cite{1986AJ.....91..602D} \\
+&4.9  & 1983 Dec 26 & $\le$0.18  $(3\sigma)$&- & \cite{1986AJ.....91..602D} \\
 &4.9  & 1984 Mar 17 & 0.24  & 4.8& \cite{1986AJ.....91..602D} \\
@@
 \hline
-\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27 \ (3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Nov 6 & $\le 0.22 \ (3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le 0.07 \ (3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
+\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le$0.27 $(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&4.9  & 1984 Nov 6 & $\le$0.22 $(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&5.0  & 1997 Sep 27 & $\le$0.07 $(3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
 &8.5  & 1997 Sep 27 & 0.28 	&9.3	& \cite{2007ApJ...655..946W} \\
@@
 The noise was slightly higher and the images were poorer quality in the C-band higher frequency sub-band, with artifacts exceeding $\pm$200 $\mu$Jy, and we cannot report a detection in this sub-band, so values given in Table \ref{tab:tab3} are taken from the lower frequency sub-band only.
-We obtain good detections ($>5\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
+We obtain good detections ($>$5$\sigma$) of the star for both epochs at $\sim$3 GHz (S-band) and the peak flux densities agree within their uncertainties.
 We can therefore safely assume that the 1.5 GHz (L-band) flux density has not changed significantly over that period either, and so can safely be included in any analysis.
@@
 $\alpha$ Tau was the only source in the high frequency maps while the brightest source in the low frequency maps was located $106\arcsec$ north north-east of $\alpha$ Tau and had flux densities of 0.85, 1.35, and 1.7 mJy at 8.5, 5.0, and 3.5 GHz, respectively.
-Strong detections ($>14\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
+Strong detections ($>$14$\sigma$) of $\alpha$ Tau were made at all frequencies between 5.0 and 43.3 GHz.
 Due to the limited number of S-band receivers available at the time, a full 2.5 hr track was dedicated to $\alpha$ Tau at 3.1 GHz in order to achieve the required sensitivity to give a possible detection.
@@
 \caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}).
-The original Drake Model has a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$ 20 $R_{\star}$ (solid black line), reaches a terminal velocity of 35-40 km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and has a wind which is 50\% ionized (dashed and dotted black lines).}
+The original Drake Model has a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$20 $R_{\star}$ (solid black line), reaches a terminal velocity of 35-40 km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and has a wind which is 50\% ionized (dashed and dotted black lines).}
 \label{fig:fig0}
@@
 Figure \ref{fig:fig1} shows the resulting predicted radio spectrum between 1 GHz and 1 THz for $\alpha$ Boo from these chromosphere and wind models.
-At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim\nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
+At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim \nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
 At low frequencies however, where the models predict the wind to have constant velocity, ionization fraction and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
@@
 X, C and S-band) if we conservatively assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
-Using the assumption then of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe.
+Using the assumption of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe.
 In the next section we argue that the radio emission from $\alpha$ Tau at these long VLA wavelengths comes from a region much closer in to the star suggesting that the MOLsphere has either a lower column depth or has a much larger geometrical width in order to make it optically thin at these wavelengths.
@@
 One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from if the thermal gradients are assumed to be small.
-Ignoring thermal gradients may be reasonable over the wind acceleration region since it is probable that some sort of Alfv\'en waves are required to lift the material out of the gravitational potential and large damping lengths would be needed to do so.
+Ignoring thermal gradients may be reasonable over the wind acceleration region since it is probable that some form of Alfv\'en waves are required to lift the material out of the gravitational potential.
+These waves would need to have large damping lengths and undergo some dissipation within a few stellar radii of the surface in order to produce the low terminal velocities \citep{1980ApJ...242..260H}.
 These large damping lengths could result in low thermal gradients close in.
-If we too make this assumption then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
+If we ignore thermal gradients, then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
 This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may be have substantial thermal gradients.

### 2013-05-10 draft_07/draft.tex
Added vladamir comment

@@
 In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value.
-This hint of variability at long wavelengths can only again be confirmed with future high S/N observations.
+This hint of variability at long wavelengths would be in agreement with the broadband nonlinear Alfv\'{e}n wave model of \cite{2010ApJ...723.1210A} but can only be confirmed with future high S/N observations.
 

### 2013-05-14 draft_07/draft.tex
14/5 Slightly changed Figs 2 & 5

@@
 
-In order to understand the unknown mechanisms which drive the large mass loss rates from evolved spectral-type K through mid-M stars, an understanding of the dynamics and thermodynamics of their atmospheres is essential.
+In order to understand the unknown mechanisms which drive the $10^{-9}-10^{-11}$ $M_{\odot}$ yr$^{-1}$ mass loss rates from evolved spectral-type K through mid-M stars, an understanding of the dynamics and thermodynamics of their atmospheres is essential.
 An important discovery in late-type evolved stellar atmospheres resulted from the first ultraviolet survey of such stars using the International Ultraviolet Explorer (IUE).
@@
 Around the same time, another class of late-type evolved star emerged which showed signs of possessing both a transition region and a cool wind \citep[e.g.,][]{1982A&A...107..292R}.
-Nowadays, many of these so called `hybrid atmosphere' stars show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
-Understanding the exact nature of the atmospheric properties of late-type evolved stars will ultimately lead to a broader understanding of the mass-loss process.
+Many of these so called `hybrid atmosphere' stars now show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
+Understanding the nature of the atmospheric structure of late-type evolved stars will ultimately lead to a broader understanding of the mass-loss process.
 
@@
 A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not yet in agreement with observations \citep{2009AIPC.1094..267C}.
-It has also been suggested that the winds may be driven by some form of magnetic pressure acting on very highly clumped wind material \citep{2008AJ....136.1964E} but \cite{2010ApJ...720.1767H} does not find support for this hypothesis.
+It has also been suggested that the winds may be driven by some form of magnetic pressure acting on very highly clumped wind material \citep{2008AJ....136.1964E} but \cite{2010ApJ...720.1767H} does not find compelling evidence for this hypothesis.
 Progress in this field continues to be driven by observations that provide new insights into the mass loss problem.
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function, $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature, $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}$).
+In the UV, the source function, $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature, $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}/\sqrt{T_{\rm{e}}}$).
 Therefore, a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and hence not reflect the global mean radial electron temperature value.
@@
 Rotation Period (yr)$\dotfill$ & $2.0 \pm 0.2$ & 1.8 \\
+$\lbrack$Fe/H$\rbrack\dotfill$ & $-0.5 \pm 0.2$ & $-0.15 \pm 0.2$  \\
 Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<$10,000  \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $\sim$10,000  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Rotaion periods are from \cite{2006PASP..118.1112G} and \cite{1993ApJ...413..339H}.
-Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
+Metallicities are from \cite{2003A&A...400..709D}.
+Wind properties are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
 
@@
 In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
-
-In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III).
-These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
-Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
-Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
-These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
-Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
 
@@
 \end{deluxetable*}
+
+In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III).
+These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
+Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
+Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
+These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
+Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.
 

### 2013-05-15 draft_07/draft.tex
15th May: Final edits before 2nd submission to co-Authors

@@
 Jansky Very Large Array (VLA) thermal continuum observations of the wind acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Importantly, most of our observations of each star were carried out over just a few days, so that we obtained an essentially consistent snapshot of the different stellar layers sampled at different wavelengths, independent of any long-term variability.
+Importantly, most of our observations of each star were carried out over just a few days, so that we obtained an essentially consistent snapshot of the different stellar atmospheric layers sampled at different wavelengths, independent of any long-term variability.
 We report the first detections at several wavelengths for each star including a detection at 10 cm (3.0 GHz: S-band) for both stars and a 20 cm (1.5 GHz: L-band) detection for $\alpha$ Boo.
@@
 Our long-wavelength data sample the outer layers of $\alpha$ Boo's atmosphere where its wind velocity is approaching (or possibly has reached) its terminal value and the ionization balance is becoming \textit{frozen-in}.
-For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating, probably due to its lower mass loss rate and lower level of ionization in its outflow.
+For $\alpha$ Tau however, our long-wavelength data is still sampling its inner atmosphere where the wind is still accelerating probably due to its lower mass loss rate.
 We compare our data with published semi-empirical models based on ultraviolet data and the marked deviations highlight the need for new atmospheric models to be developed.
@@
 Around the same time, another class of late-type evolved star emerged which showed signs of possessing both a transition region and a cool wind \citep[e.g.,][]{1982A&A...107..292R}.
-Many of these so called `hybrid atmosphere' stars now show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
+Many of these so called `hybrid atmosphere' stars now also show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
 Understanding the nature of the atmospheric structure of late-type evolved stars will ultimately lead to a broader understanding of the mass-loss process.
@@
 &4.9  & 1983 May 20 & 0.26 & 3.3& \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 Dec 26 & $\le$0.18  $(3\sigma)$&- & \cite{1986AJ.....91..602D} \\
+&4.9  & 1983 Dec 26 & $\le$0.18$(3\sigma)$&- & \cite{1986AJ.....91..602D} \\
 &4.9  & 1984 Mar 17 & 0.24  & 4.8& \cite{1986AJ.....91..602D} \\
@@
 \hline
-\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le$0.27 $(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Nov 6 & $\le$0.22 $(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le$0.07 $(3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
+\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le$0.27$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&4.9  & 1984 Nov 6 & $\le$0.22$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&5.0  & 1997 Sep 27 & $\le$0.07$(3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
 &8.5  & 1997 Sep 27 & 0.28 	&9.3	& \cite{2007ApJ...655..946W} \\
@@
 Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011.
-The red diamonds are the previous radio observations of the star which were acquired over many years.
+The red diamonds are the previous radio observations of the star which were acquired over many years (see Table \ref{tab:tab4}).
 The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
@@
 
-Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind and low mass-loss rate.
+In Figure \ref{fig:fig2} we plot the previous  radio measurements of $\alpha$ Tau at all frequencies below 250 GHz (i.e.
+0.12 cm).
+Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its relatively low mass-loss rate.
 Our lack of a Ku-band measurement means that we can only compare the previous 3 cm detection reported in \cite{2007ApJ...655..946W} to ours.
@@
 One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
-Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \citep{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
+Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
-They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are 50\% ionized.
+They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are 50\% ionized.
 We compute the expected radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
@@
 \caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}).
-The original Drake Model has a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$20 $R_{\star}$ (solid black line), reaches a terminal velocity of 35-40 km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and has a wind which is 50\% ionized (dashed and dotted black lines).}
+The original Drake Model's have a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$20 $R_{\star}$ (solid black line), reach a terminal velocity of $35-40$ km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and have a wind which is 50\% ionized (dashed and dotted black lines).}
 \label{fig:fig0}
@@
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim \nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
-At low frequencies however, where the models predict the wind to have constant velocity, ionization fraction and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+At low frequencies however, where the Drake models predict the wind to have constant velocity, ionization fraction and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
 The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
@@
 The discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e., it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
-We will discuss these possibilities in the following sections.
+We will discuss these possibilities further in sections \ref{disc:disc3} and \ref{disc:disc4}.
 
@@
 The McMurry model, which contains  the photospheric model of \cite{1973ApJ...180...81J}, is based on high S/N Hubble UV spectra and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
-Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value by 3 $R_{\star}$.
-We assume the wind to have a constant temperature of 8,000 K and have a constant ionization fraction, $x_{e}$, of 0.01 throughout.
+Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
+We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, in agreement with the ionization fraction at the corresponding temperature in the McMurry model.
+
 The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $\nu >$ 30 GHz) but does well in reproducing the VLA flux densities below 30 GHz.
@@
 This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
+The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at all nearly all VLA wavelengths, and only contributes a very small flux density at the longest wavelengths.
+As our model matches the data reasonably well below 30 GHz we conclude that $\alpha$ Tau's wind is optically thin and the VLA radio emission at all wavelengths emanates from the inner atmosphere.
 
@@
 Recently, \cite{2013A&A...553A...3O} has found that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e.
-a so-called MOLsphere) which extends out to $2.5  \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$ and a geometrical extent of 0.1 $R_{\star}$.
-It can be shown that a MOLsphere with these properties would be optically thick between 3 and 10 cm (i.e.
-X, C and S-band) if we conservatively assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
-Using the assumption of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe.
-In the next section we argue that the radio emission from $\alpha$ Tau at these long VLA wavelengths comes from a region much closer in to the star suggesting that the MOLsphere has either a lower column depth or has a much larger geometrical width in order to make it optically thin at these wavelengths.
+a so-called MOLsphere) which extends out to $2.5 \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, and a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$.
+They were unable to constrain the geometrical thickness, $\Delta L$, of the MOLsphere from their data however and arbitrarily fixed it to 0.1 $R_{\star}$.
+It can be shown that such a MOLsphere would have an optical depth of $\tau _{\rm{6 cm}} = 4.5$ at C-band and would produce a corresponding flux density of  0.06 mJy which is considerably lower than our high S/N measurement of 0.15 mJy.
+Here, we have conservatively assumed that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
+We have also assumed the CO filling factor to be unity.
+It can be shown that the MOLsphere becomes optically thin at C-band (i.e.
+$\tau _{\rm{3 cm}} < 1$) for $\Delta L >$ 1.2 $R_{\star}$.
+In the next section we argue that the radio emission from $\alpha$ Tau even at long VLA wavelengths comes from a region much closer in to the star which suggests that the MOLsphere has either has a geometrical width  $\ge$1.2 $R _{\star}$ or has a filling factor less than unity.
 
@@
 If we ignore thermal gradients, then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may be have substantial thermal gradients.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may have substantial thermal gradients.
 
@@
 Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
-Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction.
-In this scenario the temperature coefficient $n$, may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.
+Finally, the wind ionization balance may not have become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from.
+If this is true, then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction.
+In this scenario the temperature coefficient $n$, would be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.
 
@@
 The ionization of hydrogen in the chromosphere and wind is a two stage process: the $n = 2$ level is excited by electron collisions and Lyman-alpha scattering, followed by photoionization by the optically thin Balmer continuum.
-When the temperatures begins to decrease in the wind the collisional excitation rate and thus ionization rate decrease rapidly.
+When the temperature begins to decrease in the wind the collisional excitation rate and thus ionization rate decrease rapidly.
 
@@
 \begin{equation}
-\alpha _{B} = \alpha _{B}(r_{1})\left[\frac{T(r_1)}{T(r)}\right]^{0.77},
+\alpha _{B} = \alpha _{B}(r_{1})\left[\frac{T_{e}(r_1)}{T_{e}(r)}\right]^{0.77},
 \label{eq:eq3}

### 2013-05-21 draft_08/draft.tex
21st May: Added Steve's and Alex's comments

--- 2013-05-15 draft_07/draft.tex
@@
 
-In order to understand the unknown mechanisms which drive the $10^{-9}-10^{-11}$ $M_{\odot}$ yr$^{-1}$ mass loss rates from evolved spectral-type K through mid-M stars, an understanding of the dynamics and thermodynamics of their atmospheres is essential.
+In order to understand the mechanisms which drive the $10^{-9}-10^{-11}$ $M_{\odot}$ yr$^{-1}$ mass loss rates from evolved spectral-type K through mid-M stars, an understanding of the dynamics and thermodynamics of their atmospheres is essential.
 An important discovery in late-type evolved stellar atmospheres resulted from the first ultraviolet survey of such stars using the International Ultraviolet Explorer (IUE).
@@
 In the UV, the source function, $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature, $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}/\sqrt{T_{\rm{e}}}$).
-Therefore, a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and hence not reflect the global mean radial electron temperature value.
+Therefore, a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and hence not reflect the mean radial electron temperature distribution.
 At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e., $S_{\nu} = {2kT_{\rm{e}}\nu ^2 /c^2}$).
@@
 $\lbrack$Fe/H$\rbrack\dotfill$ & $-0.5 \pm 0.2$ & $-0.15 \pm 0.2$  \\
-Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
+Wind Terminal Velocity$\dotfill$ & $35-40$\,km\,s$^{-1}$ & 30\,km\,s$^{-1}$ \\
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
@@
 \subsection{Results Versus Previous Observations} \label{disc1}
-Prior to and during the early operation of the `old' VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g., \citealt{1981ApJ...245L..71B}).
-These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were false (e.g., \citealt{1992MNRAS.254....1B}).
+Prior to and during the early operation of the `old' VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g., \citealt{1989MNRAS.239..913S}).
+These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were spurious (e.g., \citealt{1992MNRAS.254....1B}).
 The first definitive detection of thermal free-free emission from a luminosity class III single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}.
@@
 Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
-Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values.
+Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may lead to larger phase errors and thus lower final flux density values.
 Future high frequency VLA observations of $\alpha$ Boo will clarify this discrepancy at 0.7 cm but past detections at longer wavelengths appear to be in good agreement with our data.
@@
 In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value.
-This hint of variability at long wavelengths would be in agreement with the broadband nonlinear Alfv\'{e}n wave model of \cite{2010ApJ...723.1210A} but can only be confirmed with future high S/N observations.
+This hint of variability at long wavelengths would be consistent with the predictions of the broadband nonlinear Alfv\'{e}n wave model of \cite{2010ApJ...723.1210A} but can only be confirmed with future high S/N observations.
 
 \subsection{Existing Atmospheric Models} \label{disc2}
-One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines.
-Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer.
+One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Ca II H and K and Mg II h and k resonance lines.
+Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg II k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
-They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are 50\% ionized.
+They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is 50\% ionized.
 We compute the expected radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
 The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
-Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm and this is a good check on the robustness of our method of producing radio spectra from these model atmospheres.
-In reality, substantial departures from spherical symmetry are to be expected in most stellar atmospheres.
-For example, a global magnetic dipole would cause density variations between the equator and the polar regions.
+Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm.
+Departures from spherical symmetry are to be expected in magnetic stellar atmospheres.
+For example, $\alpha$ Boo is now known to have an inclination axis of 58$^{\circ} \pm$25$^{\circ}$ \citep{2006PASP..118.1112G} and a global magnetic dipole could cause density variations between the equator and the polar regions.
 Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.
@@
 At high frequencies our VLA data indicates a flux excess which is in agreement with previous mm-observations.
-The discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e., it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis.
-We will discuss these possibilities further in sections \ref{disc:disc3} and \ref{disc:disc4}.
+The discrepancy at low frequencies may be due to a lower ionization fraction in the wind, or a lower mass loss rate than that used in the Drake model.
 
@@
 Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
-We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, in agreement with the ionization fraction at the corresponding temperature in the McMurry model.
+We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.
 
@@
 This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
-The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at all nearly all VLA wavelengths, and only contributes a very small flux density at the longest wavelengths.
+The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at nearly all VLA wavelengths, and only contributes a very small flux density at the longest wavelengths.
 As our model matches the data reasonably well below 30 GHz we conclude that $\alpha$ Tau's wind is optically thin and the VLA radio emission at all wavelengths emanates from the inner atmosphere.
 
-We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can test the robustness of theoretical models.
-This model is based on a fully-ionized outflow at a mass loss rate of  6.3 $\times$ 10$^{-9}$ $M_{\odot}$ yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
+We also include the predicted radio spectrum from the theoretical Alfv\'{e}n wave-driven outflow model for $\alpha$ Tau \citep{1989AcA....39..51K} in Figure \ref{fig:fig2} to demonstrate how radio observations can empirically challenge theoretical models.
+This model has a fully-ionized outflow inside 10 $R_{\star}$, and has a mass loss rate of  6.3 $\times$ 10$^{-9}$ $M_{\odot}$ yr$^{-1}$, more than two orders of magnitude higher than the more recent estimate given in Table \ref{tab:tab1}.
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization, and have higher mass loss rates and outflow velocities than the established values given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
+The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
 
-Recently, \cite{2013A&A...553A...3O} has found that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e.
-a so-called MOLsphere) which extends out to $2.5 \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, and a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$.
-They were unable to constrain the geometrical thickness, $\Delta L$, of the MOLsphere from their data however and arbitrarily fixed it to 0.1 $R_{\star}$.
-It can be shown that such a MOLsphere would have an optical depth of $\tau _{\rm{6 cm}} = 4.5$ at C-band and would produce a corresponding flux density of  0.06 mJy which is considerably lower than our high S/N measurement of 0.15 mJy.
+Recently, \cite{2013A&A...553A...3O} has detected a layer of CO in the outer atmosphere of $\alpha$ Tau (i.e.
+a so-called MOLsphere) which extends out to $\sim$2.5 $R_{\star}$, has a temperature of $1500 \ \pm 200$ K, and a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$.
+They were unable to constrain the geometrical thickness, $\Delta L$, of the MOLsphere from the data however, and arbitrarily fixed it to 0.1 $R_{\star}$.
+It can be shown that such a MOLsphere would have an optical depth of $\tau _{\rm{6\,cm}} = 4.6$ at C-band and would produce a corresponding flux density of  0.06 mJy which is considerably lower than our high S/N measurement of 0.15 mJy.
 Here, we have conservatively assumed that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density.
 We have also assumed the CO filling factor to be unity.
-It can be shown that the MOLsphere becomes optically thin at C-band (i.e.
-$\tau _{\rm{3 cm}} < 1$) for $\Delta L >$ 1.2 $R_{\star}$.
-In the next section we argue that the radio emission from $\alpha$ Tau even at long VLA wavelengths comes from a region much closer in to the star which suggests that the MOLsphere has either has a geometrical width  $\ge$1.2 $R _{\star}$ or has a filling factor less than unity.
+It can also be shown that the MOLsphere becomes optically thin at C-band (i.e.
+$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$.
+In the next section we argue that the radio emission from $\alpha$ Tau even at long VLA wavelengths comes from a region much closer in to the star which suggests that the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
 
@@
 
-Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that describe their outflow.
+Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that may describe their outflow.
 The combinations of the electron temperature and density coefficients are shown for each star in Figure \ref{fig:fig4} along with the coefficients obtained by assuming either an isothermal flow or a constant velocity flow.
-One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from if the thermal gradients are assumed to be small.
+One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.
 Ignoring thermal gradients may be reasonable over the wind acceleration region since it is probable that some form of Alfv\'en waves are required to lift the material out of the gravitational potential.
 These waves would need to have large damping lengths and undergo some dissipation within a few stellar radii of the surface in order to produce the low terminal velocities \citep{1980ApJ...242..260H}.
-These large damping lengths could result in low thermal gradients close in.
+These large damping lengths could result in shallow thermal gradients close in.
 If we ignore thermal gradients, then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may have substantial thermal gradients.
+This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may have substantial thermal gradients caused by adiabatic cooling.
 
@@
 
-To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
+To investigate this matter further,  we estimate the effective radius of the radio emitting region as a function of wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
 We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at each wavelength emanates from a surface at radial optical depth $\tau _{\rm{rad}}=$1/3.
@@
 From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$.
-Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
+Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
 Finally, the wind ionization balance may not have become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from.
@@
 
-To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [referred to `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
+To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [as referred to `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
 \begin{equation}
-T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{p},
+T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{n},
 \label{eq:eq2}
 \end{equation}
-at some distance $r_{1}$ from the star, and used the temperature coefficient $p=1.65$ obtained from our new VLA data assuming a constant velocity flow (see Figure \ref{fig:fig4}).
+at some distance $r_{1}$ from the star, and used the temperature coefficient $n=1.65$ obtained from our new VLA data assuming a constant velocity flow (see Figure \ref{fig:fig4}).
 We introduce the distance $r_{1}$ as the outer limit to ionization processes; at $r > r_{1}$, the ionization fraction is only determined by recombination.
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{HII}}=n_{\rm{HII}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
+To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H \, II}}=n_{\rm{H \, II}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
 To do so, we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
@@
 A constant velocity mass outflow, i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
-For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
+For $\alpha$ Boo, $C = 1.7 \times 10^{32} $ cm$^{-1}$ assuming a wind velocity of 35 km s$^{-1}$.
 
 2.
-All ionization processes cease beyond $r_{1}$.
+All hydrogen ionization processes cease beyond $r_{1}$.
 The ionization of hydrogen in the chromosphere and wind is a two stage process: the $n = 2$ level is excited by electron collisions and Lyman-alpha scattering, followed by photoionization by the optically thin Balmer continuum.
@@
 \end{equation}
-where the power law coefficient is obtained by finding the slope of the best fit line through the recombination coefficients between 1,000 K and 16,000 K defined in \cite{1978ppim.book.....S}.
+where the power law coefficient is obtained by finding the slope of the recombination coefficients between 1,000 K and 16,000 K given in \cite{1978ppim.book.....S}.
 
@@
 \begin{equation}
-I(r) = 2.38 \times 10^{-3} \left[\left( \frac{r_{1}}{r}\right)^{-0.19} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
+I(r) = \frac{4.7\times 10^9}{r_{1}}\left[\left( \frac{r_{1}}{r}\right)^{-0.27} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
 \label{eq:eq5}
@@
 This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
+This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ beyond 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 

### 2013-05-29 aj_submission_1/ms.tex
29th May: Finally submitted to AJ

--- 2013-05-21 draft_08/draft.tex
@@
 Despite the importance of this phenomenon and decades of study, the mechanisms that drive winds from evolved spectral-type K through mid-M stars remain an enduring mystery [clearly laid out by \cite{1985ASSL..117..229H} but still unsolved, e.g., \cite{2009AIPC.1094..267C}].
-There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
-Ultraviolet (UV) and optical observations reveal an absence of significant hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.,][]{1979ApJ...229L..27L,1981ApJ...250..293A}.
+There is insufficient atomic, molecular, or dust opacity to drive a radiation-driven outflow \citep{1995ApJ...446L..79Z,2008MNRAS.387..845J} and acoustic/pulsation models cannot drive the observed mass loss rates \citep{1995ApJ...442L..61S}.
+Ultraviolet (UV) and optical observations reveal an absence of significant hot wind plasma and the winds are thus too cool to be Parker-type thermally-driven flows \cite[e.g.,][]{1979ApJ...229L..27L,1980ApJ...235..519H,1981ApJ...250..293A}.
 
@@
           	\colhead{Integrated $F_{\nu}$} 			&
-          	\colhead{\textit{Imfit} Integrated}	&
+          	\colhead{\textit{Imfit} Integrated $F_{\nu}$}	&
 			\colhead{Image rms}					&
@@
     \colhead{(mJy beam$^{-1}$)}		        	& 
+    \colhead{(mJy)}		                		& 
+	\colhead{(\rm{mJy})}                        		& 
 	\colhead{(mJy beam$^{-1}$)}         					&
-	\colhead{$F_{\nu}$ (\rm{mJy beam$^{-1}$})}                        		& 
-	\colhead{(mJy beam$^{-1}$)}         					&
-	\colhead{(mJy beam$^{-1}$)}		}
+	\colhead{(mJy)}		}
 \startdata
@@
 In each image the flux density from the unresolved target source was calculated by, 1) taking the peak pixel value from the source, 2) manually integrating the flux density around the source, and 3) fitting an elliptical Gaussian model to the source and deriving the integrated flux density using the CASA \textit{imfit} task.
-Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3}.
+Each of these values along with the image root mean square (rms) noise measured from adjacent background regions and fitting error produced by \textit{imfit} are given in Table \ref{tab:tab3} to indicate the quality of each radio map.
+Both sources are point sources at all frequencies so the peak flux value given in Table \ref{tab:tab3} will also be its total flux density value.
 For weak detections (i.e., $F_{\nu} \lesssim 5\sigma$) we avoid using the \textit{imfit} task to obtain a flux density estimate, as this may produce biased parameter estimates \citep{1999ASPC..180.....T}.
@@
 This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.
+We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$) of -1.4; its flux density reaches 80.3 mJy at 1.6 GHz.
 
@@
 
-The combination of both atmospheric models result in a predicted excess of radio flux density at high frequencies (i.e., $\nu >$ 30 GHz) but does well in reproducing the VLA flux densities below 30 GHz.
+The radio flux densities at high frequencies (i.e., $\nu >$ 30 GHz) are overestimated by the combination of both atmospheric models, although this approach does well in reproducing the VLA flux densities below 30 GHz.
 The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum flux densities confirm that this model predicts a flux excess at even higher frequencies.

### 2013-07-01 aj_submission_2/ms.tex
Jul 1st: Started corrections from referee

--- 2013-05-29 aj_submission_1/ms.tex
@@
 \tabletypesize{\scriptsize}
-\tablecaption{Properties of red giant sample.}
+\tablecaption{Stellar and Wind Parameters of $\alpha$ Boo and $\alpha$ Tau.}
 \tablehead{	\colhead{}		       				& 
@@
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $\sim$10,000  \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & ?  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Metallicities are from \cite{2003A&A...400..709D}.
-Wind properties are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
+Wind parameters are derived from the semi-empirical models of \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
 
@@
 
-In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III).
+In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
 These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known.
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Even though they are slow rotators, a magnetic field (albeit weak: $B_{\rm{max}} =0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
 Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
@@
 
-\begin{deluxetable*}{cccccccc}
+\begin{deluxetable*}{ccccccccc}
 \tabletypesize{\scriptsize}
@@
 			\colhead{Band}		            &
-			\colhead{Frequency\tablenotemark{a}}&
+			\colhead{$\nu$\tablenotemark{a}}&
+			\colhead{$\lambda$}&
 			\colhead{Peak $F_{\nu}$}					&
@@
 	\colhead{(GHz)}								&
+	\colhead{(cm)}								&
     \colhead{(mJy beam$^{-1}$)}		        	& 
@@
 \startdata
-$\alpha$ Boo  &Q  &43.28& 5.94 & 6.09 & 6.42 & 0.30 &  0.26\\
-&Ka &33.56& 4.16 & 4.32 & 4.49 & 0.08 & 0.09 \\
-&K  &22.46& 1.83 & 1.78 & 1.81 & 0.04 & 0.05 \\
-&X  &8.46 & 0.51 & 0.51 & 0.53 & 0.03 & 0.02 \\
-&C  &4.90 & 0.21 & 0.14 & 0.16 & 0.04 & 0.01 \\
-&S  &3.15 & 0.15 & 0.14 & -     & 0.03 & -     \\
-&S  &2.87 & 0.13 & 0.12 & 0.12 & 0.01 & 0.02\\
-&L  &1.63 & 0.07 & 0.07 & -     & 0.01 & -    \\
+$\alpha$ Boo  &Q  &43.28&0.7 &5.94 & 6.09 & 6.42 & 0.30 &  0.26\\
+&Ka &33.56&0.9& 4.16 & 4.32 & 4.49 & 0.08 & 0.09 \\
+&K  &22.46&1.3& 1.83 & 1.78 & 1.81 & 0.04 & 0.05 \\
+&X  &8.46&3.5 & 0.51 & 0.51 & 0.53 & 0.03 & 0.02 \\
+&C  &4.90&6.1 & 0.21 & 0.14 & 0.16 & 0.04 & 0.01 \\
+&S  &3.15&9.5 & 0.15 & 0.14 & -     & 0.03 & -     \\
+&S  &2.87&10.4 & 0.13 & 0.12 & 0.12 & 0.01 & 0.02\\
+&L  &1.63&18.4 & 0.07 & 0.07 & -     & 0.01 & -    \\
 \hline
-\rule{0pt}{3ex}  $\alpha$ Tau &Q  &43.28 & 3.67& 3.73 & 4.08 &  0.26& 0.18	\\
-&Ka &33.56 & 2.19& 1.96 & 2.13 &  0.09& 0.07 \\
-&K  &22.46 & 1.86& 1.88 & 2.07 &  0.04& 0.08 \\
-&X  &8.46  & 0.30& 0.29 & 0.28 &  0.01& 0.02 \\
-&C  &4.96  & 0.15& 0.17 & 0.18 &  0.01& 0.01 \\
-&S  &3.15  & 0.06& 0.04 & - &  0.02 & -
+\rule{0pt}{3ex}  $\alpha$ Tau &Q  &43.28 & 0.7&3.67& 3.73 & 4.08 &  0.26& 0.18	\\
+&Ka &33.56 & 0.9&2.19& 1.96 & 2.13 &  0.09& 0.07 \\
+&K  &22.46 &1.3& 1.86& 1.88 & 2.07 &  0.04& 0.08 \\
+&X  &8.46  & 3.5&0.30& 0.29 & 0.28 &  0.01& 0.02 \\
+&C  &4.96  & 6.0&0.15& 0.17 & 0.18 &  0.01& 0.01 \\
+&S  &3.15  & 9.5&0.06& 0.04 & - &  0.02 & -
 \enddata
@@
 At the lower frequencies, it was necessary to image confusing sources, notably a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo.
-This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
-We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$) of -1.4; its flux density reaches 80.3 mJy at 1.6 GHz.
+This non-thermal source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency.
+We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$) of -1.4 between 8.5 and 1.6 GHz; its flux density reaches 80.3 mJy at 1.6 GHz.
 
-\begin{deluxetable*}{cccccc}
+\begin{deluxetable*}{ccccccc}
 \tabletypesize{\scriptsize}
@@
     \colhead{$\nu$ (GHz)}		    			& 
+		    \colhead{$\lambda$ (cm)}			&
 			\colhead{Date}						&
@@
 \startdata
-$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & 0.39 & 3.0 & \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 May 20 & 0.26 & 3.3& \cite{1986AJ.....91..602D} \\
-&4.9  & 1983 Dec 26 & $\le$0.18$(3\sigma)$&- & \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Mar 17 & 0.24  & 4.8& \cite{1986AJ.....91..602D} \\
-&15.0 & 1984 Nov 6 & 0.68 & 7.6& \cite{1986AJ.....91..602D} \\
-&22.5  & 1999 Jan 06  &1.7& 8.5& \cite{2011AA...533A.107D} \\
-&43.3  & 1999 Jan 06 & 3.3& 8.3& \cite{2011AA...533A.107D} \\
-&43.3  & 2004 Jan 25 & 3.34& 41.8& \cite{2011AA...533A.107D} \\
-&86.0  & 1985 Nov  & 21.4& 3.0& \cite{1986AA...164..227A} \\
-&108.4  & 1997 Nov - 2000 Jun & 20.1 &29.1 & \cite{2005AJ....129.2836C} \\
-&217.8 & 1997 Nov - 2000 Jun  & 83.5 &48.8 & \cite{2005AJ....129.2836C} \\
-&250.0  & 1986 Dec - 1989 Mar  & 78.0 & 9.8& \cite{1994AA...281..161A} \\
+$\alpha$ Boo (K2 III) &4.9  & 6.1&1983 Jan 21 & 0.39 & 3.0 & \cite{1986AJ.....91..602D} \\
+&4.9  &6.1& 1983 May 20 & 0.26 & 3.3& \cite{1986AJ.....91..602D} \\
+&4.9  &6.1& 1983 Dec 26 & $\le$0.18$(3\sigma)$&- & \cite{1986AJ.....91..602D} \\
+&4.9  &6.1& 1984 Mar 17 & 0.24  & 4.8& \cite{1986AJ.....91..602D} \\
+&15.0 &2.0& 1984 Nov 6 & 0.68 & 7.6& \cite{1986AJ.....91..602D} \\
+&22.5  &1.3& 1999 Jan 06  &1.7& 8.5& \cite{2011AA...533A.107D} \\
+&43.3  &0.69& 1999 Jan 06 & 3.3& 8.3& \cite{2011AA...533A.107D} \\
+&43.3  &0.69& 2004 Jan 25 & 3.34& 41.8& \cite{2011AA...533A.107D} \\
+&86.0  &0.35& 1985 Nov  & 21.4& 3.0& \cite{1986AA...164..227A} \\
+&108.4  &0.28& 1997 Nov - 2000 Jun & 20.1 &29.1 & \cite{2005AJ....129.2836C} \\
+&217.8 &0.14& 1997 Nov - 2000 Jun  & 83.5 &48.8 & \cite{2005AJ....129.2836C} \\
+&250.0  &0.12& 1986 Dec - 1989 Mar  & 78.0 & 9.8& \cite{1994AA...281..161A} \\
 \hline
-\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le$0.27$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&4.9  & 1984 Nov 6 & $\le$0.22$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
-&5.0  & 1997 Sep 27 & $\le$0.07$(3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
-&8.5  & 1997 Sep 27 & 0.28 	&9.3	& \cite{2007ApJ...655..946W} \\
-&14.9 & 1997 Sep 27 & 0.95 	&11.9	& \cite{2007ApJ...655..946W} \\
-&15.0 & 1984 Nov 6 & 0.60 	&6.0	& \cite{1986AJ.....91..602D} \\
-&108.4  & 1997 Nov - 2000 Dec &  14.0  & 9.6& \cite{2005AJ....129.2836C} \\
-&217.8 & 1999 Sep - 2000 Dec  & 25.8 & 4.6& \cite{2005AJ....129.2836C} \\
-&250.0  & 1986 Dec - 1987 Jan & 51.0 & 8.5& \cite{1994AA...281..161A} 
+\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9&6.1& 1983 Jan 21 & $\le$0.27$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&4.9&6.1  & 1984 Nov 6 & $\le$0.22$(3\sigma)$&-& \cite{1986AJ.....91..602D} \\
+&5.0  & 6.0&1997 Sep 27 & $\le$0.07$(3\sigma)$	&-& \cite{2007ApJ...655..946W} \\
+&8.5  &3.5& 1997 Sep 27 & 0.28 	&9.3	& \cite{2007ApJ...655..946W} \\
+&14.9 &2.0& 1997 Sep 27 & 0.95 	&11.9	& \cite{2007ApJ...655..946W} \\
+&15.0 &2.0& 1984 Nov 6 & 0.60 	&6.0	& \cite{1986AJ.....91..602D} \\
+&108.4 &0.28 & 1997 Nov - 2000 Dec &  14.0  & 9.6& \cite{2005AJ....129.2836C} \\
+&217.8 &0.14& 1999 Sep - 2000 Dec  & 25.8 & 4.6& \cite{2005AJ....129.2836C} \\
+&250.0 &0.12 & 1986 Dec - 1987 Jan & 51.0 & 8.5& \cite{1994AA...281..161A} 
 \enddata
@@
 \centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig0.ps}
+\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.62, angle=90]{fig0.ps}
 \\
@@
 \centering
-\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
+\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.62, angle=90]{fig1.ps}
 \\
@@
 
-Figure \ref{fig:fig1} shows the resulting predicted radio spectrum between 1 GHz and 1 THz for $\alpha$ Boo from these chromosphere and wind models.
+Figure \ref{fig:fig1} shows the resulting predicted radio spectrum between 1 GHz and 1 THz for $\alpha$ Boo from these chromosphere and wind models (green line).
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim \nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
@@
 This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm.
-$\alpha$ Tau was found to have a larger spectral index and a power law with $S_{\nu} \propto \nu ^{1.58 \pm 0.25}$ best fitted the three longest wavelength data points.
+$\alpha$ Tau was found to have a larger spectral index and a power law with $F_{\nu} \propto \nu ^{1.58 \pm 0.25}$ best fitted the three longest wavelength data points.
 This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data given in \cite{2007ApJ...655..946W}.
@@
 Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that may describe their outflow.
-The combinations of the electron temperature and density coefficients are shown for each star in Figure \ref{fig:fig4} along with the coefficients obtained by assuming either an isothermal flow or a constant velocity flow.
+The combinations of the electron temperature and density coefficients are shown for each star in Figure \ref{fig:fig4} ($\alpha$ Boo is represented by the solid line and $\alpha$ Tau by the dash-dotted line) along with the coefficients obtained by assuming either an isothermal flow (n=0) or a constant velocity flow (p=2).
 One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.

### 2013-07-02 aj_submission_2/ms.tex
July 2nd: More corrections made from referee

@@
 There is however a notable difference in flux density values at 0.7 cm  where \cite{2011AA...533A.107D} report values that are lower than ours by over 40\%.
-Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
+Although we do not rule out such a level of chromospheric variability, it would be unexpected from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
 Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may lead to larger phase errors and thus lower final flux density values.
@@
 Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg II k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
-Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$.
+The line was modeled by solving the radiative transfer equation in a spherically co-moving frame and the effects of partial redistribution were taken into account.
+A two-level atom was used to represent the upper and lower level of the resonance line.
+Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
 They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is 50\% ionized.
@@
 The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
-Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm.
+\cite{1985pssl.proc..351D} predicts that their atmospheric model would produce a flux density value of 0.4 mJy at 6 cm and encouragingly, our computed radio spectrum reproduces this value also.
 Departures from spherical symmetry are to be expected in magnetic stellar atmospheres.
@@
 
-In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromospheric model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
-The McMurry model, which contains  the photospheric model of \cite{1973ApJ...180...81J}, is based on high S/N Hubble UV spectra and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
-Beyond 1.2 $R_{\star}$ we use Robinson's wind characteristics to describe the outflow velocity where the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
+In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromosphere and transition region model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
+The McMurry model was created by using the radiative transfer code MULTI \citep{carlsson_1986} to reproduce the fluxes of collisionally excited lines in a plane-parallel, hydrostatic, one-component atmosphere.
+It contains the photospheric model of \cite{1973ApJ...180...81J} and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
+As it does not contain a wind outflow, we use Robinson's wind characteristics beyond 1.2 $R_{\star}$ to describe the outflow velocity.
+In this wind model, the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
+The Robinson wind characteristics are based on matching the Fe II 2755 $\rm{\AA}$ line and three O I lines with a simple wind model using the SEI computer code.
 We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.

### 2013-07-03 aj_submission_2/ms.tex
Jul 3rd: Sent referee's comments to GMH for review

@@
 The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
+The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect physical understanding of the wind driving mechanism and instead may be due to the large uncertainties in the free parameters in these models, such as mass loss rates and magnetic field strengths.
 
@@
 
-Equation \ref{eq:eq1} can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that may describe their outflow.
-The combinations of the electron temperature and density coefficients are shown for each star in Figure \ref{fig:fig4} ($\alpha$ Boo is represented by the solid line and $\alpha$ Tau by the dash-dotted line) along with the coefficients obtained by assuming either an isothermal flow (n=0) or a constant velocity flow (p=2).
+Equation 1 can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that may describe their outflow.
+The combinations of the electron temperature and density coefficients are shown for each star in Figure 5 ($\alpha$ Boo is represented by the solid line and $\alpha$ Tau by the dash-dotted line) along with the coefficients obtained by assuming either an isothermal flow ($n=0$) or a constant velocity flow ($p=2$).
 One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.
-Ignoring thermal gradients may be reasonable over the wind acceleration region since it is probable that some form of Alfv\'en waves are required to lift the material out of the gravitational potential.
-These waves would need to have large damping lengths and undergo some dissipation within a few stellar radii of the surface in order to produce the low terminal velocities \citep{1980ApJ...242..260H}.
-These large damping lengths could result in shallow thermal gradients close in.
-If we ignore thermal gradients, then the density coefficients are $p=$2.71 and 5.5 for $\alpha$ Boo  and $\alpha$ Tau, respectively.
-This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate from the chromosphere or wind acceleration zone, but at long VLA wavelengths (i.e., between 6 and 20 cm) we may indeed be sampling the wind very close to or at its terminal velocity and the wind may have substantial thermal gradients caused by adiabatic cooling.
+If we ignore thermal gradients completely, then the density coefficients are $p  =2.7$ and 5.5 for $\alpha$ Boo and $\alpha$ Tau, respectively.
+From mass conservation arguments the power law coefficients for the velocity profiles of each star can be found, ie., $v \propto r^{p-2}$.
+For $\alpha$ Boo we find $v \propto r^{0.7}$ while for $\alpha$ Tau we find $v \propto r^{3.5}$.
+This suggests that our long VLA wavelengths probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, probe a region where its wind is close to its terminal velocity.
 
@@
 \end{figure}
+
+The assumption of ignoring thermal gradients in a stellar outflow is probably not a valid one  however.
+It is probable that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
+These waves need damping lengths $< 1 \ R_{\star}$ in order to produce the observed wind terminal velocities, and such waves are expected to produce substantial heating deposition near the base of the wind \citep{1989A&A...209..327J,2006MNRAS.368.1145F,2006ApJ...639..416V}.
+If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile may not be described by $v \propto r^{3.5}$.
+Further out in the wind, where it has reached its terminal velocity, one would also expect a thermal gradient (but now of opposite sign) due to adiabatic expansion and line cooling.
+If the long wavelength radio emission emanates from this region of the wind then Equation \ref{eq:eq1} provides us with a direct estimate of the temperature coefficient as we can assume the density coefficient is $p=2$.
+This may be the case for our long VLA wavelength measurements of $\alpha$ Boo.
 
@@
 From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$.
-Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
+Pure adiabatic expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
 Finally, the wind ionization balance may not have become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from.

### 2013-07-05 aj_submission_2/ms.tex
Second set of referee's corrections sent to GMH

@@
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & ?  \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $\sim$10,000  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a magnetic field (albeit weak: $B_{\rm{max}} =0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
 Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
@@
 There is however a notable difference in flux density values at 0.7 cm  where \cite{2011AA...533A.107D} report values that are lower than ours by over 40\%.
-Although we do not rule out such a level of chromospheric variability, it would be unexpected from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
+Although we do not rule out such a level of chromospheric radio variability, it is not expected based on the small level of UV variability observed from such supposedly inactive stars \citep{2013MNRAS.428.2064H}.
 Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may lead to larger phase errors and thus lower final flux density values.
@@
 Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg II k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
-The line was modeled by solving the radiative transfer equation in a spherically co-moving frame and the effects of partial redistribution were taken into account.
-A two-level atom was used to represent the upper and lower level of the resonance line.
+The line was modeled by solving the radiative transfer equation in a spherical co-moving frame and the effects of partial redistribution \citep[e.g.,][]{1981BAICz..32..271H} were taken into account.
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
@@
 In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromosphere and transition region model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
-The McMurry model was created by using the radiative transfer code MULTI \citep{carlsson_1986} to reproduce the fluxes of collisionally excited lines in a plane-parallel, hydrostatic, one-component atmosphere.
+The semi-empirical McMurry model was created by using the radiative transfer code MULTI \citep{carlsson_1986} to reproduce the fluxes of collisionally excited C I, C II, Si III, Mg II, and C IV lines in a plane-parallel, hydrostatic, one-component atmosphere.
 It contains the photospheric model of \cite{1973ApJ...180...81J} and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
@@
 In this wind model, the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
-The Robinson wind characteristics are based on matching the Fe II 2755 $\rm{\AA}$ line and three O I lines with a simple wind model using the SEI computer code.
+The Robinson wind characteristics are based on matching the Fe II 2755 $\rm{\AA}$ line and the O I triplet near 1304 $\rm{\AA}$ with a simplified wind model using the SEI computer code \citep{1987ApJ...314..726L}.
 We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.
@@
 The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
-The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect physical understanding of the wind driving mechanism and instead may be due to the large uncertainties in the free parameters in these models, such as mass loss rates and magnetic field strengths.
+The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect  wind driving mechanism and instead may be due to the large uncertainties in the free parameters in these models, such as mass loss rates, magnetic field strengths, and damping lengths.
+For example, the mass loss rate is very sensitive to the surface magnetic field strength (i.e., $\dot{M} \propto B^4$) in these Alfv\'en wave models \citep{1983ApJ...275..808H} so a small uncertainty in one parameter can lead to a large uncertainty in the other.
 
@@
 \subsection{Radio Spectral Indices} \label{disc:disc3}
-Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers.
+Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission emanates from nearly static lower atmospheric layers.
 The radio flux density-frequency relationship for these stars is usually found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$).
@@
 \caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices.
-The spectral index for $\alpha$ Boo and $\alpha$ Tau are found to be 1.05 and 1.58, respectively, which are both larger than the 0.6 value expected for a constant property wind model.}
+The spectral indices for $\alpha$ Boo and $\alpha$ Tau are found to be 1.05 and 1.58, respectively, which are both larger than the 0.6 value expected for a constant property wind model.}
 \label{fig:fig3}
@@
 
-The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
+The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the power laws that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic.
 For $\alpha$ Boo a power law with $F_{\nu} \propto \nu ^{1.05 \pm 0.05}$ fits the four longest wavelength data points well.
@@
 
-Equation 1 can be used in conjunction with our new spectral index for each star to calculate possible density and temperature coefficients that may describe their outflow.
+Equation 1 can be used in conjunction with our new spectral index for each star to calculate the density and temperature coefficients that may describe their outflows.
 The combinations of the electron temperature and density coefficients are shown for each star in Figure 5 ($\alpha$ Boo is represented by the solid line and $\alpha$ Tau by the dash-dotted line) along with the coefficients obtained by assuming either an isothermal flow ($n=0$) or a constant velocity flow ($p=2$).
-One explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.
+One potential explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.
 If we ignore thermal gradients completely, then the density coefficients are $p  =2.7$ and 5.5 for $\alpha$ Boo and $\alpha$ Tau, respectively.
-From mass conservation arguments the power law coefficients for the velocity profiles of each star can be found, ie., $v \propto r^{p-2}$.
+From mass conservation arguments assuming a steady flow, the power law coefficients for the velocity profiles of each star can be found, ie., $v \propto r^{p-2}$.
 For $\alpha$ Boo we find $v \propto r^{0.7}$ while for $\alpha$ Tau we find $v \propto r^{3.5}$.
-This suggests that our long VLA wavelengths probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, probe a region where its wind is close to its terminal velocity.
+This suggests that our long VLA wavelengths may probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, may probe a region where its wind is close to its terminal velocity.
 
@@
 \caption{Predicted effective radius (dashed lines) as a function of wavelength derived from the existing atmospheric models of $\alpha$ Boo and $\alpha$ Tau.
-Also plotted is the predicted effective radius derived from our analytical advection model for $\alpha$ Boo (discussed in \ref{disc:disc4}).
+Also plotted is the predicted effective radius derived from our analytical advection model for $\alpha$ Boo (discussed in Section \ref{disc:disc4}).
 Points corresponding to our long wavelength VLA measurements are also shown.
-At the same radio wavelengths the less ionized and less opaque mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
+At the same radio wavelengths the lower mass loss rate of $\alpha$ Tau results in a smaller effective radius than that for $\alpha$ Boo.}
 \label{fig:fig5}
@@
 
-The assumption of ignoring thermal gradients in a stellar outflow is probably not a valid one  however.
-It is probable that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
-These waves need damping lengths $< 1 \ R_{\star}$ in order to produce the observed wind terminal velocities, and such waves are expected to produce substantial heating deposition near the base of the wind \citep{1989A&A...209..327J,2006MNRAS.368.1145F,2006ApJ...639..416V}.
-If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile may not be described by $v \propto r^{3.5}$.
+The assumption of completely ignoring thermal gradients in a stellar outflow is probably unreliable however.
+It is likely that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
+These waves need damping lengths which are much larger than the density scale height in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1989A&A...209..327J}.
+It has also been shown that these waves are expected to produce substantial heating deposition near the base of the wind \citep{1982ApJ...261..279H,2006MNRAS.368.1145F}.
+If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile will not be described by $v \propto r^{3.5}$.
+Furthermore, diverging flow geometries have often been invoked as a more realistic representation of stellar atmospheres \citep{1982ApJ...257..264H} and so one could write the continuity equation for a steady flow as
+\begin{equation}
+\dot{M} _{\star} = f(r)4\pi r^2 \rho (r) v(r)^2,
+\end{equation}
+where $f$ is a function describing the divergence from a purely radial flow, $\dot{M} _{\star}$ is the stellar mass loss rate, and $\rho$ is the mass density.
+If the flow expansion area can then be written as  a function of radial distance as $f \propto r^s$, where $s$ is some expansion coefficient, then $v \propto r^{3.5-s}$ would describe the velocity profile of $\alpha$ Tau (ignoring thermal gradients and assuming a constant ionization fraction).
 Further out in the wind, where it has reached its terminal velocity, one would also expect a thermal gradient (but now of opposite sign) due to adiabatic expansion and line cooling.
 If the long wavelength radio emission emanates from this region of the wind then Equation \ref{eq:eq1} provides us with a direct estimate of the temperature coefficient as we can assume the density coefficient is $p=2$.
-This may be the case for our long VLA wavelength measurements of $\alpha$ Boo.
+This may be the case for our long VLA wavelength measurements of $\alpha$ Boo in which case $T_{e} \propto r^{-1.65}$.
 
@@
 Since the radio free-free opacity increases at longer wavelengths the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths.
-This implies that the effective radius (i.e., the radius where $\tau _{\lambda} = \tau _{\rm{rad}}$) will increase with longer wavelengths and will be greater for outflows with higher densities of ionized material as $\tau _{\lambda} \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.
+This implies that the effective radius (i.e., the radius where $\tau _{\lambda} = \tau _{\rm{rad}}$) will increase with longer wavelengths and will be greater for outflows with higher densities of ionized material as $\tau _{\lambda}(r) \propto \lambda ^{2.1} \int n_{\rm{ion}}(r)n_{\rm{e}}(r) dr$.
 
-The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau means that the latter has a substantially smaller effective radius at longer wavelengths, as seen in Figure \ref{fig:fig5}.
+The larger mass loss rate of $\alpha$ Boo in comparison to $\alpha$ Tau means that the latter has a substantially smaller effective radius at longer wavelengths, as seen in Figure \ref{fig:fig5}.
 At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.2 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau.
@@
 For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest-wavelength measurements are of the region where the wind has reached a steady terminal velocity.
-From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$.
+From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient is $p=2$ and thus the $T_{\rm{e}}$ coefficient is $n=1.65$.
 Pure adiabatic expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
@@
 A failure of the Drake model for $\alpha$ Boo is that it overestimates the radio fluxes at long VLA wavelengths which sample the outer atmosphere, as clearly shown in Figure \ref{fig:fig1}.
-If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
+If these wavelengths are indeed sampling the wind at its terminal velocity then one reason for this overestimation is that the wind is cooling closer in than predicted by the existing model, which assumes a constant temperature of 8,000 K out to $\sim$20 $R_{\star}$.
 The main mechanism for such cooling would be adiabatic expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates.
 
-To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [as referred to `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
+To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [referred to as `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
 \begin{equation}
@@
 We introduce the distance $r_{1}$ as the outer limit to ionization processes; at $r > r_{1}$, the ionization fraction is only determined by recombination.
-To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H \, II}}=n_{\rm{H \, II}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
+To calculate the new electron density in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H \, II}}=n_{\rm{H \, II}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
 To do so, we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
@@
 3.
-Only radiative recombination of H is considered and the temperature variation of the recombination coefficient $\alpha _{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S} is included.
+Only radiative recombination of hydrogen is considered and the temperature variation of the recombination coefficient $\alpha _{B}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S} is included.
 The recombination coefficient varies with temperature as
 \begin{equation}
-\alpha _{B} = \alpha _{B}(r_{1})\left[\frac{T_{e}(r_1)}{T_{e}(r)}\right]^{0.77},
+\alpha _{B}(r) = \alpha _{B}(r_{1})\left[\frac{T_{e}(r_1)}{T_{e}(r)}\right]^{0.77},
 \label{eq:eq3}
@@
 We wish to thank the NRAO helpdesk for their detailed responses to our CASA related queries.
+We thank the referee for their careful reading of the manuscript and their valuable comments.
 This publication has emanated from research conducted with the financial support of Science Foundation Ireland under Grant Number SFI11/RFP.1/AST/3064, and a grant from Trinity College Dublin.

### 2013-07-09 aj_submission_2/ms.tex
Jul 9th: Sent cover letter to Co-authors

@@
 
-Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their chromospheres and wind acceleration zones where most of the energy that drives their mass loss is deposited.
+Multi-wavelength centimeter continuum observations of non-dusty, non-pulsating K spectral-type red giants directly sample their chromospheres and wind acceleration zones.
 Such stars are feeble emitters at these wavelengths however, and previous observations have provided only a small number of modest signal-to-noise measurements slowly accumulated over three decades.
@@
 Jansky Very Large Array (VLA) thermal continuum observations of the wind acceleration zones of two dust-free red giants, Arcturus ($\alpha$ Boo: K2 III) and Aldebaran ($\alpha$ Tau: K5 III).
-Importantly, most of our observations of each star were carried out over just a few days, so that we obtained an essentially consistent snapshot of the different stellar atmospheric layers sampled at different wavelengths, independent of any long-term variability.
+Importantly, most of our observations of each star were carried out over just a few days, so that we obtained a snapshot of the different stellar atmospheric layers sampled at different wavelengths, independent of any long-term variability.
 We report the first detections at several wavelengths for each star including a detection at 10 cm (3.0 GHz: S-band) for both stars and a 20 cm (1.5 GHz: L-band) detection for $\alpha$ Boo.
@@
 Spectral indices are used to discuss the possible properties of the stellar atmospheres and we find evidence for a rapidly cooling wind in the case of $\alpha$ Boo.
-Finally, we develop a simple analytical wind model for $\alpha$ Boo based on our new long wavelength flux density values.
+Finally, we develop a simple analytical wind model for $\alpha$ Boo based on our new long wavelength flux measurements.
 
@@
 Magnetic fields are most likely involved in the mass loss process, although current magnetic models are also unable to explain spectral diagnostics.
-Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} UV spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable.
+Exquisite high signal-to-noise (S/N) ratio \textit{Hubble} UV spectra have revealed that the 1-D linear Alfv\'en wave-driven wind models of the 1980’s (e.g., \citealt{1980ApJ...242..260H,1988PhDT........13H}) are untenable \citep{harper_2001}.
 These models predict chromospheres as integral parts of a turbulent, extended and heated wind acceleration zone, but the theoretical line profiles and electron densities do not agree with the \textit{Hubble} spectra, \cite[e.g.,][]{1998ApJ...494..828J}.
-One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta as shown by the increase of wind scattering absorption with optical depth in Fe II lines \citep{1999ApJ...521..382C}.
+One important property of cool evolved star winds gleaned from UV spectra is that, for the most part, the red giant winds accelerate in a quasi-steady manner and are not the result of ballistic ejecta as shown by the increase of wind scattering absorption velocity with optical depth in Fe\,\textsc{ii} lines \citep{1999ApJ...521..382C}.
 A new generation of theoretical models with outflows driven within diverging magnetic flux tubes have now emerged \citep{2006MNRAS.368.1145F, 2007ApJ...659.1592S} but these too are not yet in agreement with observations \citep{2009AIPC.1094..267C}.
@@
 Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
-Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $\sim$10,000  \\
+Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $\lesssim$10,000  \\
 Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
@@
 Metallicities are from \cite{2003A&A...400..709D}.
-Wind parameters are derived from the semi-empirical models of \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}
+Wind parameters are derived from the semi-empirical models of \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.
+The Ca\,\textsc{ii} ionization studies of \cite{2004IAUS..219..651H} indicate a wind temperature of $T_{e}\lesssim 1\times 10^4$ K for $\alpha$ Tau.}
 
@@
 
-Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from eclipsing binaries such as the $\zeta$ Aurigae and symbiotic systems (e.g., \citealt{1970VA.....12..147W}; \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
+Currently the most detailed spatial information about the atmospheres of K and early M evolved stars is obtained from the $\zeta$ Aurigae and symbiotic eclipsing binaries (e.g., \citealt{1970VA.....12..147W}; \citealt{1996ApJ...466..979B}; \citealt{2008AJ....136.1964E}; \citealt{2008ApJ...675..711C}).
 Even though these systems offer us the best opportunity to obtain information on the dynamics and thermodynamics at various heights in the evolved star's atmosphere, the very nature of the binary system may introduce further complexities.
 For example, the orbital separation is often within the wind acceleration region and one could expect flow perturbations to be present (e.g., \citealt{1981ApJ...248.1043C}).
-In fact, using the `old' VLA, \cite{2005AJ....129.1018H} confirm that the velocity structure of  of $\zeta$ Aurigae is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
+Using the `old' VLA, \cite{2005AJ....129.1018H} find a slow wind acceleration for $\zeta$ Aurigae and confirm that its velocity structure is not typical of single stars with similar spectral types, such as $\lambda$ Velorum \citep{1999ApJ...521..382C}.
 
@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
-Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere.
+Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a possible magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} indicates magnetic activity in its atmosphere.
 These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$.
@@
 There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
-However, the position uncertainties, due to noise and to the atmospheric differences between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
+However, the position uncertainties due to noise and phase uncertainties between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
 
@@
 \subsection{Existing Atmospheric Models} \label{disc2}
-One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Ca II H and K and Mg II h and k resonance lines.
-Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg II k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
-The line was modeled by solving the radiative transfer equation in a spherical co-moving frame and the effects of partial redistribution \citep[e.g.,][]{1981BAICz..32..271H} were taken into account.
+One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Ca\,\textsc{ii} H and K and Mg\,\textsc{ii} h and k resonance lines.
+Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg\,\textsc{ii} k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
+The line was modeled by solving the radiative transfer equation in a spherical co-moving frame and the effects of partial redistribution \citep[e.g.,][]{1983ApJ...273..299D} were taken into account.
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
 They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is 50\% ionized.
-We compute the expected radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included.
-The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
-\cite{1985pssl.proc..351D} predicts that their atmospheric model would produce a flux density value of 0.4 mJy at 6 cm and encouragingly, our computed radio spectrum reproduces this value also.
+We compute the radio spectrum from these models assuming spherical 1-D geometry \citep{1994MNRAS.268..894H} with the free-free Gaunt factors from \cite{1988ApJ...327..477H}.
+The radiative transfer equation is solved using the Feautrier technique \citep{1978stat.book.....M} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers.
+\cite{1985pssl.proc..351D} predicts that their atmospheric model would produce a flux density value of 0.4 mJy at 6 cm and encouragingly, our radio spectrum reproduces this value.
 Departures from spherical symmetry are to be expected in magnetic stellar atmospheres.
-For example, $\alpha$ Boo is now known to have an inclination axis of 58$^{\circ} \pm$25$^{\circ}$ \citep{2006PASP..118.1112G} and a global magnetic dipole could cause density variations between the equator and the polar regions.
+For example, $\alpha$ Boo is has an inclination axis of 58$^{\circ} \pm$25$^{\circ}$ \citep{2006PASP..118.1112G} and a global magnetic dipole could cause density variations between the equator and the polar regions.
 Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.
@@
 At high frequencies the radio spectra produced by these models have a blackbody-like slope (i.e., $\sim \nu ^{2}$) as a result of the small ion density scale heights close to the star where the temperature is changing slowly.
-At low frequencies however, where the Drake models predict the wind to have constant velocity, ionization fraction and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
+At low frequencies however, where the Drake models predict the wind to have constant velocity, ionization fraction, and temperature, the slopes approaches the well known $\sim\nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
 The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo.
@@
 In Figure \ref{fig:fig2} we plot the expected radio spectrum of $\alpha$ Tau based on the semi-empirical 1-D chromosphere and transition region model of \cite{1999MNRAS.302...37M} embedded in the 1-D wind model of \cite{1998ApJ...503..396R}.
-The semi-empirical McMurry model was created by using the radiative transfer code MULTI \citep{carlsson_1986} to reproduce the fluxes of collisionally excited C I, C II, Si III, Mg II, and C IV lines in a plane-parallel, hydrostatic, one-component atmosphere.
+The semi-empirical McMurry model was created by using the radiative transfer code MULTI \citep{carlsson_1986} to reproduce the fluxes of collisionally excited C\,\textsc{i}, C\,\textsc{ii}, Si\,\textsc{iii}, Mg\,\textsc{ii}, and C\,\textsc{iv} lines in a plane-parallel, hydrostatic, one-component atmosphere.
 It contains the photospheric model of \cite{1973ApJ...180...81J} and reaches a maximum temperature of 10$^{5}$ K at 1.2 $R_{\star}$.
-As it does not contain a wind outflow, we use Robinson's wind characteristics beyond 1.2 $R_{\star}$ to describe the outflow velocity.
+As it does not contain a wind outflow, we use Robinson et al.'s wind characteristics beyond 1.2 $R_{\star}$ to describe the outflow velocity.
 In this wind model, the wind reaches $\sim$80\% of its terminal value of 30 km s$^{-1}$ by 3 $R_{\star}$.
-The Robinson wind characteristics are based on matching the Fe II 2755 $\rm{\AA}$ line and the O I triplet near 1304 $\rm{\AA}$ with a simplified wind model using the SEI computer code \citep{1987ApJ...314..726L}.
+The Robinson et al.
+wind characteristics are based on matching the Fe\,\textsc{ii} 2755 $\rm{\AA}$ line and the O\,\textsc{i} triplet near 1304 $\rm{\AA}$ with a simplified wind model using the SEI computer code \citep{1987ApJ...314..726L}.
 We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.
@@
 One possible explanation for this is that the inner atmosphere contains extensive amounts of cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
-This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
+This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large ($> 99 \%$) filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
 The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at nearly all VLA wavelengths, and only contributes a very small flux density at the longest wavelengths.
@@
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
-The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect  wind driving mechanism and instead may be due to the large uncertainties in the free parameters in these models, such as mass loss rates, magnetic field strengths, and damping lengths.
-For example, the mass loss rate is very sensitive to the surface magnetic field strength (i.e., $\dot{M} \propto B^4$) in these Alfv\'en wave models \citep{1983ApJ...275..808H} so a small uncertainty in one parameter can lead to a large uncertainty in the other.
+The linear Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
+The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect  wind driving mechanism and instead may be due to the simplifications and  uncertainties in these models, such as wind densities, magnetic field strengths, and damping lengths.
+For example, the mass loss rate is very sensitive to the radial surface magnetic field strength (i.e., $\dot{M} \propto B^4$) in these Alfv\'en wave models \citep{1983ApJ...275..808H} so a small uncertainty in the mass loss rate can lead to a large uncertainty in the magnetic field strength.
+Relaxing some of these simplifications such as purely radial flows or non-assumption of the WKB approximation \citep{1995ApJ...454..901C} may also also lead to better agreement with our radio data.
 
@@
 a so-called MOLsphere) which extends out to $\sim$2.5 $R_{\star}$, has a temperature of $1500 \ \pm 200$ K, and a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$.
-They were unable to constrain the geometrical thickness, $\Delta L$, of the MOLsphere from the data however, and arbitrarily fixed it to 0.1 $R_{\star}$.
+They were unable to constrain the geometrical thickness $\Delta L$, of the MOLsphere from the data however, and arbitrarily set it to 0.1 $R_{\star}$.
 It can be shown that such a MOLsphere would have an optical depth of $\tau _{\rm{6\,cm}} = 4.6$ at C-band and would produce a corresponding flux density of  0.06 mJy which is considerably lower than our high S/N measurement of 0.15 mJy.
@@
 We have also assumed the CO filling factor to be unity.
-It can also be shown that the MOLsphere becomes optically thin at C-band (i.e.
-$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$.
-In the next section we argue that the radio emission from $\alpha$ Tau even at long VLA wavelengths comes from a region much closer in to the star which suggests that the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
+The disagreement in values between our radio data and the predicted flux for an optically thick disk could mean that the MOLsphere is optically thin at long VLA wavelengths.
+It can be shown that the MOLsphere becomes optically thin at C-band (i.e.
+$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$, so if the long VLA wavelength radio emission from $\alpha$ Tau comes from a region much closer in to the star then the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
 
@@
 It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then
+If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e}(r) \propto r^{-p}$ and $T_{e}(r) \propto r^{-n}$ respectively, then
 
@@
 If we ignore thermal gradients completely, then the density coefficients are $p  =2.7$ and 5.5 for $\alpha$ Boo and $\alpha$ Tau, respectively.
-From mass conservation arguments assuming a steady flow, the power law coefficients for the velocity profiles of each star can be found, ie., $v \propto r^{p-2}$.
-For $\alpha$ Boo we find $v \propto r^{0.7}$ while for $\alpha$ Tau we find $v \propto r^{3.5}$.
+From mass conservation arguments assuming a steady flow, the power law coefficients for the velocity profiles of each star can be found, ie., $v(r) \propto r^{p-2}$.
+For $\alpha$ Boo we find $v(r) \propto r^{0.7}$ while for $\alpha$ Tau we find $v(r) \propto r^{3.5}$.
 This suggests that our long VLA wavelengths may probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, may probe a region where its wind is close to its terminal velocity.
@@
 It is likely that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
-These waves need damping lengths which are much larger than the density scale height in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1989A&A...209..327J}.
-It has also been shown that these waves are expected to produce substantial heating deposition near the base of the wind \citep{1982ApJ...261..279H,2006MNRAS.368.1145F}.
-If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile will not be described by $v \propto r^{3.5}$.
-Furthermore, diverging flow geometries have often been invoked as a more realistic representation of stellar atmospheres \citep{1982ApJ...257..264H} and so one could write the continuity equation for a steady flow as
+These waves need damping lengths which are much larger than the density scale height $H$ (where $H \sim 0.005 R_{\star}$ for our targets), in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1983ApJ...275..808H}.
+It has also been shown that these waves are expected to produce substantial heating deposition near the base of the wind \citep{1982ApJ...261..279H}.
+If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile will not be described by $v(r) \propto r^{3.5}$.
+Furthermore, diverging flow geometries have been invoked as a more realistic representation of stellar atmospheres \citep{1982ApJ...257..264H,1989A&A...209..327J,2006SSRv..122..181V} and so one could write the continuity equation for a steady flow as
 \begin{equation}
-\dot{M} _{\star} = f(r)4\pi r^2 \rho (r) v(r)^2,
+\dot{M} _{\star} = f(r)4\pi r^2 \rho (r) v(r),
 \end{equation}
-where $f$ is a function describing the divergence from a purely radial flow, $\dot{M} _{\star}$ is the stellar mass loss rate, and $\rho$ is the mass density.
-If the flow expansion area can then be written as  a function of radial distance as $f \propto r^s$, where $s$ is some expansion coefficient, then $v \propto r^{3.5-s}$ would describe the velocity profile of $\alpha$ Tau (ignoring thermal gradients and assuming a constant ionization fraction).
+where $f(r)$ is a function describing the divergence from a purely radial flow [i.e., $f(r)=1$], $\dot{M} _{\star}$ is the stellar mass loss rate, and $\rho(r)$ is the gas density at $r$.
+If the non-radial expansion term can be described by a power-law $f(r) \propto r^s$, where $s>1$ indicates super-radial expansion, then $v(r) \propto r^{3.5-s}$ would describe the velocity profile of $\alpha$ Tau (ignoring thermal gradients and assuming a constant ionization fraction).
 Further out in the wind, where it has reached its terminal velocity, one would also expect a thermal gradient (but now of opposite sign) due to adiabatic expansion and line cooling.
 If the long wavelength radio emission emanates from this region of the wind then Equation \ref{eq:eq1} provides us with a direct estimate of the temperature coefficient as we can assume the density coefficient is $p=2$.
-This may be the case for our long VLA wavelength measurements of $\alpha$ Boo in which case $T_{e} \propto r^{-1.65}$.
+This may be the case for our long VLA wavelength measurements of $\alpha$ Boo in which case $T_{e}(r) \propto r^{-1.65}$.
 
-To investigate this matter further,  we estimate the effective radius of the radio emitting region as a function of wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau.
-We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at each wavelength emanates from a surface at radial optical depth $\tau _{\rm{rad}}=$1/3.
+To investigate this matter further,  we estimate the effective radius of the radio emitting region as a function of wavelength based on the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson et al.
+model for $\alpha$ Tau.
+We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at each wavelength is characterized by emission from a radial optical depth $\tau _{\rm{rad}}\sim 1/3$.
 This is a modification of the Eddington-Barbier relation for an extended atmosphere where emission from smaller optical depths has added weight.
@@
 From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient is $p=2$ and thus the $T_{\rm{e}}$ coefficient is $n=1.65$.
-Pure adiabatic expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H$^{+}$ and/or line cooling.
+Pure adiabatic expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H\,\textsc{ii} and/or line cooling.
 Finally, the wind ionization balance may not have become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from.
@@
 We introduce the distance $r_{1}$ as the outer limit to ionization processes; at $r > r_{1}$, the ionization fraction is only determined by recombination.
-To calculate the new electron density in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H \, II}}=n_{\rm{H \, II}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
+To calculate the new electron density in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_{\rm{H\,\textsc{ii}}}=n_{\rm{H\,\textsc{ii}}}/n_{\rm{H}}$, where $n_{\rm{HII}}$ and $n_{\rm{H}}$ are the ionized and total hydrogen number densities, respectively.
 To do so, we need to make a number of assumptions about the wind properties beyond radius $r_{1}$, namely:
@@
 \begin{equation}
-x_{\rm{HII}}(r)= \frac{x_{\rm{HII}}(r_1)x_{\rm{ion}}e^{-I(r)}}{x_{\rm{ion}}+x_{\rm{HII}}(r_1)[1 - e^{-I(r)}]}
+x_{\rm{H\,\textsc{ii}}}(r)= \frac{x_{\rm{H\,\textsc{ii}}}(r_1)x_{\rm{ion}}e^{-I(r)}}{x_{\rm{ion}}+x_{\rm{H\,\textsc{ii}}}(r_1)[1 - e^{-I(r)}]}
 \label{eq:eq4}
@@
 This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.
-This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ beyond 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
+This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{H\,\textsc{ii}}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{H\,\textsc{ii}}}$ beyond 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
 

### 2013-07-10 aj_submission_2/ms.tex
Jul 10th

@@
 This should give a more appropriate estimate of the mean radial electron temperature.
-It is this value that controls the atomic level populations and ionization of the mean plasma that feed into UV spectroscopic analyses.
-This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, allowing constraints on potential mass loss mechanisms to be derived.
+It is this value that controls the atomic level populations and ionization of the mean plasma which is needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, allowing constraints on potential mass loss mechanisms to be derived.
 
@@
 
-Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in both sub-bands for the 2011 data.
+Apart from $\alpha$ Boo at C-band and $\alpha$ Tau at S-band, detections were made in every sub-band for the 2011 data.
 For all other bands, the flux densities of the targets in both sub-bands were found to be the same within their uncertainties so we do not present separate values here.
@@
 There is a slight positional offset of $1\arcsec$ between the position of the peak flux density at 1.5 and at 3.0 GHz for the 2012 data, which were taken within 1 day of each other.
-However, the position uncertainties due to noise and phase uncertainties between the directions of the phase reference source and the target, are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
+However, the position uncertainties due to noise and phase uncertainties between the directions of the phase reference source and the target are at least $1\arcsec$, and so we feel that it is highly likely that both detections are of $\alpha$ Boo.
 
@@
 In Figure \ref{fig:fig2} we plot the previous  radio measurements of $\alpha$ Tau at all frequencies below 250 GHz (i.e.
-0.12 cm).
+$> 0.12$ cm).
 Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e., X and Ku) and had never been detected at wavelengths longer than 3 cm due to its relatively low mass-loss rate.
@@
 Departures from spherical symmetry are to be expected in magnetic stellar atmospheres.
-For example, $\alpha$ Boo is has an inclination axis of 58$^{\circ} \pm$25$^{\circ}$ \citep{2006PASP..118.1112G} and a global magnetic dipole could cause density variations between the equator and the polar regions.
+For example, $\alpha$ Boo has an inclination axis of 58$^{\circ} \pm$25$^{\circ}$ \citep{2006PASP..118.1112G} and a global magnetic dipole could cause density variations between the equator and the polar regions.
 Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.

### 2013-07-11 aj_submission_2/ms.tex
Jul 11th: Almost ready to send off

@@
 Around the same time, another class of late-type evolved star emerged which showed signs of possessing both a transition region and a cool wind \citep[e.g.,][]{1982A&A...107..292R}.
-Many of these so called `hybrid atmosphere' stars now also show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
+Many of these so-called `hybrid atmosphere' stars now also show evidence for coronal emission, albeit much weaker than on the blue side of the dividing line \citep{1997ApJ...491..876A,2005ApJ...622..629D}.
 Understanding the nature of the atmospheric structure of late-type evolved stars will ultimately lead to a broader understanding of the mass-loss process.
@@
 Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained.
-In the UV, the source function, $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature, $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}/\sqrt{T_{\rm{e}}}$).
+In the UV, the source function $S_{\nu}$, of electron collisionally excited emission lines is sensitive to electron temperature $T_{\rm{e}}$, (i.e., $S_{\nu} \propto e^{-h\nu /kT_{\rm{e}}}/\sqrt{T_{\rm{e}}}$).
 Therefore, a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and hence not reflect the mean radial electron temperature distribution.
@@
 
-In the cm-radio regime the radio opacity, $ \kappa _{\lambda}$, strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of a stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
+In the cm-radio regime the radio opacity $ \kappa _{\lambda}$, strongly increases with wavelength (i.e., $ \kappa _{\lambda} \propto \lambda ^{2.1}$) and so the longer wavelengths sample the extended layers of a stars atmosphere, thus	 providing us with spatial information about the star's mass outflow region.
 The NRAO\footnote{The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.} Karl G.
@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a possible magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has possibly been detected for $\alpha$ Boo \citep{2011A&A...529A.100S} along with a possible magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
 Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} indicates magnetic activity in its atmosphere.
@@
 One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Ca\,\textsc{ii} H and K and Mg\,\textsc{ii} h and k resonance lines.
-Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg\,\textsc{ii} k 2796 $\rm{\AA}$ emission line observed with the International Ultraviolet Explorer.
+Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} which is based on the Mg\,\textsc{ii} k 2796 $\rm{\AA}$ emission line observed with the IUE telescope.
 The line was modeled by solving the radiative transfer equation in a spherical co-moving frame and the effects of partial redistribution \citep[e.g.,][]{1983ApJ...273..299D} were taken into account.
 Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
-They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is 50\% ionized.
+They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is $\sim50$\% ionized.
 We compute the radio spectrum from these models assuming spherical 1-D geometry \citep{1994MNRAS.268..894H} with the free-free Gaunt factors from \cite{1988ApJ...327..477H}.
@@
 At high frequencies our VLA data indicates a flux excess which is in agreement with previous mm-observations.
+This may be due to larger chromospheric ion densities or to the possible presence of transition region plasma not accounted for in the Drake model.
 The discrepancy at low frequencies may be due to a lower ionization fraction in the wind, or a lower mass loss rate than that used in the Drake model.
@@
 wind characteristics are based on matching the Fe\,\textsc{ii} 2755 $\rm{\AA}$ line and the O\,\textsc{i} triplet near 1304 $\rm{\AA}$ with a simplified wind model using the SEI computer code \citep{1987ApJ...314..726L}.
-We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction, $x_{e}$, of 0.5 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.
+We assume the wind to have a constant temperature of 10,000 K and have a constant ionization fraction of 0.6 throughout, based on the ionization fraction at the corresponding temperature in the McMurry model.
 
@@
 The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum flux densities confirm that this model predicts a flux excess at even higher frequencies.
-One possible explanation for this is that the inner atmosphere contains extensive amounts of cooler gas than that predicted by the 1-D static chromospheric model of McMurry.
+One possible explanation for this is that the inner atmosphere contains extensive amounts of cooler gas than that predicted by the 1-D static chromosphere and transition region model of McMurry.
 This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large ($> 99 \%$) filling factors i.e., a thermally bifurcated CO-mosphere \citep{1996IAUS..176..371A}.
-The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at nearly all VLA wavelengths, and only contributes a very small flux density at the longest wavelengths.
+The wind which we have overlain on top of the McMurry chromosphere and transition region is found to be optically thin at nearly all VLA wavelengths, and only contributes a very small flux at the longest wavelengths.
 As our model matches the data reasonably well below 30 GHz we conclude that $\alpha$ Tau's wind is optically thin and the VLA radio emission at all wavelengths emanates from the inner atmosphere.
@@
 We have also assumed the CO filling factor to be unity.
-The disagreement in values between our radio data and the predicted flux for an optically thick disk could mean that the MOLsphere is optically thin at long VLA wavelengths.
+The disagreement in values between our radio data and the predicted flux for an optically thick disk could mean that the MOLsphere is optically thin at long VLA wavelengths and that the radio emission emanates from the more ionized material closer to the star.
 It can be shown that the MOLsphere becomes optically thin at C-band (i.e.
-$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$, so if the long VLA wavelength radio emission from $\alpha$ Tau comes from a region much closer in to the star then the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
+$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$, so if the long VLA wavelength radio emission from $\alpha$ Tau comes from a region closer in to the star, then the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
 
@@
 For $\alpha$ Boo we find $v(r) \propto r^{0.7}$ while for $\alpha$ Tau we find $v(r) \propto r^{3.5}$.
-This suggests that our long VLA wavelengths may probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, may probe a region where its wind is close to its terminal velocity.
+This suggests that our long VLA wavelengths may probe a steep acceleration region for $\alpha$ Tau's outflow but for $\alpha$ Boo, may probe a region where the wind is close to its terminal velocity.
 
@@
 It is likely that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
-These waves need damping lengths which are much larger than the density scale height $H$ (where $H \sim 0.005 R_{\star}$ for our targets), in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1983ApJ...275..808H}.
+These waves need damping lengths which are much larger than the density scale height $H_{\star}$ (where $H_{\star} \sim 10 \ H_{\odot}$ for our targets), in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1983ApJ...275..808H}.
 It has also been shown that these waves are expected to produce substantial heating deposition near the base of the wind \citep{1982ApJ...261..279H}.
@@
 1.
-A constant velocity mass outflow, i.e., $n_{\rm{H}}(r)=C/r^2$ where $n_{\rm{H}}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
+A constant velocity mass outflow, i.e., $n_{\rm{H}}(r)=C/r^2$ where $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity.
 For $\alpha$ Boo, $C = 1.7 \times 10^{32} $ cm$^{-1}$ assuming a wind velocity of 35 km s$^{-1}$.

### 2013-07-11 aj_submission_2/ms.tex
Jul 11th: Hopefully send this out tomoro! to AJ

@@
 Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds.
-Even though they are slow rotators, a mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26$ G) has possibly been detected for $\alpha$ Boo \citep{2011A&A...529A.100S} along with a possible magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
+Even though they are slow rotators, three possible values for the mean longitudinal magnetic field (albeit weak: $B = 0.65 \pm 0.26, 0.43 \pm 0.16$, and $-0.23 \pm 0.20$ G) have been reported for $\alpha$ Boo \citep{2011A&A...529A.100S} along with a possible magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}.
 Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} indicates magnetic activity in its atmosphere.
@@
 The line was modeled by solving the radiative transfer equation in a spherical co-moving frame and the effects of partial redistribution \citep[e.g.,][]{1983ApJ...273..299D} were taken into account.
-Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
+Both of Drake's atmospheric models are semi-empirical and contain no assumptions about the wind driving mechanism.
+They contain the photospheric model of \cite{1975ApJ...200..660A}, predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$, and reach a maximum microturbulence of 5 km s$^{-1}$.
 They contain a broad temperature plateau with $T_{\rm{e}}$ $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and hydrogen is $\sim50$\% ionized.

### 2013-07-13 aj_submission_2/ms.tex
Jul 13: Resubmitted to AJ: If any more edits required then make in new directory

@@
 As the radio opacity is proportional to $n _{\rm{e}} n _{\rm{ion}}$, where $n_{\rm{e}}$ and $n_{\rm{ion}}$ are the electron and ion number densities respectively, this model greatly overestimates the actual radio flux density at all VLA wavelengths.
-The linear Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the established value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
-The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect  wind driving mechanism and instead may be due to the simplifications and  uncertainties in these models, such as wind densities, magnetic field strengths, and damping lengths.
+The linear Alfv\'{e}n wave models for $\alpha$ Boo \citep{1988AcA....38..107K} also assume full ionization and have higher mass loss rates than the value given in Table \ref{tab:tab1}, predicting higher flux densities than observed.
+The lack of agreement between the Alfv\'en wave-driven wind models of \cite{1988AcA....38..107K,1989AcA....39..51K} and our observed radio fluxes may not necessarily be due to an incorrect  wind driving mechanism and instead may be due to the simplifications and  uncertainties in these models, such as wind densities, magnetic field strengths, damping lengths, and flow geometries close to the star.
 For example, the mass loss rate is very sensitive to the radial surface magnetic field strength (i.e., $\dot{M} \propto B^4$) in these Alfv\'en wave models \citep{1983ApJ...275..808H} so a small uncertainty in the mass loss rate can lead to a large uncertainty in the magnetic field strength.
@@
 It can be shown that the MOLsphere becomes optically thin at C-band (i.e.
-$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.45 $R_{\star}$, so if the long VLA wavelength radio emission from $\alpha$ Tau comes from a region closer in to the star, then the MOLsphere either has a geometrical width  $>$0.45 $R _{\star}$ or has a filling factor less than unity.
+$\tau _{\rm{6\,cm}} < 1$) for $\Delta L >$0.46 $R_{\star}$, so if the long VLA wavelength radio emission from $\alpha$ Tau comes from a region closer in to the star, then the MOLsphere either has a geometrical width  $>$0.46 $R _{\star}$ or has a filling factor less than unity.
 
@@
 It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}.
-If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e}(r) \propto r^{-p}$ and $T_{e}(r) \propto r^{-n}$ respectively, then
+If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power law form $n_{e}(r) \propto r^{-p}$ and $T_{e}(r) \propto r^{-n}$ respectively, then
 
@@
 \end{equation}
-\citep[e.g.,][]{1987ApJ...312..813S}.
+\citep[e.g.,][]{1987ApJ...312..813S}. These power law approximations are only going to be valid over certain radial ranges of the star's outflow.
 
@@
 One potential explanation for spectral indices of stellar outflows being larger than 0.6 is that the wind is still accelerating in the radio emitting region, if the thermal gradients are assumed to be small.
-If we ignore thermal gradients completely, then the density coefficients are $p  =2.7$ and 5.5 for $\alpha$ Boo and $\alpha$ Tau, respectively.
-From mass conservation arguments assuming a steady flow, the power law coefficients for the velocity profiles of each star can be found, ie., $v(r) \propto r^{p-2}$.
+For an isothermal flow, the density coefficients are $p  =2.7$ and 5.5 for $\alpha$ Boo and $\alpha$ Tau, respectively.
+From mass conservation, and assuming a steady flow, the power law coefficients for the velocity profiles of each star can be found, ie., $v(r) \propto r^{p-2}$.
 For $\alpha$ Boo we find $v(r) \propto r^{0.7}$ while for $\alpha$ Tau we find $v(r) \propto r^{3.5}$.
@@
 
-The assumption of completely ignoring thermal gradients in a stellar outflow is probably unreliable however.
+The assumption of shallow thermal gradients in a stellar outflow is probably unreliable however.
 It is likely that some form of Alfv\`{e}n waves are required to lift the material out of the gravitational potential as suggested by \cite{1980ApJ...242..260H}.
-These waves need damping lengths which are much larger than the density scale height $H_{\star}$ (where $H_{\star} \sim 10 \ H_{\odot}$ for our targets), in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1983ApJ...275..808H}.
-It has also been shown that these waves are expected to produce substantial heating deposition near the base of the wind \citep{1982ApJ...261..279H}.
+These waves need damping lengths which are much larger than the chromospheric density scale height $H$ (where $H \sim 0.01\ R_{\star}$ for our targets), in order to lift the material out of the gravitational potential but $\lesssim 1 \, R_{\star}$ in order to avoid wind terminal velocities greater than those observed \citep[e.g.][]{1983ApJ...275..808H}.
+It has also been shown that these waves are expected to produce substantial heating near the base of the wind \citep[e.g.][]{1982ApJ...261..279H}.
 If the long wavelength radio emission from $\alpha$ Tau is indeed emanating from the wind acceleration region, then the dissipation of these Alfv\`{e}n waves may introduce thermal gradients in this region and its velocity profile will not be described by $v(r) \propto r^{3.5}$.
-Furthermore, diverging flow geometries have been invoked as a more realistic representation of stellar atmospheres \citep{1982ApJ...257..264H,1989A&A...209..327J,2006SSRv..122..181V} and so one could write the continuity equation for a steady flow as
-\begin{equation}
-\dot{M} _{\star} = f(r)4\pi r^2 \rho (r) v(r),
-\end{equation}
-where $f(r)$ is a function describing the divergence from a purely radial flow [i.e., $f(r)=1$], $\dot{M} _{\star}$ is the stellar mass loss rate, and $\rho(r)$ is the gas density at $r$.
-If the non-radial expansion term can be described by a power-law $f(r) \propto r^s$, where $s>1$ indicates super-radial expansion, then $v(r) \propto r^{3.5-s}$ would describe the velocity profile of $\alpha$ Tau (ignoring thermal gradients and assuming a constant ionization fraction).
+Furthermore, diverging flow geometries have been invoked as a more realistic representation of stellar atmospheres \citep{1982ApJ...257..264H,1989A&A...209..327J,2006SSRv..122..181V} and so one could write the area of a flux tube (normalized to its value at $r_{1}$) as $(r/r_{1})^2f(r)$ where $f(r)$ is a function describing the divergence from a purely radial flow [i.e., when $f(r)=1$].
+If the non-radial expansion term can be described by a power law $f(r) \propto r^s$, where $s>1$ indicates super-radial expansion, then $v(r) \propto r^{3.5-s}$ would describe the velocity profile of $\alpha$ Tau (assuming an isothermal flow with a constant ionization fraction).
+Therefore, including diverging geometries reduces the magnitude of the acceleration.
 Further out in the wind, where it has reached its terminal velocity, one would also expect a thermal gradient (but now of opposite sign) due to adiabatic expansion and line cooling.
@@
 From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient is $p=2$ and thus the $T_{\rm{e}}$ coefficient is $n=1.65$.
-Pure adiabatic expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to recombination of H\,\textsc{ii} and/or line cooling.
+Pure adiabatic spherical expansion cooling with no heat source has $n=1.33$ so additional cooling routes must be operating, possibly due to line cooling.
 Finally, the wind ionization balance may not have become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from.
@@
 
-To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [referred to as `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power-law falloff of the form
+To investigate the possibility of the wind undergoing more rapid cooling closer in to the star, we adjusted one of the existing models [referred to as `Model A' in \cite{1985pssl.proc..351D}] to include a temperature power law falloff of the form
 \begin{equation}
